\worldchapter{\trans{foes_title}}{appendix-foes}
\label{ch:appendix-foes}

\begin{multicols}{2}


    \section{Alien}



    \subsection*{Hellish Berserker}

    The Hellish Berserker is a remotely humanoid alien creature of unknown origin. Bullish in stature, the creature walks upright, and is able to quickly cover a great distance.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 8 \\
        \textbf{\trans{movement_label}:} & 10 \\
        \textbf{\trans{strength_label}:} & 4 \\
        \textbf{\trans{dexterity_label}:} & 3 \\
        \textbf{\trans{mind_label}:} & 2 \\
    \end{tabular}

    \textbf{Charge} (8)\\
    The berserk rushes towards a victim and rams it. On impact it causes piercing 1 and rams the victim back 1D6 metres.\\
    \textbf{Bite} (6)\\
    Piercing 1, Blutend 1\\


    \subsection*{Brain}

    The Brain is a flying, spherical creature about one metre in diameter. Its skin appears to be made of a dark metal. At the front of the head is an opening that glows like hot lava and gives a hint of the Brain's contents.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 10 \\
        \textbf{\trans{movement_label}:} & 7 \\
        \textbf{\trans{strength_label}:} & 2 \\
        \textbf{\trans{dexterity_label}:} & 1 \\
        \textbf{\trans{mind_label}:} & 4 \\
    \end{tabular}

    \textbf{Aura} (6)\\
    Creates an aura of successes*D6 metres in which all aliens have 4 extra dice for all rolls.\\
    \textbf{Self destruction} (8)\\
    The brain explodes in a cloud of fire, spraying molten slag in all directions. For each success, a large portion of slag hits a character within a ten-metre radius. This inflicts two hits on impact and the Burning 1 status. At the end of each combat round, it hits again if it has not been removed.\\


    \subsection*{Nok}

    The Nok is a flying alien, similar to the [[brain|Brain]]. It also floats in the air. Its skin, like the Brain's, is a metallic but living surface. At the front, it has a narrow, raised-edge opening that reveals red-hot magma.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 4 \\
        \textbf{\trans{movement_label}:} & 6 \\
        \textbf{\trans{strength_label}:} & 2 \\
        \textbf{\trans{dexterity_label}:} & 3 \\
        \textbf{\trans{mind_label}:} & 2 \\
        \textbf{\trans{resistances_label}:} & ['Fire'] \\
    \end{tabular}

    \textbf{Fire Ball} (6)\\
    Causes 3 hits within a radius of D6 meters on each participant in the fight, each with two wounds and puncture 1.\\


    \subsection*{Medusa}

    These large, floating creatures are appearing in increasing numbers around the Dante Station built above Jupiter's surface. They are at least 2 metres in diameter and float, both in space and in the atmosphere of a space station.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 15 \\
        \textbf{\trans{movement_label}:} & 8 \\
        \textbf{\trans{strength_label}:} & 2 \\
        \textbf{\trans{dexterity_label}:} & 4 \\
        \textbf{\trans{mind_label}:} & 4 \\
        \textbf{\trans{resistances_label}:} & ['Fire', 'Steal Actions'] \\
    \end{tabular}

    \textbf{Fire Beam} (8)\\
    A jet of fire pours out of what might be called the Medusa's mouth. The hits cause piercing 1 and can be divided among victims in a straight line. Any victim who has taken at least one wound receives Burning 1.\\
    \textbf{Charging} (6)\\
    The Medusa rolls D6 according to this skill. For each success it receives a charge, which can be used as additional dice for the next fire beam. From the moment it charges, the Medusa has 6+ cover until the start of its next combat round.\\


    \subsection*{Harbinger}

    The Harbinger is a flying alien being from beyond, whose appearance is unlike anything that has been seen before. It hovers in the air with wings that resemble those of a bird, but made of an unusual material. Its skin is a smooth and reflective golden surface that glows in the sunlight.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 25 \\
        \textbf{\trans{movement_label}:} & 6 \\
        \textbf{\trans{strength_label}:} & 3 \\
        \textbf{\trans{dexterity_label}:} & 4 \\
        \textbf{\trans{mind_label}:} & 5 \\
        \textbf{\trans{resistances_label}:} & ['Fire', 'Shock', 'Steal Actions'] \\
    \end{tabular}

    \textbf{Energy Beam} (9)\\
    A beam of energy from the eyes of the Harbinger causes piercing 2. Hits can be split in a straight line across victims and can cause critical hits.\\
    \textbf{Energy Shield} (5)\\
    The Harbinger can build up an energy shield as a reaction, which provides 5+ cover.\\
    \textbf{Shock} (8)\\
    The Harbinger causes a shockwave with a radius of 1D6 metres around him. The shockwave has piercing 1. It causes any victim who has taken a wound to be Shocked 1. It cannot cause Critical Hits.\\


    \section{Undead}



    \subsection*{Vampire spawn}

    The vampire spawn is a lower vampire. Without much influence, this is a figure which has limited powers, and may be left to its own devices.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 10 \\
        \textbf{\trans{movement_label}:} & 4 \\
        \textbf{\trans{strength_label}:} & 2 \\
        \textbf{\trans{dexterity_label}:} & 2 \\
        \textbf{\trans{mind_label}:} & 2 \\
        \textbf{\trans{resistances_label}:} & ['Cold', 'Water'] \\
    \end{tabular}

    \textbf{Bite} (8)\\
    Bleeding 1\\
    \textbf{Black Magic} (6)\\
    The Vampire Spawn casts a spell of black magic. The successes of this roll represent the \textbf{power} of the spell.\\


    \subsection*{Zombie}

    The zombie is a tragic figure that appears in many stories. A human being who is kept alive in a special and unnatural way after his death. Zombies have a brain the size of a pea, they know little more than the desire for blood. And brains. So, if pop culture is to be believed.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 6 \\
        \textbf{\trans{movement_label}:} & 3 \\
        \textbf{\trans{strength_label}:} & 3 \\
        \textbf{\trans{dexterity_label}:} & 1 \\
        \textbf{\trans{mind_label}:} & 1 \\
        \textbf{\trans{resistances_label}:} & ['Fire', 'Poison'] \\
    \end{tabular}

    \textbf{Undead Grip} (4)\\
    Poison 1\\
    \textbf{Bite} (5)\\
    Poison 1\\


    \subsection*{Mummy}

    The living mummy is undead. It has been magically brought to life. Nothing of her spirit remains, all she seeks is to take the life of her victims. She is usually unarmed, but her curse poisons her victims.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 8 \\
        \textbf{\trans{movement_label}:} & 3 \\
        \textbf{\trans{strength_label}:} & 3 \\
        \textbf{\trans{dexterity_label}:} & 1 \\
        \textbf{\trans{mind_label}:} & 2 \\
        \textbf{\trans{resistances_label}:} & ['Fire', 'Poison'] \\
    \end{tabular}

    \textbf{Grip} (6)\\
    Piercing 0\\
    \textbf{Curse} (4)\\
    Piercing 3, Poison 2\\


    \subsection*{Former Officer}

    This officer of Division S or V has suffered a fate worse than death. An unnatural, alien power has saved him from dying of his wounds. Instead, he ekes out an uncertain, eternal existence as a living corpse.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 8 \\
        \textbf{\trans{movement_label}:} & 6 \\
        \textbf{\trans{strength_label}:} & 3 \\
        \textbf{\trans{dexterity_label}:} & 2 \\
        \textbf{\trans{mind_label}:} & 2 \\
    \end{tabular}

    \textbf{Pistol} (6)\\
    Durchschlag 1\\


    \subsection*{Minaos Torq, the first Guardian}

    Once a shining figure and guardian of the first lock, Minaos Torq is now only a skeletal shadow of his former self. Banished by the magic of his crown, he sits on his throne and waits for a lucky coincidence that will bring him back to life.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 30 \\
        \textbf{\trans{movement_label}:} & 4 \\
        \textbf{\trans{strength_label}:} & 4 \\
        \textbf{\trans{dexterity_label}:} & 2 \\
        \textbf{\trans{mind_label}:} & 4 \\
        \textbf{\trans{resistances_label}:} & ['Fire', 'Shock', 'Steal Actions'] \\
    \end{tabular}

    \textbf{Cold Grip} (6)\\
    Pierce 0\\
    \textbf{Lightning Strike} (10)\\
    Minaos rolls the attack roll and spreads the hits over any number of enemies in his view. Anyone hit may roll for resistance. If this roll shows a success, one wound is prevented. Pierce 1, Shock 1.\\
    \textbf{Shock} (6)\\
    Pierce 1, Shock 1\\
    \textbf{Awaken servant} (8)\\
    In sight, 1D3 Minoan statues are brought to life by Minaos.\\


    \subsection*{Scarecrow}

    At harvest time, when death revisits the twilit world and summer’s blossoms bow their withered heads, eerie scarecrows loom in silent vigil over empty fields. With immortal patience, these stoic sentinels hold their posts through wind, storm, and flood, bound to their master’s command, eager to terrify prey with its sackcloth visage and rend victims with its razor-sharp claws.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 8 \\
        \textbf{\trans{movement_label}:} & 0 \\
        \textbf{\trans{strength_label}:} & 2 \\
        \textbf{\trans{dexterity_label}:} & 0 \\
        \textbf{\trans{mind_label}:} & 4 \\
        \textbf{\trans{resistances_label}:} & ['Fire'] \\
    \end{tabular}

    \textbf{Claw} (6)\\
    Bleeding 1\\


    \subsection*{Skelett}

    Ein wandelndes Skelett, von dunkler Magie belebt.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 4 \\
        \textbf{\trans{movement_label}:} & 3 \\
        \textbf{\trans{strength_label}:} & 2 \\
        \textbf{\trans{dexterity_label}:} & 2 \\
        \textbf{\trans{mind_label}:} & 2 \\
    \end{tabular}

    \textbf{Knochengriff} (8)\\
    Vergiftet 1\\
    \textbf{Kalter Atem} (6)\\
    Geschockt 2, 5 Meter Reichweite\\


    \section{Animal}



    \subsection*{Vulture}

    On rising thermals, the vulture circles patiently, watching for signs of weakness below. It does not hunt in the traditional sense—waiting instead for the inevitable, drawn to death, decay, and the promise of easy sustenance. Its presence is a silent omen, often arriving before the end has fully come. On the ground, it moves with awkward persistence, tearing and feeding with grim efficiency. In darker interpretations, it feels like a herald of fate, appearing wherever life falters, as if summoned by the dying.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 2 \\
        \textbf{\trans{movement_label}:} & 6 \\
        \textbf{\trans{strength_label}:} & 1 \\
        \textbf{\trans{dexterity_label}:} & 3 \\
        \textbf{\trans{mind_label}:} & 2 \\
    \end{tabular}

    \textbf{Beak} (7)\\
    Piercing 1\\


    \subsection*{Seal}

    Along cold shores and drifting ice, the seal moves with effortless grace between water and land. In the sea it is swift and elusive, diving and turning with fluid precision; on land it appears slower, yet remains alert and wary. Seals are not natural aggressors, but when cornered or defending their young, they react with sudden ferocity—biting and thrashing with surprising strength. Their presence often signals rich hunting grounds, but also hidden dangers beneath the surface. In darker interpretations, they feel watchful and knowing, eyes lingering just above the waterline before slipping silently out of sight.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 5 \\
        \textbf{\trans{movement_label}:} & 5 \\
        \textbf{\trans{strength_label}:} & 1 \\
        \textbf{\trans{dexterity_label}:} & 2 \\
        \textbf{\trans{mind_label}:} & 2 \\
    \end{tabular}

    \textbf{Bite} (5)\\
    Piercing 0\\


    \subsection*{Rhinoceros}

    A heavily built and short-tempered giant, the rhinoceros embodies raw impact, stubborn resilience, and explosive aggression. Its poor eyesight is offset by acute hearing and scent, reacting instantly to perceived threats. Once it commits, it charges with unstoppable force, goring and crushing anything in its path. A rhinoceros does not maneuver or hesitate—it breaks through. In darker interpretations, it feels like a living battering ram, driven by blind momentum and unyielding instinct.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 10 \\
        \textbf{\trans{movement_label}:} & 4 \\
        \textbf{\trans{strength_label}:} & 3 \\
        \textbf{\trans{dexterity_label}:} & 3 \\
        \textbf{\trans{mind_label}:} & 1 \\
    \end{tabular}

    \textbf{Charge} (10)\\
    Piercing 2\\


    \subsection*{Schlange}

    A silent and elusive predator, the venomous snake embodies patience, precision, and hidden lethality. It relies on camouflage and stillness, striking with lightning speed when prey comes within reach. Its venom does the true killing—weakening, paralyzing, or slowly breaking the victim from within. Snakes avoid open confrontation, preferring ambush and retreat, but a single mistake near them can prove fatal. In darker interpretations, they feel cold and calculating, as if every movement is deliberate and every strike inevitable.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 2 \\
        \textbf{\trans{movement_label}:} & 5 \\
        \textbf{\trans{strength_label}:} & 1 \\
        \textbf{\trans{dexterity_label}:} & 3 \\
        \textbf{\trans{mind_label}:} & 1 \\
    \end{tabular}

    \textbf{Bite} (8)\\
    Poison 1\\


    \subsection*{Rat}

    In the dark and hidden places, the rat thrives where others falter. It slips through cracks, nests in walls, and gathers in numbers that turn nuisance into threat. Alone it is timid and easily driven off, but in groups it becomes bold—gnawing, biting, and overwhelming through sheer persistence. Rats spread filth, consume supplies, and carry unseen dangers with them. In darker interpretations, they feel like a creeping infestation, a living sign of decay that grows stronger the longer it is ignored.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 2 \\
        \textbf{\trans{movement_label}:} & 5 \\
        \textbf{\trans{strength_label}:} & 1 \\
        \textbf{\trans{dexterity_label}:} & 3 \\
        \textbf{\trans{mind_label}:} & 1 \\
    \end{tabular}

    \textbf{Bite} (5)\\
    Bleeding 1\\


    \subsection*{Scorpion}

    Hidden beneath sand, stone, or shadow, the scorpion waits with unnerving stillness. It reacts in an instant when disturbed, its stinger striking with precise, practiced speed. The venom does not need brute force—it weakens, paralyzes, or ends the fight outright. It does not chase; it punishes intrusion. In harsher interpretations, it feels ancient and indifferent, perfectly suited to a world where hesitation means death.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 3 \\
        \textbf{\trans{movement_label}:} & 5 \\
        \textbf{\trans{strength_label}:} & 1 \\
        \textbf{\trans{dexterity_label}:} & 3 \\
        \textbf{\trans{mind_label}:} & 1 \\
    \end{tabular}

    \textbf{Bite} (6)\\
    Poison 1\\
    \textbf{Sting} (8)\\
    Poison 2\\


    \subsection*{Frog}

    Bright colors in the undergrowth signal danger long before the frog itself moves. Small and easily overlooked, it relies on potent toxins rather than strength, turning even a careless touch into a threat. It does not hunt through pursuit but through proximity—its presence alone can be enough to harm. In dense jungles or humid environments, it becomes part of the landscape, a hidden hazard among leaves and water. In darker interpretations, it feels almost unnatural, its vivid appearance a deliberate warning that something beneath the surface is deeply wrong.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 2 \\
        \textbf{\trans{movement_label}:} & 4 \\
        \textbf{\trans{strength_label}:} & 1 \\
        \textbf{\trans{dexterity_label}:} & 1 \\
        \textbf{\trans{mind_label}:} & 1 \\
    \end{tabular}

    \textbf{Tong} (3)\\
    Poison 1\\


    \subsection*{Tiger}

    A solitary and elusive apex predator, the tiger embodies stealth, patience, and explosive violence. Unlike pack hunters, it relies on perfect timing—stalking unseen, closing distance in silence, and ending the hunt in a single decisive strike. Tigers are territorial and unpredictable, vanishing into their surroundings as easily as they emerge. In darker interpretations, they feel almost spectral—silent, inevitable, and terrifyingly precise.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 6 \\
        \textbf{\trans{movement_label}:} & 4 \\
        \textbf{\trans{strength_label}:} & 2 \\
        \textbf{\trans{dexterity_label}:} & 3 \\
        \textbf{\trans{mind_label}:} & 2 \\
    \end{tabular}

    \textbf{Bite} (10)\\
    Piercing 1, Bleeding 1\\
    \textbf{Claws} (10)\\
    Piercing 1\\


    \subsection*{Jellyfish}

    Drifting through the water with quiet grace, the jellyfish appears almost harmless—until contact is made. Its translucent body conceals trailing tentacles armed with potent venom, reacting instantly to touch. It does not pursue or hunt in the traditional sense; instead, it turns its surroundings into a passive hazard, where movement itself becomes dangerous. In numbers, they form near-invisible barriers that are difficult to detect until it is too late. In darker interpretations, they feel like living traps of the sea—silent, indifferent, and unavoidable.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 2 \\
        \textbf{\trans{movement_label}:} & 4 \\
        \textbf{\trans{strength_label}:} & 1 \\
        \textbf{\trans{dexterity_label}:} & 2 \\
        \textbf{\trans{mind_label}:} & 1 \\
    \end{tabular}

    \textbf{Sting} (4)\\
    Poison 1\\


    \subsection*{Ox}

    A powerful and stubborn beast, the bull embodies raw force, endurance, and territorial fury. Whether wild or driven to rage, it reacts with sudden, violent charges, using its horns to gore and toss aside anything in its path. Unlike predators, it does not hunt—it confronts, driving intruders away through sheer momentum and intimidation. Oxen, while more controlled, still possess immense strength and can become dangerous when stressed or overburdened. In darker interpretations, the bull becomes a symbol of blind wrath and unstoppable momentum, a living force that cannot be reasoned with once unleashed.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 8 \\
        \textbf{\trans{movement_label}:} & 4 \\
        \textbf{\trans{strength_label}:} & 2 \\
        \textbf{\trans{dexterity_label}:} & 3 \\
        \textbf{\trans{mind_label}:} & 2 \\
    \end{tabular}

    \textbf{Ram} (10)\\
    Piercing 1\\


    \subsection*{Elephant}

    A towering giant of the natural world, the elephant embodies immense strength, resilience, and unstoppable momentum. Usually calm and deliberate, it becomes a devastating force when threatened or provoked—charging with crushing weight and sweeping aside anything in its path. Its size alone reshapes the battlefield, turning terrain into an advantage. Elephants are not inherently aggressive, but once angered or panicked, they are nearly impossible to stop. In darker interpretations, they feel like living engines of destruction—slow to rouse, but catastrophic when unleashed.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 10 \\
        \textbf{\trans{movement_label}:} & 4 \\
        \textbf{\trans{strength_label}:} & 4 \\
        \textbf{\trans{dexterity_label}:} & 2 \\
        \textbf{\trans{mind_label}:} & 2 \\
    \end{tabular}

    \textbf{Choke} (8)\\
    The elephant chokes the victim with its trunk.\\
    \textbf{Stomp} (16)\\
    The elephant’s full weight bears down on the victim. The attack has Piercing 2, but can only be used if the elephant has already been adjacent to the target for one round.\\


    \subsection*{Eagle}

    High above the land, the eagle circles with commanding vision, observing every movement below. It does not waste effort—waiting for the precise moment before diving in a swift, lethal descent. Its talons strike with accuracy and force, seizing prey before it can react. Even when not attacking, its presence dominates the sky, a constant watcher that cannot be easily approached or escaped. In darker interpretations, it feels like an unblinking eye of the heavens, distant, patient, and utterly decisive when it acts.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 2 \\
        \textbf{\trans{movement_label}:} & 10 \\
        \textbf{\trans{strength_label}:} & 1 \\
        \textbf{\trans{dexterity_label}:} & 4 \\
        \textbf{\trans{mind_label}:} & 2 \\
    \end{tabular}

    \textbf{Claws} (7)\\
    Bleeding 1\\
    \textbf{Beak} (7)\\
    Piercing 1\\


    \subsection*{Bat}

    From the rafters and cave ceilings, bats descend in restless motion, guided more by sound than sight. They move in erratic swarms, disorienting and unnerving, their sudden proximity enough to startle even seasoned travelers. Alone they are fragile, but in numbers they overwhelm—clawing, biting, and filling the air with chaotic movement. Their presence often marks decay, darkness, or forgotten places. In darker interpretations, they feel like living shadows, erupting from the black and vanishing just as quickly.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 2 \\
        \textbf{\trans{movement_label}:} & 5 \\
        \textbf{\trans{strength_label}:} & 1 \\
        \textbf{\trans{dexterity_label}:} & 4 \\
        \textbf{\trans{mind_label}:} & 1 \\
    \end{tabular}

    \textbf{Bite} (2)\\
    Piercing 2\\


    \subsection*{Boar}

    A brutal and fearless force of the wild, the boar embodies aggression, resilience, and territorial dominance. When threatened or cornered, it charges with explosive speed, using its tusks to gore and trample anything in its path. Boars do not retreat easily—they commit fully, fighting through injury and pain with relentless fury. In darker interpretations, they appear almost unstoppable, driven by blind rage and an unyielding instinct to destroy intruders.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 8 \\
        \textbf{\trans{movement_label}:} & 4 \\
        \textbf{\trans{strength_label}:} & 3 \\
        \textbf{\trans{dexterity_label}:} & 1 \\
        \textbf{\trans{mind_label}:} & 2 \\
    \end{tabular}

    \textbf{Ram} (10)\\
    Piercing 1\\


    \subsection*{Camel}

    A hardy beast of harsh lands turned volatile and dangerous, the camel embodies endurance twisted into aggression. Normally resilient and deliberate, it can become fiercely territorial or unpredictable under stress, lashing out with powerful bites, trampling kicks, and sudden charges. Its endurance allows it to outlast opponents, pressing the attack longer than expected. Camels are difficult to intimidate once enraged, their stubborn nature turning into relentless hostility. In darker interpretations, they feel uncanny—enduring, spiteful, and disturbingly persistent, as if the desert itself refuses to yield.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 8 \\
        \textbf{\trans{movement_label}:} & 4 \\
        \textbf{\trans{strength_label}:} & 2 \\
        \textbf{\trans{dexterity_label}:} & 2 \\
        \textbf{\trans{mind_label}:} & 2 \\
    \end{tabular}

    \textbf{Bite} (6)\\
    Piercing 1\\


    \subsection*{Gorilla}

    A massively built and intelligent primate, the gorilla embodies controlled strength, social dominance, and explosive violence. Normally calm within its group, it reacts with terrifying force when threatened, defending territory or kin with overwhelming physical power. Displays of dominance—beating its chest, roaring, charging—are often warnings, but once it commits, the attack is swift and brutal. A gorilla does not hunt like a predator; it confronts and crushes threats directly. In darker interpretations, it feels almost sentient in its fury—calculated, protective, and unstoppable when roused.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 6 \\
        \textbf{\trans{movement_label}:} & 4 \\
        \textbf{\trans{strength_label}:} & 2 \\
        \textbf{\trans{dexterity_label}:} & 3 \\
        \textbf{\trans{mind_label}:} & 3 \\
    \end{tabular}

    \textbf{Grip} (8)\\
    The victim is held fast and can only break free with a Strength test.\\


    \subsection*{Owl}

    In the quiet hours, the owl moves where sound itself seems to fade. Its flight is nearly silent, wings cutting through the dark without warning. Guided by exceptional hearing, it locates movement others would miss, striking with sudden precision from above. It does not linger—appearing only long enough to seize what it seeks before vanishing again into shadow. In darker interpretations, it feels like a watcher of the night, unseen yet ever-present, a whisper of motion just beyond perception.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 2 \\
        \textbf{\trans{movement_label}:} & 8 \\
        \textbf{\trans{strength_label}:} & 1 \\
        \textbf{\trans{dexterity_label}:} & 3 \\
        \textbf{\trans{mind_label}:} & 4 \\
    \end{tabular}

    \textbf{Beak} (6)\\
    Piercing 0\\


    \subsection*{Goose}

    By still water and open fields, the goose holds its ground with unexpected defiance. What seems like a harmless creature quickly turns confrontational when approached, hissing, spreading its wings, and advancing without hesitation. It defends territory and kin with startling boldness, striking with its beak and battering with powerful wings. Retreat is not its first instinct—challenge is. In darker interpretations, it feels oddly relentless, a small but furious guardian that refuses to yield, no matter the odds.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 2 \\
        \textbf{\trans{movement_label}:} & 6 \\
        \textbf{\trans{strength_label}:} & 1 \\
        \textbf{\trans{dexterity_label}:} & 2 \\
        \textbf{\trans{mind_label}:} & 3 \\
    \end{tabular}

    \textbf{Bite} (8)\\
    Bleeding 1\\


    \subsection*{Wild Dog}

    A relentless pack hunter driven by coordination, endurance, and instinct. Wild dogs do not rely on strength alone—they win through teamwork, communication, and exhaustion of their prey. They harry targets over long distances, forcing mistakes and isolating the weak before closing in together. Individually manageable, but in numbers they become a fast-moving, disciplined threat. In darker interpretations, they feel eerily synchronized—like a single will spread across many bodies.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 6 \\
        \textbf{\trans{movement_label}:} & 4 \\
        \textbf{\trans{strength_label}:} & 2 \\
        \textbf{\trans{dexterity_label}:} & 2 \\
        \textbf{\trans{mind_label}:} & 2 \\
    \end{tabular}

    \textbf{Bite} (6)\\
    Bleeding 1\\
    \textbf{Call to the pack} (6)\\
    The wild dog calls to its pack. After 1d3 combat rounds, additional wild dogs arrive equal to the number of successes on this roll.\\


    \subsection*{Giant Crab}

    Across tidal flats and along rocky shores, the giant crab advances with unsettling purpose. Its heavy shell turns aside lesser blows, while massive claws snap with crushing force, capable of breaking bone or armor alike. It does not rush blindly—each movement is measured, closing distance while guarding itself with raised pincers. In its domain, footing is treacherous, and escape is hindered by terrain it knows well. In darker interpretations, it feels like a living bastion of the coast—unyielding, alien, and perfectly adapted to drag the unwary into a slow, inevitable end.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 6 \\
        \textbf{\trans{movement_label}:} & 6 \\
        \textbf{\trans{strength_label}:} & 2 \\
        \textbf{\trans{dexterity_label}:} & 2 \\
        \textbf{\trans{mind_label}:} & 1 \\
    \end{tabular}

    \textbf{Claws} (10)\\
    \textit{Dad-a-chum? Dum-a-chum? Ded-a-chek? Did-a-chick?}\\


    \subsection*{Wolf}

    A predatory hunter of the wild, the wolf embodies patience, instinct, and coordination. Rarely alone, it stalks its prey in packs, testing for weakness before committing to the kill. Wolves avoid unnecessary risk, circling, harassing, and striking when advantage is certain. In harsher interpretations, they may appear unnaturally intelligent, relentless, or disturbingly fearless.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 4 \\
        \textbf{\trans{movement_label}:} & 5 \\
        \textbf{\trans{strength_label}:} & 2 \\
        \textbf{\trans{dexterity_label}:} & 3 \\
        \textbf{\trans{mind_label}:} & 2 \\
    \end{tabular}

    \textbf{Bite} (7)\\
    Bleeding 1\\


    \subsection*{Spider}

    A patient and methodical predator, the venomous spider embodies stillness, precision, and entrapment. It waits unseen, concealed in webs or hidden corners, striking only when prey is caught or vulnerable. Its venom weakens or paralyzes, ensuring the victim cannot escape once seized. Unlike hunters that pursue, the spider controls its domain—turning space itself into a trap. In darker interpretations, it feels calculating and alien, a silent architect of death whose presence is often noticed too late.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 2 \\
        \textbf{\trans{movement_label}:} & 2 \\
        \textbf{\trans{strength_label}:} & 1 \\
        \textbf{\trans{dexterity_label}:} & 3 \\
        \textbf{\trans{mind_label}:} & 1 \\
    \end{tabular}

    \textbf{Bite} (4)\\
    Poison 1, Piercing 1\\


    \subsection*{Giant Octopus}

    From the depths, something vast and patient unfolds. The giant octopus is a master of concealment, blending seamlessly with rock and reef until it chooses to act. Its intelligence is unsettling—testing, probing, learning. When it strikes, it does so with sudden reach, ensnaring prey in powerful limbs and pulling it into a crushing, inescapable grip. The water becomes its weapon, obscuring vision and direction alike. In darker interpretations, it feels ancient and watchful, a mind lurking below, waiting for the right moment to claim what drifts too close.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 10 \\
        \textbf{\trans{movement_label}:} & 4 \\
        \textbf{\trans{strength_label}:} & 3 \\
        \textbf{\trans{dexterity_label}:} & 3 \\
        \textbf{\trans{mind_label}:} & 2 \\
    \end{tabular}

    \textbf{Grip} (10)\\
    The victim is grappled and suffers 2 Wounds each combat round. It can break free on its turn with a Strength test.\\


    \subsection*{Bear}

    A massive and resilient force of nature, the bear embodies raw strength, endurance, and territorial fury. Unlike swift predators, it does not rely on speed or subtlety—once roused, it overwhelms through sheer power and persistence. Bears are often indifferent until provoked, but when threatened or defending their domain, they become relentless and devastating. In darker interpretations, they feel almost unstoppable—an embodiment of primal wrath given form.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 8 \\
        \textbf{\trans{movement_label}:} & 3 \\
        \textbf{\trans{strength_label}:} & 3 \\
        \textbf{\trans{dexterity_label}:} & 2 \\
        \textbf{\trans{mind_label}:} & 2 \\
    \end{tabular}

    \textbf{Bite} (8)\\
    Bleeding 2\\
    \textbf{Claws} (8)\\
    Bleeding 1\\


    \subsection*{Crocodile}

    A patient and ancient ambush predator, the crocodile embodies stillness, precision, and sudden, overwhelming violence. It waits half-submerged, barely visible, striking in an instant when prey comes too close to the water’s edge. Its grip is relentless—once seized, escape is unlikely. Crocodiles do not pursue far; they control the boundary between land and water, turning safe ground into a deadly trap. In darker interpretations, they feel primordial and calculating, as if the water itself has teeth.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 6 \\
        \textbf{\trans{movement_label}:} & 4 \\
        \textbf{\trans{strength_label}:} & 2 \\
        \textbf{\trans{dexterity_label}:} & 2 \\
        \textbf{\trans{mind_label}:} & 2 \\
    \end{tabular}

    \textbf{Bite} (10)\\
    The victim can only break free from the bite with a Strength test. The crocodile will try to drag its victim underwater whenever possible.\\


    \subsection*{Shark}

    Beneath the surface, the shark moves with silent certainty, sensing what cannot be seen. It does not rush blindly—it circles, tests, and closes in with deliberate intent. A sudden strike ends the encounter in a burst of motion and blood, vanishing again into the depths just as quickly. In its domain, escape is uncertain and footing is lost. In darker interpretations, it feels like an unseen force of the deep, drawn to weakness and disturbance, as if the water itself has turned against its prey.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 8 \\
        \textbf{\trans{movement_label}:} & 6 \\
        \textbf{\trans{strength_label}:} & 2 \\
        \textbf{\trans{dexterity_label}:} & 3 \\
        \textbf{\trans{mind_label}:} & 1 \\
    \end{tabular}

    \textbf{Bite} (10)\\
    Piercing 1\\


    \subsection*{Hyena}

    A cunning scavenger and opportunistic hunter, the hyena thrives where others falter. It survives through adaptability, endurance, and ruthless pragmatism, often circling conflict rather than initiating it. Hyenas test weakness relentlessly, harassing, outlasting, and exploiting any sign of vulnerability. Their eerie vocalizations and unsettling demeanor give them a reputation that borders on the unnatural. In darker interpretations, they feel mocking and cruel—creatures that revel in decay and the downfall of others.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 4 \\
        \textbf{\trans{movement_label}:} & 4 \\
        \textbf{\trans{strength_label}:} & 1 \\
        \textbf{\trans{dexterity_label}:} & 3 \\
        \textbf{\trans{mind_label}:} & 2 \\
    \end{tabular}

    \textbf{Bite} (8)\\
    Bleeding 1\\


    \subsection*{Lion}

    A dominant apex predator, the lion embodies strength, authority, and lethal precision. Unlike relentless pack hunters, it relies on bursts of overwhelming force, often striking from concealment or claiming territory through sheer presence. A lion does not chase endlessly—it decides when the hunt begins and ends. In harsher interpretations, it appears regal and terrifying, a symbol of power that tolerates no challenge.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 6 \\
        \textbf{\trans{movement_label}:} & 4 \\
        \textbf{\trans{strength_label}:} & 3 \\
        \textbf{\trans{dexterity_label}:} & 2 \\
        \textbf{\trans{mind_label}:} & 2 \\
    \end{tabular}

    \textbf{Bite} (8)\\
    Piercing 1, Bleeding 1\\
    \textbf{Claws} (6)\\
    Piercing 1, Bleeding 2\\


    \section{Human}



    \subsection*{Cultist}

    A cultist, a member of some dark cult. They worship a dark deity, a powerful alien, or simply a lamb. They are not particularly clever, but they are many. And they can handle an Uzi. They probably eat children too!

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 10 \\
        \textbf{\trans{movement_label}:} & 4 \\
        \textbf{\trans{strength_label}:} & 2 \\
        \textbf{\trans{dexterity_label}:} & 2 \\
        \textbf{\trans{mind_label}:} & 2 \\
    \end{tabular}

    \textbf{Ritual Dagger} (8)\\
    Bleeding 1\\
    \textbf{Pistol} (6)\\
    Piercing 0\\


    \section{Mechanical}



    \subsection*{Alien spider}

    The spider is a mechanical being in the form of a spider, created by an unknown power. The spiders usually appear in groups and are mostly harmless, although they can bite with mechanical teeth.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 3 \\
        \textbf{\trans{movement_label}:} & 7 \\
        \textbf{\trans{strength_label}:} & 1 \\
        \textbf{\trans{dexterity_label}:} & 3 \\
        \textbf{\trans{mind_label}:} & 2 \\
        \textbf{\trans{resistances_label}:} & ['Fire', 'Shock'] \\
    \end{tabular}

    \textbf{Bite} (3)\\
    Shocked 1\\


    \subsection*{Minoan Statue}

    The statue of a minotaur guardian, finely crafted and life-size. It can be brought to life by Minaos Torq.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 8 \\
        \textbf{\trans{movement_label}:} & 2 \\
        \textbf{\trans{strength_label}:} & 3 \\
        \textbf{\trans{dexterity_label}:} & 1 \\
        \textbf{\trans{mind_label}:} & 2 \\
        \textbf{\trans{resistances_label}:} & ['Magic', 'Fire', 'Poison', 'Shock'] \\
    \end{tabular}

    \textbf{Sword blow} (6)\\
    Pierce 1\\


    \subsection*{Ultra Bot 5000}

    The Ultra Bot 5000 was researched by the NEXUS as a combat robot in Victorian times. However, the project was later dropped. Not only was the robot very ponderous and slow, its electronic drive was far ahead of its time and the battery did not last long enough to be fit for combat use.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 12 \\
        \textbf{\trans{movement_label}:} & 3 \\
        \textbf{\trans{strength_label}:} & 5 \\
        \textbf{\trans{dexterity_label}:} & 1 \\
        \textbf{\trans{mind_label}:} & 2 \\
        \textbf{\trans{resistances_label}:} & ['Fire', 'Shock'] \\
    \end{tabular}

    \textbf{Bayonet} (8)\\
    Piercing 1\\
    \textbf{12mm cannon} (8)\\
    Piercing 1\\


    \section{Magical}



    \subsection*{Werewolf}

    The werewolf is a creature that is half wolf, half human. At full moon, the normal human transforms into a wolf, which can grow up to two steps tall and is extremely aggressive. Anyone can become a werewolf as soon as they are bitten by an already infected werewolf.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 12 \\
        \textbf{\trans{movement_label}:} & 8 \\
        \textbf{\trans{strength_label}:} & 5 \\
        \textbf{\trans{dexterity_label}:} & 3 \\
        \textbf{\trans{mind_label}:} & 3 \\
    \end{tabular}

    \textbf{Bite} (8)\\
    Piercing 1, Bleeding 1\\
    \textbf{Claws} (8)\\
    Bleeding 1\\


    \subsection*{Compost fairy}

    The Compost Fairy is a strange, magical creature. She once lived in the compost of the witch Mare, in the Middle Ages on earth, not far from the town of Aquisgrani. Mare and she share a special bond, which is also magical.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 2 \\
        \textbf{\trans{movement_label}:} & 8 \\
        \textbf{\trans{strength_label}:} & 2 \\
        \textbf{\trans{dexterity_label}:} & 5 \\
        \textbf{\trans{mind_label}:} & 3 \\
        \textbf{\trans{resistances_label}:} & ['Magic'] \\
    \end{tabular}

    \textbf{Energy Orb} (2)\\
    Piercing 2, Shocked 1\\


    \section{Paranormal}



    \subsection*{Spectre}

    The Spectre is a ghost-like apparition that can move freely in space. The creature can glide through walls. Its grip and breath are ice-cold, and can cause serious harm to a victim.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 4 \\
        \textbf{\trans{movement_label}:} & 8 \\
        \textbf{\trans{strength_label}:} & 2 \\
        \textbf{\trans{dexterity_label}:} & 3 \\
        \textbf{\trans{mind_label}:} & 2 \\
        \textbf{\trans{resistances_label}:} & ['Magic', 'Physical Damage'] \\
    \end{tabular}

    \textbf{Cold Breath} (3)\\
    Penetration 4, Shock 2, Disoriented 1\\
    \textbf{Submerge} (4)\\
    The Spector may submerge from the real world and appear at an arbitrary place at the start of the next round. Submerging and Appearing uses one action each.\\
    \textbf{Cold Grip} (7)\\
    Shock 2\\


    \subsection*{Stalker}

    The stalker is a strange, paranormal being. He almost blurs into the background, and moves slowly without taking any steps. When he reaches a victim he strangles them, this seems to be his only interaction with the world.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 8 \\
        \textbf{\trans{movement_label}:} & 6 \\
        \textbf{\trans{strength_label}:} & 3 \\
        \textbf{\trans{dexterity_label}:} & 1 \\
        \textbf{\trans{mind_label}:} & 2 \\
        \textbf{\trans{resistances_label}:} & ['Magic', 'Physical Damage'] \\
    \end{tabular}

    \textbf{Choke} (7)\\
    Shock 1\\


    \subsection*{Phantomwarrior}

    A phantom warrior is the undead spirit of a soldier or other skilled person-at-arms (i.e. a professional killer) who has died in violent conflict or before completing an assigned task. Although incorporeal, a phantom warrior carries ghostly armour, shield and weapon. A phantom warrior's memory of the days before his death is hazy at best.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 10 \\
        \textbf{\trans{movement_label}:} & 4 \\
        \textbf{\trans{strength_label}:} & 3 \\
        \textbf{\trans{dexterity_label}:} & 3 \\
        \textbf{\trans{mind_label}:} & 2 \\
        \textbf{\trans{resistances_label}:} & ['Magic', 'Physical Damage'] \\
    \end{tabular}

    \textbf{Sword Attack} (10)\\
    Piercing 1\\


    \subsection*{Prehistoric axolotl}

    A creature from long forgotten times, which for some reason has survived into modern times.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 3 \\
        \textbf{\trans{movement_label}:} & 4 \\
        \textbf{\trans{strength_label}:} & 1 \\
        \textbf{\trans{dexterity_label}:} & 3 \\
        \textbf{\trans{mind_label}:} & 2 \\
    \end{tabular}



    \subsection*{Shoggy}

    Ein kleines Überbleibsel eines Shoggotten, welchem nur ein paar Augen und ein zahnloser Mund geblieben sind. Größtenteils harmlos.

    \begin{tabular}{@{}ll@{}}
        \textbf{\trans{wounds_label}:} & 2 \\
        \textbf{\trans{movement_label}:} & 1 \\
        \textbf{\trans{strength_label}:} & 1 \\
        \textbf{\trans{dexterity_label}:} & 2 \\
        \textbf{\trans{mind_label}:} & 2 \\
    \end{tabular}


\end{multicols}