\worldchapter{\trans{quirks_title}}{appendix-quirks}
\label{ch:appendix-quirks}

\begin{multicols}{2}

    \section{Madness and visions}

    \subsection*{Schizophrenia}

    The character experiences the world differently to how other people do. They may experience hallucinations, causing them to see, hear or feel things that are not there. They may also experience delusions that influence their behaviour and thought processes.

    The character is exceptionally creative and can find unique solutions to problems that others would never think of. Their different perspective on the world can lead to innovative ideas and artistic forms of expression. They have a strong ability to think \textbf{logically} and \textbf{perform}.

    The symptoms of schizophrenia make it difficult for the character to socialise or maintain stable relationships. Their \textbf{Communication} skills and \textbf{Charm} are limited.

    \begin{tabular}{@{}ll@{}}
        \textbf{Logic} & +1\\
        \textbf{Charm} & -1\\
        \textbf{Performance} & +2\\
        \textbf{Communication} & -2\\
    \end{tabular}

    \subsection*{Delusion}

    The character clings to beliefs that do not correspond to reality and are not shared by anyone else. These delusions may relate to various topics, such as persecution, grandeur or relationships.

    The delusion gives the character a strong sense of purpose and direction. Their unwavering belief in their cause gives them strong inner motivation and determination in certain situations. Their \textbf{Courage} and \textbf{Willpower} are increased.

    Delusions can cause a character to become alienated from reality, impairing their ability to act rationally or interact effectively with others. The game master may demand a logic check at any time. If the character fails this check, it means they are experiencing an active delusion at that moment.

    \begin{tabular}{@{}ll@{}}
        \textbf{Willpower} & +1\\
        \textbf{Logic} & +1\\
    \end{tabular}

    \subsection*{Dark Visions}

    The character is plagued by eerie visions that occasionally offer him glimpses of hidden or future events. These visions are often fragmentary and enigmatic. Sometimes they depict disturbing or threatening scenes. They occur unpredictably, sometimes making the character seem as if he is trapped in another reality.

    The visions can provide the character with valuable clues or warnings that help him avoid danger and uncover hidden truths.

    The visions are often disturbing and can take an emotional toll on the character. After each vision, they must take a stress test. If they fail, they receive two \textbf{stress}.


    \subsection*{Possession}

    The character is influenced by an otherworldly entity that gives him extra powers, but which also occasionally takes control of his body and mind. This possession occurs at unpredictable times and can be both helpful and harmful. The entity has its own goals and intentions, which do not always align with the character's own.

    The character receives a permanent +2 bonus to an attribute of their choice that corresponds to the entity.

    Occasionally, the entity can take control of the character and force them to perform unpredictable or dangerous actions. When this happens, the character rolls a D6. The higher the result, the more positive the outcome for the character. Results above 3 are usually positive.


    \subsection*{Doubting mind}

    The character is naturally suspicious and constantly questions the intentions and actions of others. While this scepticism protects them from deception, it also makes it difficult for them to find true allies and build trust. He tends to see a hidden agenda or trap in everything.

    The character is immune to manipulation and deception involving a deception roll.

    The character has difficulty trusting others due to his constant mistrust. This results in a -2 penalty to his \textbf{Communication} skill.

    \begin{tabular}{@{}ll@{}}
        \textbf{Communication} & -2\\
    \end{tabular}

    \section{Impulsive behavior}

    \subsection*{Depression}

    The character suffers from persistent feelings of hopelessness. They may have lost interest in activities they used to enjoy, and often feel tired or lacking in energy.

    Having experienced depression themselves, the character can develop a deep understanding of and compassion for others' suffering.

    Depression can prevent the character from performing everyday tasks or participating in social activities. They may withdraw and isolate themselves.

    \begin{tabular}{@{}ll@{}}
        \textbf{Conscientiousness} & -1\\
        \textbf{Endurance} & -1\\
        \textbf{Empathy} & +2\\
    \end{tabular}

    \subsection*{Thoughtless}

    The character often acts impulsively, without thinking things through. This spontaneity leads them to make quick decisions and rely on their instincts. However, this trait can also cause them to overlook important details or take ill-considered risks.

    The character is able to act quickly in dangerous or stressful situations. With the \textbf{Quick Reaction} rule, they can repeat a failed roll once.

    Because of his impulsive nature, the character tends to overlook important details and take ill-considered risks. This results in a reduction in \textbf{Logic}.

    \begin{tabular}{@{}ll@{}}
        \textbf{Logic} & -1\\
    \end{tabular}

    \subsection*{Restlessness}

    The character is driven by an inner restlessness that keeps them constantly on the move. Settling down or staying in one place for any length of time is difficult for them.

    Thanks to their restlessness, the character can remain active for longer without needing to take a break. Their endurance is increased.

    The character finds it difficult to concentrate on tasks that require calmness or patience. Their \textbf{Deftness} and \textbf{Conscientiousness} are reduced.

    \begin{tabular}{@{}ll@{}}
        \textbf{Conscientiousness} & -1\\
        \textbf{Deftness} & -1\\
        \textbf{Endurance} & +2\\
    \end{tabular}

    \subsection*{Daredevil}

    The character becomes increasingly reckless and careless. Where others would hesitate, he takes risks and often acts on instinct.

    The character's \textbf{Courage} has increased.

    The character's \textbf{Logic} is reduced.

    \begin{tabular}{@{}ll@{}}
        \textbf{Logic} & -2\\
        \textbf{Courage} & +2\\
    \end{tabular}

    \section{Personal characteristics}

    \subsection*{Nervousness}

    The character is fundamentally nervous. This means that he is easily distracted in battle, but it also enables him to carry out surprise attacks.

    The character receives 10 dice for each battle, which they can use as they wish for attacks and defences.

    The character cannot score critical hits when attacking.


    \subsection*{Clumsy}

    This character tends to drop things, trip over and be clumsy in general. This can lead to accidental mishaps in everyday life. However, it also adds an element of unpredictability and creativity.

    The character is distinguished by his unique ability to solve problems in unconventional ways. His clumsy nature often leads them to solutions that others would not think of, making them unexpected. He receives a bonus of two dice on checks that require unconventional thinking for this reason.

    The character has a reduced \textbf{Deftness}.

    \begin{tabular}{@{}ll@{}}
        \textbf{Deftness} & -2\\
    \end{tabular}

    \subsection*{Weak will to live}

    The character lacks resilience in the face of life's challenges. When faced with difficulties, they tend to give up more quickly or become discouraged by setbacks.

    Because of their indifference, the character has, in a sense, surrendered to their fate. He is given a destiny die.

    The character has reduced \textbf{Resistance}.

    \begin{tabular}{@{}ll@{}}
        \textbf{destiny dice} & +1\\
        \textbf{Resistance} & -2\\
    \end{tabular}

    \subsection*{Perfectionism}

    The character strives for perfection in all that they do. Never satisfied with anything less than his best, they work tirelessly to complete their tasks to the highest standard.

    The character receives two bonus dice and two rerolls due to his perfectionism.

    More complex actions taken by this character usually take twice as long as they would for other characters. If speed is important, the game master may require a logic roll. If this roll fails, the specified time is doubled.

    \begin{tabular}{@{}ll@{}}
        \textbf{rerolls} & +2\\
        \textbf{bonus dice} & +2\\
    \end{tabular}

    \section{Fears and aversions}

    \subsection*{Agoraphobia}




    \begin{tabular}{@{}ll@{}}
        \textbf{evasion} & +1\\
        \textbf{Conscientiousness} & -1\\
        \textbf{Perception} & +1\\
    \end{tabular}

    \subsection*{Social anxiety disorder}




    \begin{tabular}{@{}ll@{}}
        \textbf{rerolls} & -1\\
        \textbf{Conscientiousness} & +1\\
        \textbf{Communication} & -1\\
    \end{tabular}

    \subsection*{Acrophobia}




    \begin{tabular}{@{}ll@{}}
        \textbf{Perception} & +1\\
        \textbf{Courage} & -2\\
    \end{tabular}

    \subsection*{Hydrophobia}




    \begin{tabular}{@{}ll@{}}
        \textbf{Courage} & -2\\
        \textbf{Orientation} & +1\\
    \end{tabular}

    \subsection*{Mysophobia}




    \begin{tabular}{@{}ll@{}}
        \textbf{Conscientiousness} & +1\\
        \textbf{Resistance} & -1\\
    \end{tabular}

    \subsection*{Zoophobia}




    \begin{tabular}{@{}ll@{}}
        \textbf{evasion} & +1\\
        \textbf{Courage} & -1\\
        \textbf{Nature} & -1\\
    \end{tabular}

    \subsection*{Delusional parasitosis}




    \begin{tabular}{@{}ll@{}}
        \textbf{max stress} & +1\\
        \textbf{Conscientiousness} & -2\\
    \end{tabular}

    \subsection*{Coulrophobia}




    \begin{tabular}{@{}ll@{}}
        \textbf{Apprehension} & +1\\
        \textbf{Performance} & -1\\
        \textbf{Courage} & -1\\
    \end{tabular}

    \subsection*{teratophobia}




    \begin{tabular}{@{}ll@{}}
        \textbf{rerolls} & +1\\
        \textbf{Resistance} & -1\\
        \textbf{Orientation} & -1\\
    \end{tabular}

    \subsection*{Verfolgungsangst}

    der betroffene wird von Phasen geplagt in denen er sich von einer paranoiden Verfolgungsangst heimgesucht sieht,



    \begin{tabular}{@{}ll@{}}
        \textbf{Charm} & -1\\
        \textbf{Stealth} & -1\\
        \textbf{Courage} & -1\\
    \end{tabular}

    \subsection*{Fear of antiquities}

    The character has an irrational fear of anything old. He believes that every old object contains a power or secret that endangers him.

    Because of his fear, the character naturally spends more time studying antiquities. He achieves a grade of 4 in this knowledge.

    When near ancient artefacts, such as old walls, ruins or statues, as well as documents or books, the character becomes clumsier due to fear. All \textbf{physical} attributes are reduced by one.

    \begin{tabular}{@{}ll@{}}
        \textbf{Ancient Relics} & +4\\
    \end{tabular}

    \subsection*{Faithless}

    The character has lost all faith in higher beings or religion. They seek rational explanations for everything and are often suspicious of things that cannot be explained logically.

    Because they don't believe, the character always strives to find a rational explanation. He is given three \textbf{rerolls}.

    All rolls involving supernatural phenomena require a minimum roll that is two points higher. The character's religion skill is reduced.

    \begin{tabular}{@{}ll@{}}
        \textbf{Religion} & -3\\
    \end{tabular}

    \subsection*{Hypochondria}

    The character is overly concerned about his health, interpreting even the slightest physical symptom as a sign of a serious illness.

    The character is very knowledgeable about medical topics and healthcare due to his constant concern for their health. They receive a bonus on \textbf{First Aid} and \textbf{Medicine} knowledge.

    An exaggerated fear of illness can place a heavy strain on the character, impairing their ability to act. Their \textbf{Logic} and \textbf{Conscientiousness} are reduced.

    \begin{tabular}{@{}ll@{}}
        \textbf{Logic} & -1\\
        \textbf{Conscientiousness} & -1\\
        \textbf{First Aid} & +2\\
        \textbf{Medical science} & +1\\
    \end{tabular}

    \section{Mood swings}

    \subsection*{Night owl}

    The character is plagued by insomnia at night, leaving him feeling exhausted during the day.

    The character is particularly alert and attentive at night. He receives a +2 bonus to \textbf{Perception} and a +1 bonus to \textbf{Orientation} at night.

    The overtired character receives a -2 penalty to \textbf{Logic} and a -1 penalty to \textbf{Mechanics} during the day.


    \subsection*{Capricious}

    The character is known for his rapid and unpredictable mood swings. This moodiness can make them seem charming and persuasive one moment, and irritable or melancholic the next.

    The character can be very charming and persuasive in social situations. This gives them a bonus to their \textbf{Charm}. The ability to quickly switch between different moods enables them to adapt flexibly to different social dynamics.

    During any lengthy or in-depth conversation, the character must make a \textbf{Communication} roll. If they fail, their mood will swing and they will receive a penalty of -2 for the next D6 hours (instead of the bonus).

    \begin{tabular}{@{}ll@{}}
        \textbf{Charm} & +2\\
        \textbf{Communication} & +1\\
    \end{tabular}

    \subsection*{Diurnal}

    The character is at their most productive during the day and feels most comfortable in daylight. However, at night they are plagued by constant discomfort and subtle anxiety.

    During the day, the minimum roll for all skill rolls is reduced by one.

    At night, the minimum roll for all skill rolls is increased by one.


    \subsection*{Unresting}

    The character's restless spirit keeps them constantly alert and attentive. This inner turmoil means they can never find peace or relax completely.

    The character is always alert and vigilant. This gives them a bonus to \textbf{Perception}.

    Because they are unable to fully relax, the character only regenerates half of the normal amount of stress reduction (rounded up) with each instance of stress reduction. Even when resting, stress is halved instead of being completely eliminated.

    \begin{tabular}{@{}ll@{}}
        \textbf{Perception} & +2\\
    \end{tabular}

    \section{Sensory alterations}

    \subsection*{Hypersensitivity}

    The character experiences his surroundings more intensely than others do. He hears, sees and smells things more clearly and notices even subtle changes in his environment. This heightened sensitivity can be both enriching and burdensome.

    The character gains a +2 bonus to their Perception skill.

    The character quickly becomes overwhelmed in noisy environments. In these situations, he must pass a stress test. If he fails, he receives one \textbf{stress}.

    \begin{tabular}{@{}ll@{}}
        \textbf{Perception} & +2\\
    \end{tabular}

    \subsection*{Tinnitus}

    The character suffers from a constant ringing or buzzing in his ears. This noise can be particularly disturbing in quiet moments and impair concentration.

    The character is immune to acoustic illusions or manipulation due to the constant noise in their ears. Noises from their surroundings cannot distract him.

    The minimum roll for all \textbf{Perception} checks involving hearing is increased by 3.


    \section{Mystical ticks}

    \subsection*{Ancient Bloodline}

    The character believes that he is descended from an ancient, mystical bloodline. This bloodline is supposedly responsible for his special abilities and deep understanding of forgotten languages and symbols.

    The character can understand and interpret ancient languages and symbols. They receive a bonus of 2 dice on checks related to education, history, and antiquities, provided these are related to ancient writings. The character receives the Antiquities 1 knowledge.

    The character feels elitist and becomes increasingly eccentric. He gets a penalty on communication and charm.

    \begin{tabular}{@{}ll@{}}
        \textbf{Charm} & -1\\
        \textbf{Communication} & -1\\
        \textbf{Ancient Relics} & +1\\
    \end{tabular}

    \subsection*{Insatiable thirst for knowledge}

    The character is driven by an insatiable thirst for knowledge. They are constantly searching for new information, whether through books, conversations, or exploration.

    The character receives bonuses to \textbf{Logic} and \textbf{Education}.

    The insatiable thirst for knowledge leads to a negative perception of the character.

    \begin{tabular}{@{}ll@{}}
        \textbf{Education} & +1\\
        \textbf{Logic} & +1\\
        \textbf{Perception} & -1\\
    \end{tabular}

    \subsection*{Ascetic}

    The character increasingly sees no value in material possessions and becomes increasingly withdrawn. While this lifestyle provides them with inner strength and independence, it also causes them to distance themselves from social norms and relationships.

    The character experiences hungry and thirsty later than others, and has increased \textbf{Resistance}.

    The character's abstemious lifestyle makes it difficult for them to fit into social groups or form relationships. This results in a penalty in \textbf{Communication}.

    \begin{tabular}{@{}ll@{}}
        \textbf{Resistance} & +2\\
        \textbf{Communication} & -2\\
    \end{tabular}

    \section{Physical characteristics}

    \subsection*{Frail}

    The character grows weaker and weaker as their fears cause their strength to wane. While this physical weakness makes them more susceptible to physical strain, it also gives them a certain lightness and agility.

    Thanks to their less robust stature, the character can move more quietly and inconspicuously. They receive a bonus to \textbf{Stealth}.

    The character experiences reduced \textbf{Strength} and a constant sense of physical weakness and insecurity.

    \begin{tabular}{@{}ll@{}}
        \textbf{Strength} & -1\\
        \textbf{Stealth} & +2\\
    \end{tabular}

    \subsection*{Addiction}

    The character relies on a particular substance, activity or behaviour to function normally. This dependency can affect various areas of life, influencing decisions and actions significantly.

    If the character has access to the things they depend on, they become extremely focused and motivated. During this time, they have two destiny dice.

    If the character does not have access to what he depends on, they suffer withdrawal symptoms that impair their physical and mental performance.  Their minimum roll increases by one.


\end{multicols}