\worldchapter{Rüstung}{appendix-riotgear}
\label{ch:appendix-riotgear}

\begin{multicols}{2}


\section{Light armour}



\subsection*{Leather Cuirass}

\begin{pexample}
A lightweight leather cuirass that provides basic torso protection.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 2.50 kg \\
    \textbf{\trans{price_label}:} & 250 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N N C \footnote{D - Protection against demonic influence, S - Shock protection, R - Reflective Protection, F - Fire Protection, P - Poison Protection, B - Bleeding Protection, H - Sticky Protection, C - Crit Protection, N - Normal Protection}\\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{eye}\hspace{0.5em}}{}


\subsection*{Linothorax Breastplate}

\begin{pexample}
A layered linen breastplate reinforced with leather, providing flexibility and protection.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 3.00 kg \\
    \textbf{\trans{price_label}:} & 450 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N N N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{eye}\hspace{0.5em}}{}


\subsection*{Motorcycle Helmet}

\begin{pexample}
This piece of headwear consists of a large, rigid, aerodynamic outer shell made of polished composites or polymer, designed to fully encase the head. It features a thick, clear or tinted transparent visor that pivots up and down to cover the face.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 2.00 kg \\
    \textbf{\trans{price_label}:} & 400 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{plane}\hspace{0.5em}\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Linen Surcoat}

\begin{pexample}
Made of linen, this lightweight garment is worn over armour to keep the metal cool and reduce glare. It's decorated with emblems and colours, making it easy to identify the wearer in battle.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 2.00 kg \\
    \textbf{\trans{price_label}:} & 400 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N B \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{chess-rook}\hspace{0.5em}\faIcon{umbrella}\hspace{0.5em}}{}


\subsection*{Paper armor}

\begin{pexample}
The paper or the fibers of the mulberry tree are used to make the paper armor. The paper is folded several times, pressed and glued with glue. The paper sheets are formed into individual scales, which are connected by leather strips. These individual scales are used to make armor that protects the shoulders, chest, abdomen, genitals, back, and sometimes the thighs.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 5.00 kg \\
    \textbf{\trans{price_label}:} & 120 \\
    \textbf{\trans{protection_label}:} &
N N N N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{eye}\hspace{0.5em}\faIcon{chess-rook}\hspace{0.5em}\faIcon{umbrella}\hspace{0.5em}}{}


\subsection*{Tactical Vest}

\begin{pexample}
This is a lightweight, load-bearing garment made of heavy-duty nylon, often built over a mesh frame. It is designed without any inherent ballistic panels. Its entire surface, front and back, is covered in a dense grid of modular webbing and/or numerous permanently stitched pouches, intended for organizing and carrying equipment.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 2.00 kg \\
    \textbf{\trans{price_label}:} & 1200 \\
    \textbf{\trans{encumbrance_label}:} & 2 \\
    \textbf{\trans{protection_label}:} &
N N C C \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Stab-proof Vest}

\begin{pexample}
This vest is reinforced with layers of tightly woven Kevlar, specifically designed to prevent penetration by knives and other sharp objects. It's often used in prisons and by security personnel.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 1.50 kg \\
    \textbf{\trans{price_label}:} & 350 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
C B B \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{flag}\hspace{0.5em}\faIcon{plane}\hspace{0.5em}\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Hospital Gown}

\begin{pexample}
This garment is a lightweight, loose-fitting smock made of thin, pale cotton, often pale blue or bearing a simple, faded pattern. It features short, wide sleeves and is characterized by its open-back design.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 1.00 kg \\
    \textbf{\trans{price_label}:} & 30 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
B \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{flag}\hspace{0.5em}\faIcon{plane}\hspace{0.5em}\faIcon{microchip}\hspace{0.5em}\faIcon{space-shuttle}\hspace{0.5em}}{}


\subsection*{Chain mail hauberk}

\begin{pexample}
This armor is a heavy, coat-like garment made entirely of thousands of interlinked metal rings. It is shaped like a long shirt, covering the torso, shoulders, and arms, and typically falls to the mid-thigh or knees. The construction is entirely flexible, lacking the rigid plates of plate armor, and forms a dense, heavy metallic mesh.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 12.00 kg \\
    \textbf{\trans{price_label}:} & 600 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
H H N N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{eye}\hspace{0.5em}\faIcon{chess-rook}\hspace{0.5em}}{}


\subsection*{Soft Armor Concealable Vest}

\begin{pexample}
Made from soft, flexible ballistic fibres such as Kevlar, this vest is designed to protect against handguns while being thin enough to wear under clothing. It's often used by undercover police officers.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 1.00 kg \\
    \textbf{\trans{price_label}:} & 650 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{plane}\hspace{0.5em}\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Subjected Vest}

\begin{pexample}
This vest is constructed from rigid, black polymer plates integrated into a heavy-duty nylon carrier. It features multiple reinforced metal D-rings on the chest and shoulders, and the entire garment secures using heavy-duty, non-standard locking mechanisms instead of quick-release buckles. The interior is unpadded, lined only with a coarse, synthetic mesh.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 1.50 kg \\
    \textbf{\trans{price_label}:} & 900 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N B \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{flag}\hspace{0.5em}\faIcon{plane}\hspace{0.5em}\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Canvas and Leather Brigandine}

\begin{pexample}
This brigandine is made with an outer layer of canvas and metal plates sewn inside and covered with leather. The internal plates are arranged to provide flexible but solid protection, making it practical for foot soldiers.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 3.00 kg \\
    \textbf{\trans{price_label}:} & 600 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N N B \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{chess-rook}\hspace{0.5em}\faIcon{umbrella}\hspace{0.5em}}{}


\subsection*{Lorica Squamata}

\begin{pexample}
The lorica squamata  is a type of scale armour used by the ancient Roman military during the Roman Republic and at later periods. It was made from small metal scales sewn to a fabric backing.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 13.00 kg \\
    \textbf{\trans{price_label}:} & 800 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N N N N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{eye}\hspace{0.5em}}{}


\subsection*{Quilted Linen Gambeson}

\begin{pexample}
This padded jacket is made from layers of quilted linen filled with wool for extra cushioning. Worn under armour, it absorbs shock and prevents metal from rubbing against the skin.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 2.00 kg \\
    \textbf{\trans{price_label}:} & 400 \\
    \textbf{\trans{protection_label}:} &
B S \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{chess-rook}\hspace{0.5em}\faIcon{umbrella}\hspace{0.5em}}{}


\subsection*{Space Suit}

\begin{pexample}
This is a bulky, full-body garment made of multiple layers of thick, insulated fabric and reinforced polymer plates, often in white or metallic silver. It is completely sealed, featuring thick, articulated gloves and a prominent, domed helmet with a reflective, often gold-tinted, visor. A large, complex life-support unit, covered in valves and connection ports, is fixed securely to the back.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 18.00 kg \\
    \textbf{\trans{price_label}:} & 400 \\
    \textbf{\trans{encumbrance_label}:} & 2 \\
    \textbf{\trans{protection_label}:} &
N N P P \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{space-shuttle}\hspace{0.5em}}{}


\subsection*{Security Vest}

\begin{pexample}
This vest is a simple, outer-shell carrier made of durable black or dark blue nylon. It is often marked with SECURITY in large, white lettering on the front and back. The garment is secured with adjustable velcro straps at the sides and shoulders, and features several fixed pouches for a radio or flashlight, lacking the modular webbing of a tactical vest.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 2.00 kg \\
    \textbf{\trans{price_label}:} & 2000 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Flak jacket}

\begin{pexample}
This sleeveless vest is a bulky garment made of heavy-duty synthetic fabric, often in olive-drab or camouflage patterns. Its interior is filled with thick, semi-rigid panels of woven ballistic fibers. The entire vest is secured at the front or sides with heavy zippers or thick velcro straps, lacking the pockets for rigid ceramic plates seen on modern ballistic vests.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 8.00 kg \\
    \textbf{\trans{price_label}:} & 1500 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N N B B \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{plane}\hspace{0.5em}\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Tied iron sheets}

\begin{pexample}
Buford Mad Dog Tannen:
What about Monday? Are we doing anything Monday?

Buford's Gang Member \#1:
Uh, no, Monday would be fine. You can kill him on Monday.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 2.00 kg \\
    \textbf{\trans{price_label}:} & 0 \\
    \textbf{\trans{protection_label}:} &
C \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{umbrella}\hspace{0.5em}\faIcon{flag}\hspace{0.5em}}{}


\subsection*{Leather Armor}

\begin{pexample}
This armor is crafted from thick sections of hide, which have been boiled, stiffened, and stitched or riveted together. It typically consists of a rigid cuirass and shoulder guards (pauldrons), often secured with heavy leather straps and metal buckles.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 2.00 kg \\
    \textbf{\trans{price_label}:} & 200 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N N N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{chess-rook}\hspace{0.5em}\faIcon{umbrella}\hspace{0.5em}}{}


\subsection*{Ballistic vest}

\begin{pexample}
The ballistic vest consists of a heavy-duty nylon or synthetic carrier (often in black, tan, or camouflage patterns) designed to be worn over the torso. It is secured by thick velcro straps at the shoulders and sides. The interior is lined with panels of tightly woven aramid fibers, and the exterior often features prominent pouches or pockets designed to hold rigid, rectangular ceramic armor plates.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 2.00 kg \\
    \textbf{\trans{price_label}:} & 1200 \\
    \textbf{\trans{encumbrance_label}:} & 2 \\
    \textbf{\trans{protection_label}:} &
N N N C C \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Gas mask}

\begin{pexample}
Verhindert alle Effekte von Gas oder biologischen Kampfstoffen in der Luft.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 500.00 kg \\
    \textbf{\trans{price_label}:} & 200 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
P P \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{microchip}\hspace{0.5em}\faIcon{spider}\hspace{0.5em}\faIcon{fire}\hspace{0.5em}}{}


\subsection*{Lorica Segmentata}

\begin{pexample}
The lorica segmentata is a type of personal armour that was used by soldiers of the Roman Empire, consisting of metal strips (girth hoops fashioned into circular bands), fastened to internal leather straps.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 14.00 kg \\
    \textbf{\trans{price_label}:} & 800 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N N H H \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{eye}\hspace{0.5em}}{}


\subsection*{Lightweight ballistic vest}

\begin{pexample}
This vest is a thin, concealable carrier made of soft nylon or cotton, designed to be worn discreetly beneath clothing. It is secured with flat elastic and velcro straps. The interior is fitted with large, flexible panels of tightly woven aramid fibers, but it lacks the external pouches or reinforced pockets for rigid ceramic plates.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 1.00 kg \\
    \textbf{\trans{price_label}:} & 800 \\
    \textbf{\trans{encumbrance_label}:} & 2 \\
    \textbf{\trans{protection_label}:} &
N N N C \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{plane}\hspace{0.5em}\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Glitzerballerinas}

\begin{pexample}
Ballerinas. They sparkle.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 1.00 kg \\
    \textbf{\trans{price_label}:} & 50 \\
    \textbf{\trans{protection_label}:} &
B \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{flag}\hspace{0.5em}\faIcon{plane}\hspace{0.5em}\faIcon{microchip}\hspace{0.5em}\faIcon{space-shuttle}\hspace{0.5em}\faIcon{dragon}\hspace{0.5em}}{}


\subsection*{Hazmat Suit}

\begin{pexample}
A chemical protective suit is personal protective equipment that completely isolates the wearer from his environment so that he can work in radiologically, chemically or bacteriologically contaminated environments.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 10.00 kg \\
    \textbf{\trans{price_label}:} & 1000 \\
    \textbf{\trans{encumbrance_label}:} & 2 \\
    \textbf{\trans{protection_label}:} &
P P \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Fire-Resistant Flight Suit}

\begin{pexample}
This suit is made from flame resistant fabric to protect pilots and crew from burns. The suit's design includes multiple pockets for utility and an adjustable waist for comfort.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 1.00 kg \\
    \textbf{\trans{price_label}:} & 400 \\
    \textbf{\trans{protection_label}:} &
F F F \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{flag}\hspace{0.5em}\faIcon{plane}\hspace{0.5em}\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Lorica Hamata}

\begin{pexample}
The lorica hamata  is a type of chain mail armour used by soldiers for over 600 years (3rd century BC to 4th century AD) from the Roman Republic to the Roman Empire. Lorica hamata comes from the Latin hamatus (hooked) from hamus which means hook, as the rings hook into one another.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 12.00 kg \\
    \textbf{\trans{price_label}:} & 800 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N H H \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{eye}\hspace{0.5em}}{}


\section{Medium armour}



\subsection*{Kevlar vest}

\begin{pexample}
This vest consists of a simple, often concealable, carrier made of nylon or cotton. Its interior is filled with thick, dense panels made of tightly woven, yellow-gold aramid (Kevlar) fibers. The entire garment is flexible but stiff, lacking the rigid, plate-like feel of hard armor, and is typically secured with flat velcro straps.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 7.00 kg \\
    \textbf{\trans{price_label}:} & 2200 \\
    \textbf{\trans{encumbrance_label}:} & 2 \\
    \textbf{\trans{protection_label}:} &
N N N N C C \footnote{D - Protection against demonic influence, S - Shock protection, R - Reflective Protection, F - Fire Protection, P - Poison Protection, B - Bleeding Protection, H - Sticky Protection, C - Crit Protection, N - Normal Protection}\\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Hard Armor}

\begin{pexample}
This armor is a heavy, full-body encasement, consisting of large, rigid composite or ceramic plates designed to cover the torso, back, and limbs. These plates are affixed to a thick, padded aramid-fiber (Kevlar) undersuit, and the entire assembly is secured by heavy-duty locking buckles and reinforced straps. A full, enclosed helmet with a thick, transparent ballistic visor completes the suit, offering significantly more protection than a standard vest.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 10.00 kg \\
    \textbf{\trans{price_label}:} & 1600 \\
    \textbf{\trans{encumbrance_label}:} & 2 \\
    \textbf{\trans{protection_label}:} &
N N N N N C \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Lorica Plumata}

\begin{pexample}
The lorica plumata also known the lorica hamata squamatque was a set of Roman armor. The name Lorica Plumata translates to feathered curiass. The reason the armor has this armor had this name, is because it had a feathered appearance due to the feather-like scales called plumes attached to oval shaped rings.The Lorica Plumata was a sleeveless armor with no shoulder guards that looked like a Linothorax. The Lorica plumata was one of the few sets of armor that combined mail and scales.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 17.00 kg \\
    \textbf{\trans{price_label}:} & 800 \\
    \textbf{\trans{encumbrance_label}:} & 2 \\
    \textbf{\trans{protection_label}:} &
N N N N H H H \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{eye}\hspace{0.5em}}{}


\subsection*{Half-Plate}

\begin{pexample}
This armor consists of a set of articulated, forged steel plates - including a solid cuirass, backplate, and large pauldrons - designed to protect the torso and upper body. It is distinguished from full plate by its omission of full leg and arm encasement, relying instead on mail or hardened leather to protect the joints and lower limbs.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 13.00 kg \\
    \textbf{\trans{price_label}:} & 800 \\
    \textbf{\trans{encumbrance_label}:} & 2 \\
    \textbf{\trans{protection_label}:} &
N N N N N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{eye}\hspace{0.5em}\faIcon{chess-rook}\hspace{0.5em}}{}


\subsection*{Cuirass}

\begin{pexample}
The iron cuirass is made from iron plates with a fitted, flared shape around the waist. Its smooth, rounded surfaces help to deflect blows to the chest, providing both protection and a sleek aesthetic.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 3.00 kg \\
    \textbf{\trans{price_label}:} & 1200 \\
    \textbf{\trans{encumbrance_label}:} & 4 \\
    \textbf{\trans{protection_label}:} &
N N N N C \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{chess-rook}\hspace{0.5em}\faIcon{umbrella}\hspace{0.5em}}{}


\subsection*{Reinforced Iron Plackart}

\begin{pexample}
This lower chest plate is made of reinforced iron and protects the stomach and lower ribs. It is attached to a cuirass to form a continuous barrier against attacks to the torso.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 3.00 kg \\
    \textbf{\trans{price_label}:} & 500 \\
    \textbf{\trans{encumbrance_label}:} & 3 \\
    \textbf{\trans{protection_label}:} &
N N C C C \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{chess-rook}\hspace{0.5em}\faIcon{umbrella}\hspace{0.5em}}{}


\subsection*{Ceramic Plate Carrier Vest}

\begin{pexample}
This vest has pockets for inserting ceramic plates that stop high velocity rifle bullets. The outer shell is made of tear-resistant fabric with webbing for attaching pouches and accessories.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 4.00 kg \\
    \textbf{\trans{price_label}:} & 800 \\
    \textbf{\trans{encumbrance_label}:} & 2 \\
    \textbf{\trans{protection_label}:} &
N N C C C \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Shock-Absorbing Tactical Vest Liner}

\begin{pexample}
Made from breathable foam and mesh, this liner is inserted into the vest for added comfort and ventilation. It absorbs shock and prevents bruising from impact with armour plates.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 2.00 kg \\
    \textbf{\trans{price_label}:} & 300 \\
    \textbf{\trans{encumbrance_label}:} & 2 \\
    \textbf{\trans{protection_label}:} &
S S \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Hard Plate Armor Inserts}

\begin{pexample}
Made from hardened polyethylene or ceramic, these side plates fit into plate carriers to protect the ribs and lower torso. They provide a high level of ballistic protection without adding excessive weight.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 2.00 kg \\
    \textbf{\trans{price_label}:} & 600 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Plasma-Infused Chest Plate}

\begin{pexample}
Chest plate with plasma gel to absorb and dissipate energy from lasers and plasma weapons.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 8.00 kg \\
    \textbf{\trans{price_label}:} & 3500 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N N S S S \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{space-shuttle}\hspace{0.5em}}{}


\subsection*{Laser-Dampening Chest Armor}

\begin{pexample}
Chest armour with reflective coating to dissipate laser energy and reduce burns.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 8.20 kg \\
    \textbf{\trans{price_label}:} & 4000 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N R R R \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{space-shuttle}\hspace{0.5em}}{}


\subsection*{Thermal-Absorbing Vest}

\begin{pexample}
A waistcoat with heat-absorbing material to reduce the effects of heat.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 3.20 kg \\
    \textbf{\trans{price_label}:} & 3000 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
F F F F F \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{space-shuttle}\hspace{0.5em}}{}


\subsection*{Spartan Bronze Cuirass}

\begin{pexample}
A solid bronze cuirass designed to fit around the torso, it provided sturdy protection for Greek soldiers.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 7.50 kg \\
    \textbf{\trans{price_label}:} & 750 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N N N N C \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{eye}\hspace{0.5em}}{}


\subsection*{Scale Armor Vest}

\begin{pexample}
A vest made of overlapping bronze scales.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 5.50 kg \\
    \textbf{\trans{price_label}:} & 700 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N N N H \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{eye}\hspace{0.5em}}{}


\subsection*{Iron Lamellar Armor}

\begin{pexample}
A piece of armour made of small iron plates that are laced together.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 8.00 kg \\
    \textbf{\trans{price_label}:} & 900 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N N N N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{eye}\hspace{0.5em}}{}


\section{Heavy armour}



\subsection*{Plate Armor}

\begin{pexample}
A polished, form-fitting shell of interlocking, articulated steel plates, covering the wearer from head to toe, defines this armor. It includes a full helm, a solid cuirass, and defenses for the arms and legs, all meticulously shaped. This suit, often worn over a padded gambeson or mail, is secured by numerous internal straps and buckles, creating a complete, heavy encasement.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 15.00 kg \\
    \textbf{\trans{price_label}:} & 2000 \\
    \textbf{\trans{encumbrance_label}:} & 4 \\
    \textbf{\trans{protection_label}:} &
N N N N N C C C C C \footnote{D - Protection against demonic influence, S - Shock protection, R - Reflective Protection, F - Fire Protection, P - Poison Protection, B - Bleeding Protection, H - Sticky Protection, C - Crit Protection, N - Normal Protection}\\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{chess-rook}\hspace{0.5em}}{}


\subsection*{Heavy ballistic vest}

\begin{pexample}
The heavy ballistic vest is a bulky, full-torso carrier made of heavy-duty nylon, designed to hold thick, multi-curve ceramic plates in the front, back, and sides. It is distinguished by its additional, often detachable, armored components, such as a reinforced gorget (neck guard), large shoulder pauldrons, and a hanging groin protector, providing extensive coverage at the cost of mobility.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 4.00 kg \\
    \textbf{\trans{price_label}:} & 1800 \\
    \textbf{\trans{encumbrance_label}:} & 4 \\
    \textbf{\trans{protection_label}:} &
N N N N N N N C C \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Combined tactical vest}

\begin{pexample}
This modern vest features a heavy-duty nylon carrier with integrated pouches for rigid armor plates. Its defining feature is the extensive, built-in webbing covering the front, back, and sides, designed to combine ballistic protection with a fully modular load-bearing system for pouches and gear.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 8.00 kg \\
    \textbf{\trans{price_label}:} & 2800 \\
    \textbf{\trans{encumbrance_label}:} & 4 \\
    \textbf{\trans{protection_label}:} &
N N N C C C B B \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Infantry Battle Suit}

\begin{pexample}
This full-body armor consists of interlocking, matte-finished composite plates (often in olive-drab or grey) worn over a sealed, synthetic undersuit. It features a full-face, enclosed helmet with a rectangular, multi-spectrum visor. The entire suit is covered in a modular webbing system for attaching ammunition pouches and utility gear, and is powered by a flat, rectangular power pack integrated into the backplate.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 18.00 kg \\
    \textbf{\trans{price_label}:} & 2200 \\
    \textbf{\trans{encumbrance_label}:} & 4 \\
    \textbf{\trans{protection_label}:} &
N N N N N C C C C \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{space-shuttle}\hspace{0.5em}}{}


\subsection*{Powered Battlesuit}

\begin{pexample}
A heavy, articulated frame of dark alloys and composite plating forms this full-body exoskeleton, standing significantly taller and broader than a normal person. It features a sealed, reflective helmet/visor, oversized pauldrons, and a prominent, rear-mounted power core. Thick bundles of synthetic muscle or hydraulic pistons are visible at the major joints, such as the elbows, knees, and waist.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 22.00 kg \\
    \textbf{\trans{price_label}:} & 5000 \\
    \textbf{\trans{encumbrance_label}:} & 4 \\
    \textbf{\trans{protection_label}:} &
N N C C P P B B F F \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{space-shuttle}\hspace{0.5em}}{}


\subsection*{Ulrich's plate armour}

\begin{pexample}
This armour was made by a master blacksmith named Ulrich. It has increased resistance.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 15.00 kg \\
    \textbf{\trans{price_label}:} & 5000 \\
    \textbf{\trans{encumbrance_label}:} & 4 \\
    \textbf{\trans{protection_label}:} &
N N N N N C \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{chess-rook}\hspace{0.5em}}{}


\subsection*{Carbon-Nanotube Exoskeleton Suit}

\begin{pexample}
A full-body carbon nanotube exoskeleton that increases strength and agility while providing high ballistic resistance.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 20.50 kg \\
    \textbf{\trans{price_label}:} & 11000 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N N C C C C C B F \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{space-shuttle}\hspace{0.5em}}{}


\subsection*{Synthetic Power Armor}

\begin{pexample}
Power armour lined with synthetic fibres that increase the wearer's strength.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 25.00 kg \\
    \textbf{\trans{price_label}:} & 11000 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N N N N C C C C C \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{space-shuttle}\hspace{0.5em}}{}


\subsection*{Iron Muscle Cuirass}

\begin{pexample}
An iron cuirass sculpted to show idealised muscles, providing both protection and an imposing appearance.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 9.00 kg \\
    \textbf{\trans{price_label}:} & 1200 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N N N N C C C \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{eye}\hspace{0.5em}}{}


\section{Clothing}



\subsection*{Normal clothing}

\begin{pexample}
This set of apparel consists of simple, practical garments made from common fabrics like linen, wool, or cotton. It typically includes a basic shirt or tunic, a pair of trousers or a skirt, and perhaps a simple leather belt. The clothing is functional and unadorned, lacking any form of padding, armor, or specialized design.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 1.50 kg \\
    \textbf{\trans{price_label}:} & 200 \\
    \textbf{\trans{protection_label}:} &
N \footnote{D - Protection against demonic influence, S - Shock protection, R - Reflective Protection, F - Fire Protection, P - Poison Protection, B - Bleeding Protection, H - Sticky Protection, C - Crit Protection, N - Normal Protection}\\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{cube}\hspace{0.5em}}{}


\subsection*{Two-piece Suit}

\begin{pexample}
This set consists of a tailored jacket and matching trousers, both crafted from an exceptionally fine, dark wool or silk, giving the fabric a subtle, lustrous sheen. The cut is precise and sharp, featuring hand-stitched lapels and functional cuff buttons. The jacket is fully lined with a smooth, high-quality silk.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 0.80 kg \\
    \textbf{\trans{price_label}:} & 1200 \\
    \textbf{\trans{protection_label}:} &
N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{umbrella}\hspace{0.5em}\faIcon{flag}\hspace{0.5em}\faIcon{plane}\hspace{0.5em}\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Robe}

\begin{pexample}
A floor-length, single-piece garment of heavy, single-colored fabric (often black, white, or deep red). Its most distinct features are the exceptionally wide, bell-shaped sleeves and a deep, oversized hood designed to shadow the face.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 4.00 kg \\
    \textbf{\trans{price_label}:} & 120 \\
    \textbf{\trans{protection_label}:} &
B \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{cube}\hspace{0.5em}}{}


\subsection*{Trenchcoat}

\begin{pexample}
This is a long overcoat, typically knee-length or longer, cut from heavy-duty, water-resistant fabric like gabardine, often in a tan, black, or olive-drab color. It features a double-breasted front, wide lapels, and a prominent belt of the same material, which is cinched with a buckle. Distinctive details include storm flaps, epaulets on the shoulders, and buckled straps at the cuffs.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 2.00 kg \\
    \textbf{\trans{price_label}:} & 299 \\
    \textbf{\trans{protection_label}:} &
N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{plane}\hspace{0.5em}\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Tunic}

\begin{pexample}
The Tunic is crafted from a basic weave, typically linen, cotton, or wool. It falls from the shoulders to somewhere between the hips and the knees, featuring two simple sleeves and a basic, round or V-shaped opening for the head.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 3.00 kg \\
    \textbf{\trans{price_label}:} & 120 \\
    \textbf{\trans{protection_label}:} &
N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{eye}\hspace{0.5em}\faIcon{chess-rook}\hspace{0.5em}}{}


\subsection*{Victorian gentleman clothing}

\begin{pexample}
Chic but unobtrusive dress with hat, tailcoat, shirt, trousers, belt and boots.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 3.00 kg \\
    \textbf{\trans{price_label}:} & 500 \\
    \textbf{\trans{protection_label}:} &
N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{umbrella}\hspace{0.5em}}{}


\subsection*{Gown}

\begin{pexample}
This garment is a simple, loose-fitting outer robe made of coarse, heavy fabric like linen or wool. It is long-sleeved and typically reaches the ankles, designed to be worn over other clothing. It is secured at the front with simple fabric ties or a basic belt, lacking any complex fasteners or ornamentation.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 2.00 kg \\
    \textbf{\trans{price_label}:} & 20 \\
    \textbf{\trans{protection_label}:} &
B \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{cube}\hspace{0.5em}}{}


\subsection*{Adaptive Camouflage Bodysuit}

\begin{pexample}
Bodysuit that uses nanofibres to mimic the environment, making the wearer virtually invisible.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 3.00 kg \\
    \textbf{\trans{price_label}:} & 5000 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
S \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{space-shuttle}\hspace{0.5em}}{}


\subsection*{Thermal-Regulating Bodysuit}

\begin{pexample}
A suit that regulates temperature to keep the wearer comfortable in extreme climates.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 2.00 kg \\
    \textbf{\trans{price_label}:} & 1500 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
F F \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{space-shuttle}\hspace{0.5em}}{}


\subsection*{Photon-Refracting Cloak}

\begin{pexample}
A cloak that bends light to make the wearer invisible, ideal for stealth missions.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 0.70 kg \\
    \textbf{\trans{price_label}:} & 7500 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
C \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{space-shuttle}\hspace{0.5em}}{}


\subsection*{Synthetic Fiber Stealth Suit}

\begin{pexample}
A bodysuit that muffles the sound of movement, making it easier to infiltrate silently.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 3.00 kg \\
    \textbf{\trans{price_label}:} & 5000 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N N N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{space-shuttle}\hspace{0.5em}}{}


\subsection*{Leather Pteruges Skirt}

\begin{pexample}
A skirt made of leather strips that hangs from the waist to protect the thighs while allowing movement.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 1.80 kg \\
    \textbf{\trans{price_label}:} & 200 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N C \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{eye}\hspace{0.5em}}{}


\subsection*{Leather Sandals with Reinforced Soles}

\begin{pexample}
Sturdy leather sandals with reinforced soles, worn by soldiers on long marches.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 0.80 kg \\
    \textbf{\trans{price_label}:} & 80 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{eye}\hspace{0.5em}}{}


\subsection*{Fancy dress}

\begin{pexample}
A really chic dress, in any color.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 1.50 kg \\
    \textbf{\trans{price_label}:} & 250 \\
    \textbf{\trans{protection_label}:} &
B \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{cube}\hspace{0.5em}}{}


\section{Arms and Legs}



\subsection*{Bronze Vambrace}

\begin{pexample}
A bronze forearm guard to deflect blows and reduce injury to the arm.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 1.20 kg \\
    \textbf{\trans{price_label}:} & 150 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N \footnote{D - Protection against demonic influence, S - Shock protection, R - Reflective Protection, F - Fire Protection, P - Poison Protection, B - Bleeding Protection, H - Sticky Protection, C - Crit Protection, N - Normal Protection}\\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{eye}\hspace{0.5em}}{}


\subsection*{Leather shoes}

\begin{pexample}
Laced leather shoes
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 1.00 kg \\
    \textbf{\trans{price_label}:} & 70 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{chess-rook}\hspace{0.5em}\faIcon{umbrella}\hspace{0.5em}\faIcon{flag}\hspace{0.5em}}{}


\subsection*{Poleyns with Hinged Plates}

\begin{pexample}
Made from iron, these knee guards have a hinged design that allows the wearer to move freely while still protecting the knee joint. Their rounded shape helps to deflect blows to this vulnerable area.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 2.00 kg \\
    \textbf{\trans{price_label}:} & 150 \\
    \textbf{\trans{protection_label}:} &
C \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{chess-rook}\hspace{0.5em}\faIcon{umbrella}\hspace{0.5em}}{}


\subsection*{Wool gloves}

\begin{pexample}
Wool gloves protect your hands from cuts and cold.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 0.50 kg \\
    \textbf{\trans{price_label}:} & 20 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
B N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{cube}\hspace{0.5em}}{}


\subsection*{Powered Kneecap Armor}

\begin{pexample}
Knee pads reinforced with shock absorbing material for highly mobile soldiers.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 2.00 kg \\
    \textbf{\trans{price_label}:} & 1000 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
S S \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{space-shuttle}\hspace{0.5em}}{}


\subsection*{Carbon-Fiber Exoskeletal Spine}

\begin{pexample}
A carbon fibre spinal exoskeleton for back support.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 4.50 kg \\
    \textbf{\trans{price_label}:} & 3000 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
S S \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{space-shuttle}\hspace{0.5em}}{}


\subsection*{Ballistic Groin Protector}

\begin{pexample}
This Kevlar-based protector is designed to protect the groin area from shrapnel and small arms fire. It attaches to vests to provide additional lower body protection, especially in high threat environments.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 0.50 kg \\
    \textbf{\trans{price_label}:} & 200 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
C \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{flag}\hspace{0.5em}\faIcon{plane}\hspace{0.5em}\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Steel-Toe Combat Boots}

\begin{pexample}
These boots have steel reinforcement in the toe area to protect against crushing injuries. The soles are slip resistant and the uppers are made from waterproof leather for durability in a variety of environments.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 2.00 kg \\
    \textbf{\trans{price_label}:} & 120 \\
    \textbf{\trans{protection_label}:} &
N N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{flag}\hspace{0.5em}\faIcon{plane}\hspace{0.5em}\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Pauldrons with Wing Extensions}

\begin{pexample}
These large shoulder protectors are made from iron and have flared wing extensions for extra coverage of the neck and upper arms. The curved design deflects blows away from vital areas.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 2.00 kg \\
    \textbf{\trans{price_label}:} & 150 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
C C \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{chess-rook}\hspace{0.5em}\faIcon{umbrella}\hspace{0.5em}}{}


\subsection*{Ballistic Elbow Pads}

\begin{pexample}
Made from ballistic nylon and dense foam, these elbow pads absorb impact and protect against cuts. They’re designed to withstand high wear and tear and offer flexibility for tactical operations.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 0.50 kg \\
    \textbf{\trans{price_label}:} & 200 \\
    \textbf{\trans{protection_label}:} &
N N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{flag}\hspace{0.5em}\faIcon{plane}\hspace{0.5em}\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Armored Shoulder Plates}

\begin{pexample}
Lightweight composite shoulder armour for upper body protection.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 3.00 kg \\
    \textbf{\trans{price_label}:} & 1000 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{space-shuttle}\hspace{0.5em}}{}


\subsection*{Greek Bronze Greaves}

\begin{pexample}
Bronze guards worn on the shins to protect against blows and rough terrain.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 2.20 kg \\
    \textbf{\trans{price_label}:} & 400 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{eye}\hspace{0.5em}}{}


\subsection*{Iron Gauntlets}

\begin{pexample}
These gauntlets are constructed from small, overlapping iron plates that allow each finger to move independently. Reinforced knuckles protect the hands from direct blows, while still allowing for dexterity when wielding weapons.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 2.00 kg \\
    \textbf{\trans{price_label}:} & 200 \\
    \textbf{\trans{encumbrance_label}:} & 2 \\
    \textbf{\trans{protection_label}:} &
N N N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{chess-rook}\hspace{0.5em}\faIcon{umbrella}\hspace{0.5em}}{}


\subsection*{Antigravity Combat Boots}

\begin{pexample}
Boots equipped with antigravity generators for brief levitation and shock-absorbing landings.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 3.50 kg \\
    \textbf{\trans{price_label}:} & 4500 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
S S S \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{space-shuttle}\hspace{0.5em}}{}


\subsection*{Neural-Linked Gauntlets}

\begin{pexample}
Gauntlets connected to the neural interface, allowing you to control gadgets with thought commands.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 1.00 kg \\
    \textbf{\trans{price_label}:} & 2000 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{space-shuttle}\hspace{0.5em}}{}


\subsection*{Silk gloves}

\begin{pexample}
These gloves are made from fine, tightly-woven silk thread, resulting in a smooth, lustrous surface. They are exceptionally thin and lightweight, tailored to fit the hands and fingers snugly. The stitching is delicate and precise, almost invisible on the smooth fabric.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 0.20 kg \\
    \textbf{\trans{price_label}:} & 40 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{cube}\hspace{0.5em}}{}


\subsection*{Iron Spaulders}

\begin{pexample}
These shoulderguards are made of iron with decorative etching along the edges. They curve over the shoulders and connect to the upper arm armour, providing coverage without restricting arm movement.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 1.00 kg \\
    \textbf{\trans{price_label}:} & 200 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{chess-rook}\hspace{0.5em}\faIcon{umbrella}\hspace{0.5em}}{}


\subsection*{Iron Sabatons}

\begin{pexample}
These boots are forged from blackened iron to resist rust. The sabatons are articulated for flexible movement, while the pointed toes add a touch of intimidating style.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 2.00 kg \\
    \textbf{\trans{price_label}:} & 250 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{chess-rook}\hspace{0.5em}\faIcon{umbrella}\hspace{0.5em}}{}


\subsection*{Shock-Resistant Boots}

\begin{pexample}
Electric shock resistant boots with rubber and synthetic layers.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 3.50 kg \\
    \textbf{\trans{price_label}:} & 2000 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
S S S \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{space-shuttle}\hspace{0.5em}}{}


\subsection*{Nanoweave Covert Gloves}

\begin{pexample}
Nanofibre gloves for enhanced dexterity and grip.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 0.50 kg \\
    \textbf{\trans{price_label}:} & 500 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{space-shuttle}\hspace{0.5em}}{}


\subsection*{Laser-Deflecting Wrist Guards}

\begin{pexample}
Wrist guards with reflective coating to deflect laser attacks.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 1.00 kg \\
    \textbf{\trans{price_label}:} & 1000 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
R R \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{space-shuttle}\hspace{0.5em}}{}


\subsection*{Ballistic Knee Pads}

\begin{pexample}
These knee pads have a ballistic nylon exterior and memory foam interior for comfort. They're designed for high shock absorption and flexibility, allowing for easy movement in rugged terrain.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 1.00 kg \\
    \textbf{\trans{price_label}:} & 150 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
C \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{flag}\hspace{0.5em}\faIcon{plane}\hspace{0.5em}\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Electromagnetic Repulsor Gloves}

\begin{pexample}
Gloves that generate an electromagnetic field to repel small metal objects.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 1.50 kg \\
    \textbf{\trans{price_label}:} & 3500 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N N N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{space-shuttle}\hspace{0.5em}}{}


\subsection*{Bronze Arm Guard}

\begin{pexample}
Bronze guard worn on the upper arm.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 1.00 kg \\
    \textbf{\trans{price_label}:} & 200 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{eye}\hspace{0.5em}}{}


\subsection*{Leather Gauntlet}

\begin{pexample}
A thick leather glove that protects hands and wrists from cuts and impacts.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 0.50 kg \\
    \textbf{\trans{price_label}:} & 90 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{eye}\hspace{0.5em}}{}


\subsection*{Reinforced Kevlar Tactical Pants}

\begin{pexample}
These trousers have Kevlar panels sewn into the knees and thighs to protect against abrasions and cuts. They're durable and ideal for rugged environments where lower body protection is essential.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 0.70 kg \\
    \textbf{\trans{price_label}:} & 100 \\
    \textbf{\trans{protection_label}:} &
B \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{plane}\hspace{0.5em}\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Iron-Plated Tassets}

\begin{pexample}
These thigh protectors are made of iron plates that hang from the waist to cover the thighs. Their overlapping design allows for mobility while effectively shielding the thighs from blows.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 1.00 kg \\
    \textbf{\trans{price_label}:} & 150 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N C \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{chess-rook}\hspace{0.5em}\faIcon{umbrella}\hspace{0.5em}}{}


\subsection*{Blast-Resistant Combat Gloves}

\begin{pexample}
Made from Kevlar and reinforced with rubber padding at the knuckles, these gloves offer both cut and blast resistance. They're designed to allow dexterity while protecting against fire and shrapnel.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 1.00 kg \\
    \textbf{\trans{price_label}:} & 35 \\
    \textbf{\trans{protection_label}:} &
N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{flag}\hspace{0.5em}\faIcon{plane}\hspace{0.5em}\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Iron Rerebrace}

\begin{pexample}
Covering the upper arm, this piece of armour is made from iron and secured with leather straps. Its curved shape follows the natural contours of the arm, providing robust protection without restricting movement.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 1.00 kg \\
    \textbf{\trans{price_label}:} & 150 \\
    \textbf{\trans{protection_label}:} &
N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{chess-rook}\hspace{0.5em}\faIcon{umbrella}\hspace{0.5em}}{}


\subsection*{Iron Greaves}

\begin{pexample}
Protective iron guards for the lower legs, worn by soldiers to shield from strikes and debris.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 2.40 kg \\
    \textbf{\trans{price_label}:} & 300 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{eye}\hspace{0.5em}}{}


\subsection*{Energy-Absorbing Arm Guards}

\begin{pexample}
Armguards embedded with materials to absorb impact and protect the forearms.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 1.50 kg \\
    \textbf{\trans{price_label}:} & 2000 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{space-shuttle}\hspace{0.5em}}{}


\section{Head and Throat}



\subsection*{Polycarbonate Visor}

\begin{pexample}
This visor attaches to helmets to protect the face from thrown objects and non-lethal projectiles. Its polycarbonate construction is lightweight, impact resistant and easy to clean after exposure to contaminants.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 0.80 kg \\
    \textbf{\trans{price_label}:} & 250 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
C \footnote{D - Protection against demonic influence, S - Shock protection, R - Reflective Protection, F - Fire Protection, P - Poison Protection, B - Bleeding Protection, H - Sticky Protection, C - Crit Protection, N - Normal Protection}\\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{EMP-Shielded Helmet}

\begin{pexample}
A helmet with reinforced electronics to withstand electromagnetic pulses.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 2.20 kg \\
    \textbf{\trans{price_label}:} & 3500 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
S S S \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{space-shuttle}\hspace{0.5em}}{}


\subsection*{Iron Bevor}

\begin{pexample}
This neck and lower face guard is made from a single piece of iron that curves upwards to cover the chin and jawline. It fits underneath the helmet, protecting vulnerable areas such as the throat and allowing for freedom of movement.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 2.00 kg \\
    \textbf{\trans{price_label}:} & 150 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
C C \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{chess-rook}\hspace{0.5em}\faIcon{umbrella}\hspace{0.5em}}{}


\subsection*{Carbon Fiber Face Shield}

\begin{pexample}
This face shield is made from lightweight carbon fibre with an anti-fog coating. It provides impact protection for the face and is often used in tactical and riot situations where visibility is critical.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 0.80 kg \\
    \textbf{\trans{price_label}:} & 120 \\
    \textbf{\trans{protection_label}:} &
C \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{plane}\hspace{0.5em}\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Carbon Fiber Combat Helmet}

\begin{pexample}
The helmet is made from carbon fibre and offers a lightweight alternative to traditional Kevlar helmets. It provides ballistic resistance and includes mounts for accessories such as cameras or flashlights.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 1.00 kg \\
    \textbf{\trans{price_label}:} & 650 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N C \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{plane}\hspace{0.5em}\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Smart Helmet with Integrated Comms}

\begin{pexample}
A helmet equipped with integrated communication systems for field communication.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 2.50 kg \\
    \textbf{\trans{price_label}:} & 700 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{space-shuttle}\hspace{0.5em}}{}


\subsection*{Graphene-Armored Helmet with HUD}

\begin{pexample}
Graphene helmet with heads-up display showing real-time tactical and health metrics.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 1.80 kg \\
    \textbf{\trans{price_label}:} & 2500 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{space-shuttle}\hspace{0.5em}}{}


\subsection*{Plumed Bronze Helm}

\begin{pexample}
A bronze helmet with an impressive crest, designed to intimidate enemies and protect the head.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 2.80 kg \\
    \textbf{\trans{price_label}:} & 600 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{eye}\hspace{0.5em}}{}


\subsection*{Chainmail Aventail}

\begin{pexample}
This aventail is made of interlinked iron rings and hangs from the helmet to cover the neck and shoulders. It provides extra protection for the neck while allowing flexible movement.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 1.00 kg \\
    \textbf{\trans{price_label}:} & 150 \\
    \textbf{\trans{protection_label}:} &
H \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{chess-rook}\hspace{0.5em}\faIcon{umbrella}\hspace{0.5em}}{}


\subsection*{Kettle hat}

\begin{pexample}
The helmet has a wide, flaring brim, giving it the appearance of a cooking pot. Made entirely of iron, it shields the head from above while deflecting rain and sunlight from the face.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 1.00 kg \\
    \textbf{\trans{price_label}:} & 200 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{chess-rook}\hspace{0.5em}\faIcon{umbrella}\hspace{0.5em}}{}


\subsection*{Padded Cloth Coif}

\begin{pexample}
Made from padded fabric and worn under a helmet for added comfort and shock absorption. It covers the head and neck, providing an extra layer of defence against blows.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 0.20 kg \\
    \textbf{\trans{price_label}:} & 50 \\
    \textbf{\trans{protection_label}:} &
B \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{chess-rook}\hspace{0.5em}\faIcon{umbrella}\hspace{0.5em}}{}


\subsection*{Chainmail Coif}

\begin{pexample}
This coif consists of interlocking iron rings that form a hood-like structure covering the head, neck and shoulders. It's worn under a helmet to provide additional protection to areas that might otherwise be exposed.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 1.50 kg \\
    \textbf{\trans{price_label}:} & 250 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N H \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{eye}\hspace{0.5em}\faIcon{chess-rook}\hspace{0.5em}\faIcon{umbrella}\hspace{0.5em}}{}


\subsection*{Quantum-Reactive Helmet}

\begin{pexample}
Helmet with quantum sensors that predict threats and emit a brief energy shield to deflect attacks.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 2.50 kg \\
    \textbf{\trans{price_label}:} & 3000 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
S S R R \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{space-shuttle}\hspace{0.5em}}{}


\subsection*{Bronze Corinthian Helmet}

\begin{pexample}
A bronze helmet with a sloping nose guard and cheek pieces, providing strong protection for the head.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 2.30 kg \\
    \textbf{\trans{price_label}:} & 500 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{eye}\hspace{0.5em}}{}


\subsection*{Transparent Nanofilm Visor}

\begin{pexample}
A virtually indestructible nanofilm visor that protects against bullets and bright light.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 0.50 kg \\
    \textbf{\trans{price_label}:} & 2500 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
S S \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{space-shuttle}\hspace{0.5em}}{}


\subsection*{Leather Bascinet Helmet}

\begin{pexample}
Made from boiled leather, this helmet has a rounded, pointed shape with a visor for extra face protection. The leather material is lighter than metal but still offers decent protection, and the visor can be lifted for better visibility.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 0.50 kg \\
    \textbf{\trans{price_label}:} & 150 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{chess-rook}\hspace{0.5em}\faIcon{umbrella}\hspace{0.5em}}{}


\subsection*{Ballistic Neck Collar}

\begin{pexample}
Made from layered Kevlar, this collar wraps around the neck to provide ballistic protection from shrapnel and small arms fire. It attaches to tactical vests for secure neck coverage.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 1.00 kg \\
    \textbf{\trans{price_label}:} & 120 \\
    \textbf{\trans{encumbrance_label}:} & 2 \\
    \textbf{\trans{protection_label}:} &
C \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{plane}\hspace{0.5em}\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Iron Gorget}

\begin{pexample}
Made from thick iron, this neck guard wraps around the throat to prevent injury from slashes and thrusts. It fits snugly around the neck and attaches to the upper armour, providing continuous defence.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 1.00 kg \\
    \textbf{\trans{price_label}:} & 300 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
C C \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{chess-rook}\hspace{0.5em}\faIcon{umbrella}\hspace{0.5em}}{}


\subsection*{Acoustic Dampening Helm}

\begin{pexample}
A helmet equipped with acoustic dampeners to protect hearing from explosions.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 2.30 kg \\
    \textbf{\trans{price_label}:} & 1000 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
S S S \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{space-shuttle}\hspace{0.5em}}{}


\subsection*{Tactical Helmet}

\begin{pexample}
This helmet is made from multiple layers of Kevlar to provide ballistic protection against small calibre bullets and shrapnel. It includes a four-point harness for a secure fit and is compatible with night vision equipment.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 1.00 kg \\
    \textbf{\trans{price_label}:} & 1000 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{plane}\hspace{0.5em}\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Bronze Boeotian Helmet}

\begin{pexample}
A bronze helmet with a rounded top and cheekguards, popular with Greek cavalry.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 2.00 kg \\
    \textbf{\trans{price_label}:} & 480 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N C \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{eye}\hspace{0.5em}}{}


\subsection*{Ballistic Eyewear}

\begin{pexample}
These goggles are made from polycarbonate lenses to protect your eyes from shrapnel and debris. Frames are typically padded for comfort and feature anti-fog and scratch-resistant coatings.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 0.30 kg \\
    \textbf{\trans{price_label}:} & 450 \\
    \textbf{\trans{protection_label}:} &
C C \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{plane}\hspace{0.5em}\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Brass-Crested Burgonet Helmet}

\begin{pexample}
The helmet has an open face with a small brass crest on top and cheek plates on the sides. The rounded shape of the helmet deflects blows, while the brass detailing adds a touch of grandeur.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 2.00 kg \\
    \textbf{\trans{price_label}:} & 350 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
N N N \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{chess-rook}\hspace{0.5em}\faIcon{umbrella}\hspace{0.5em}}{}


\subsection*{Fire Resistant Balaclava}

\begin{pexample}
Made from flame-resistant fabric, this balaclava covers the head and neck to protect against burns. It's often worn under helmets by firefighters and SWAT teams for thermal protection.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 0.50 kg \\
    \textbf{\trans{price_label}:} & 200 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
B F \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{flag}\hspace{0.5em}\faIcon{plane}\hspace{0.5em}\faIcon{microchip}\hspace{0.5em}}{}


\section{Shield}



\subsection*{Roundshield}

\begin{pexample}
This large, circular shield is constructed from thick wooden planks, often faced with stretched leather and bound by a heavy iron rim. A prominent, domed steel boss (umbo) sits at the exact center. This boss protects the wielder's hand, which grips a single horizontal bar directly behind it, a design distinct from the arm-straps of a kite shield.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 2.50 kg \\
    \textbf{\trans{price_label}:} & 500 \\
    \textbf{\trans{encumbrance_label}:} & 2 \\
    \textbf{\trans{protection_label}:} &
\footnote{D - Protection against demonic influence, S - Shock protection, R - Reflective Protection, F - Fire Protection, P - Poison Protection, B - Bleeding Protection, H - Sticky Protection, C - Crit Protection, N - Normal Protection}\\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{eye}\hspace{0.5em}\faIcon{chess-rook}\hspace{0.5em}}{}


\subsection*{Personal protection shield Standard}

\begin{pexample}
The Standard Personal Protection Shield was developed in conjunction with emergency responders with the goal of achieving an ideal blend between handling, weight, size and modularity. The shield provides protection against the most common threats.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 11.00 kg \\
    \textbf{\trans{price_label}:} & 800 \\
    \textbf{\trans{encumbrance_label}:} & 3 \\
    \textbf{\trans{protection_label}:} &
\\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{plane}\hspace{0.5em}\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Personal Protection Shield XUR-ASIA}

\begin{pexample}
Einsatzschild gegen leichte Gefahren durch Faustfeuerwaffen. Auch geeignet für den Einsatz bei Ausschreitungen oder bei der Strafverfolgung. Das ballistische Visierfenster ist austauschbar.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 10.00 kg \\
    \textbf{\trans{price_label}:} & 1200 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
\\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{plane}\hspace{0.5em}\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Tower shield}

\begin{pexample}
An enormous, heavy shield, built to be almost as tall as a person. Its shape is typically rectangular or a large, elongated oval, often curved to wrap slightly around the body. The construction is of thick, reinforced wood, frequently faced with leather and bound in metal, and it is secured by a series-of heavy straps for the arm and hand.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 11.00 kg \\
    \textbf{\trans{price_label}:} & 1200 \\
    \textbf{\trans{encumbrance_label}:} & 4 \\
    \textbf{\trans{protection_label}:} &
\\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{eye}\hspace{0.5em}\faIcon{chess-rook}\hspace{0.5em}}{}


\subsection*{Buckler}

\begin{pexample}
A small, round disc of steel or hardened leather, often no wider than a forearm's length, defines this shield. Its primary feature is a prominent, central metal boss which protects a simple bar grip held directly behind it in the fist. It lacks the arm-straps found on larger kite or heater shields.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 4.00 kg \\
    \textbf{\trans{price_label}:} & 200 \\
    \textbf{\trans{protection_label}:} &
\\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{eye}\hspace{0.5em}\faIcon{chess-rook}\hspace{0.5em}}{}


\subsection*{Polycarbonate Riot Shield}

\begin{pexample}
Constructed from a transparent polycarbonate material, the shield provides impact resistance against thrown objects, blunt force and non-lethal projectiles. Its lightweight design allows for easy manoeuvrability in crowd control situations.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 2.00 kg \\
    \textbf{\trans{price_label}:} & 300 \\
    \textbf{\trans{encumbrance_label}:} & 3 \\
    \textbf{\trans{protection_label}:} &
\\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Aluminum Armored Shield with Transparent Window}

\begin{pexample}
This heavy-duty shield is constructed from reinforced aluminium with a polycarbonate visor that is both impact and ballistic resistant. The window allows clear vision while providing a high level of defence in combat situations.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 2.00 kg \\
    \textbf{\trans{price_label}:} & 800 \\
    \textbf{\trans{encumbrance_label}:} & 3 \\
    \textbf{\trans{protection_label}:} &
\\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{plane}\hspace{0.5em}\faIcon{microchip}\hspace{0.5em}}{}


\subsection*{Magnetic Shield Generator}

\begin{pexample}
A wrist-mounted device that creates a magnetic field to deflect metal projectiles.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 0.80 kg \\
    \textbf{\trans{price_label}:} & 7500 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
\\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{space-shuttle}\hspace{0.5em}}{}


\subsection*{Greek Hoplite Shield}

\begin{pexample}
A large circular shield with bronze facing, used by hoplites to defend and form phalanxes.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 6.50 kg \\
    \textbf{\trans{price_label}:} & 600 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
C C C \\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{eye}\hspace{0.5em}}{}


\subsection*{Wooden Shield with Bronze Boss}

\begin{pexample}
A wooden shield with a bronze boss for added protection and ease of grip.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 4.20 kg \\
    \textbf{\trans{price_label}:} & 320 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
\\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{eye}\hspace{0.5em}}{}


\subsection*{Wooden Leather-reinforced Shield}

\begin{pexample}
A wooden shield reinforced with leather.
\end{pexample}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{weight_label}:} & 4.00 kg \\
    \textbf{\trans{price_label}:} & 350 \\
    \textbf{\trans{encumbrance_label}:} & 1 \\
    \textbf{\trans{protection_label}:} &
\\
\end{tabular}




\wbif{phasesix}{
    \vspace{3mm}
\faIcon{eye}\hspace{0.5em}}{}


\end{multicols}