\worldchapter{\trans{spells_title}}{appendix-spells}
\label{ch:appendix-spells}

\begin{multicols}{2}


\section{Wizardry}


\subsection*{Bogus}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 1\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & 4d6 minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Illusion\\
\textbf{\trans{variant_label}:} & Arcana\\
\end{tabular}


The caster creates an illusion that replaces any object. The illusion must be approximately the same shape as the object. The object, like the illusion, must not exceed a size of meters corresponding to the \textbf{power of the spell}. The duration of the effect is \textbf{magic level}+1 W6 minutes.


\subsection*{Unmask}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 3\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Abjuration\\
\textbf{\trans{variant_label}:} & Arcana\\
\end{tabular}


Within a radius of \textbf{power}+\textbf{magic level} meters, the spell instantly cancels all illusions.


\subsection*{Glitter}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 3\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 200\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power d6 minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Illusion\\
\textbf{\trans{variant_label}:} & Light\\
\end{tabular}


In the magician's field of vision, a glitter is created anywhere on an area 10*\textbf{power} centimeters square. The glitter can take any shape and color. The glitter remains for \textbf{magic level}W6 minutes.


\subsection*{Illusion}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power*2 d6 minutes\\    \textbf{\trans{concentration_label}:} & Ja \\
\textbf{\trans{type_label}:} & Illusion\\
\textbf{\trans{variant_label}:} & Arcana\\
\end{tabular}


The great illusion! Within a radius of \textbf{power}*20 steps around the wizard, everything begins to deform. Familiar objects become strange artifacts, walls bend to impossible angles, and living creatures transform into other-like creatures. The zone of illusion remains in the place where it was created. The spell lasts (\textbf{magic level}+1)W6 minutes.


\subsection*{Ogre's breath}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 3\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 2\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power d6 minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Illusion\\
\textbf{\trans{variant_label}:} & Nature\\
\end{tabular}


The magician creates a cloud of any odor, which spreads over an area of \textbf{power}*10 steps. The smell remains even after the spell is finished, but the spell is active for \textbf{Magic level} W6 minutes. The cloud can only be controlled within the spell duration and is driven by the wind afterwards.

Magic level 5+: The smell is so intense that anyone who smells it is significantly affected by it. A foul smell will make them sick, while a sweet smell will enchant them.


\subsection*{Perfect shape}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 3\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Magic Level minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Illusion\\
\textbf{\trans{variant_label}:} & Arcana\\
\end{tabular}


The caster appears in a perfect form. All good features are highlighted. The caster receives the \textbf{power of the spell} as a bonus to attractiveness for \textbf{magic level} minutes.


\subsection*{Simulacrum}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 10\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Magic Level rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Illusion\\
\textbf{\trans{variant_label}:} & Light\\
\end{tabular}


The caster conjures a simulacrum of a creature that appears deceptively real.
The illusion remains for \textbf{magic level} rounds.
A successful roll on Perception against the \textbf{power} of the spell allows it to be recognised as an illusion.


\subsection*{Doppelganger}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 10\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Magic Level rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Illusion\\
\textbf{\trans{variant_label}:} & Light\\
\end{tabular}


The caster summons an exact replica of himself that moves in his vicinity for \textbf{magic level} combat rounds, confusing attackers. For the duration of the spell's effect, the caster's \textit{Evasion} is increased by \textbf{power}.


\subsection*{Water to wine}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 1\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Water\\
\end{tabular}


The sorcerer turns water, which he holds in front of him in a vessel, into wine.


\subsection*{Flatulentio}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 2\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 50\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Illusion\\
\textbf{\trans{variant_label}:} & Nature\\
\end{tabular}

\begin{quote}
Auch das menschliche Hinterteil verliert dann und wann den Status der rückwärtigen Dienste und wird zur Offensivwaffe.
    \begin{flushright}
    -- Martin Gerhard Reisenberg
    \end{flushright}
\end{quote}

The magician creates the illusion that a creature no more than 50 paces away is farting loudly enough to be heard from afar. In addition to the obvious noise, a distinctive odour also spreads away from the person.

The greater the \textbf{power} of the spell and the \textbf{magic level}, the more noticeable the flatulence.


\subsection*{Levitar}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 3\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 50\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Control\\
\textbf{\trans{variant_label}:} & Energy\\
\end{tabular}


Mit einer einfachen Geste entfesselt der Zaubernde eine unsichtbare Kraft, die Gegenstände durch die Luft bewegt. Levitar kann genutzt werden, um Objekte aufzuheben, heranzuziehen oder mit einem kraftvollen Stoß fortzuschleudern. Die Stärke der Bewegung hängt von der Willenskraft des Anwenders ab.

Besonderheit: Erfahrene Magier können den Zauber verfeinern, um Objekte vorsichtig zu greifen oder sie im Kampf einzusetzen.

Spruchformeln:
„Levitaris Volantis!“ – (Für präzise, schwebende Bewegungen)
„Levitar Impetus!“ – (Für kräftige Stöße oder Würfe)


\section{White Magic}


\subsection*{Defenseless figure}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & 5*Power minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Illusion\\
\textbf{\trans{variant_label}:} & Arcana\\
\end{tabular}


The caster appears absolutely harmless for 5*\textbf{Power} minutes. Depending on the appearance, he appears like a frail old, sick man, a defenseless woman or similar.

The caster receives a bonus of \textbf{magic level} points to his \textit{stealth} skill.


\subsection*{Overlight}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 15\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Control\\
\textbf{\trans{variant_label}:} & Light\\
\end{tabular}


The caster is able to get ahead of effects that have taken place in a range of \textbf{magic level}\textit{5  steps in approx. \textbf{power}}2 seconds. It is possible for him to catch a glass even though it shatters on the ground.


\subsection*{Detect magician}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 3\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 200\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Divination\\
\textbf{\trans{variant_label}:} & Arcana\\
\end{tabular}


The caster can detect the magical talent and alignment of a person in his field of vision. The observed person rolls a WillPower roll. If he achieves success according to the \textbf{power of the spell} + \textbf{magic level}, his magical talent remains hidden.


\subsection*{Protection wall}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Earth\\
\end{tabular}


The caster creates a protective wall around himself that offers protection to the caster.

The wall can withstand \textbf{power}*2 wounds. The protective wall can only be damaged by magical weapons or spells, in this way it can be worn down to 0 prematurely.

The wall remains \textbf{Magic level}+1 combat rounds.


\subsection*{Banish lower undead}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 9\\
    \textbf{\trans{arcana_cost_label}:} & 3\\
    \textbf{\trans{range_label}:} & 10\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Abjuration\\
\textbf{\trans{variant_label}:} & Light\\
\end{tabular}


The caster's hand releases a flash of bright white light that strikes up to \textbf{Power} undead. These immediately shatter, leaving nothing but a smoking pile of bones. The spell only works on lower undead like zombies, skeletons, or lower vampires. To higher undead, such as higher vampires or were-creatures, it inflicts significant damage (\textbf{magic level}*3 wounds).


\subsection*{Banish magic}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 3\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & 5 minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Abjuration\\
\textbf{\trans{variant_label}:} & Arcana\\
\end{tabular}


The caster creates a \textbf{power}*2 meter magic spell circle. No magic or magical action can be cast within this circle. Existing spells expire immediately, with the exception of the spell Banish Magic.

The circle remains in place for \textbf{\_magic level}+1 minutes.


\subsection*{Detect lie}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 3\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Divination\\
\textbf{\trans{variant_label}:} & Mind\\
\end{tabular}


The caster recognizes whether his counterpart is lying or not. Up to \textbf{magic level} statements of the observed can be checked.

The target of the spell may roll against its willpower. If the roll with \textbf{power} successes, it remains hidden whether it is lying or not.


\subsection*{Circle of light}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 3\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & 15 minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Light\\
\end{tabular}


The caster creates a bright circle of light of \textbf{Power}*2 meters radius around him. The circle remains for 15 minutes.


\subsection*{Fast as light}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 11\\
    \textbf{\trans{arcana_cost_label}:} & 3\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Light\\
\end{tabular}


The caster begins to run at a speed equal to that of light. To bystanders, he seems to vanish into thin air, but in reality he sprints at incredible speed, perceiving his surroundings as if he were merely running fast. It is possible for the caster to run over any walkable terrain, for example, he can cross an entire continent in the time of a blink of an eye. It is not possible for him to perform any other action while running. 

The spell lasts for one second.


\subsection*{Light attack}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Damage\\
\textbf{\trans{variant_label}:} & Light\\
\end{tabular}


The victim is blinded by glaring light and is completely disoriented and unable to act for \textbf{power} rounds of combat. The victim takes \textbf{magic level} hits.


\subsection*{Candle}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 3\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 50\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Fire\\
\end{tabular}


The caster lights up to \textbf{Power}*3 candles.


\subsection*{Banish higher undead}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 13\\
    \textbf{\trans{arcana_cost_label}:} & 5\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Abjuration\\
\textbf{\trans{variant_label}:} & Light\\
\end{tabular}


From the hands of the caster a glaring white wall of light emerges, which glides towards an undead. The undead flares up in flames and suffers unimaginable agonies (it is said that he goes through all the agonies of his victims at once). Apart from a pile of ashes, nothing remains of the higher undead. The wall of light has a width of about \textbf{power}\textit{3 meters, it is also possible to destroy several lower undead that are hit by the wall, but only one higher undead. Other higher undead that are next to the victim suffer \textbf{magic level}}2 wounds.

The wall moves at a speed of \textbf{magic level}+1 steps per combat round.


\subsection*{Good friend}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 7\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Magic level d6 minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Control\\
\textbf{\trans{variant_label}:} & Mind\\
\end{tabular}


The caster makes the victim believe that he is a good friend of his, even one of his best. He willingly tells him everything he would tell his best friend. After the spell is finished, the victim cannot explain why he did it.

The victim of the spell rolls on his willpower. If he achieves successes equal to the \textbf{power of the spell}, the spell has failed and the victim has knowledge of the enchantment attempt.

The friendship lasts for \textbf{magic level} minutes.


\subsection*{Banish ghosts}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 3\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Abjuration\\
\textbf{\trans{variant_label}:} & Arcana\\
\end{tabular}


The caster banishes up to \textbf{magic level} ghostly creatures that are in a defined area (house/temple/forest). He must at least mentally fix the ghosts.

The ghosts roll dice according to their remaining wounds. If they achieve as many successes as the \textbf{power of the spell}, they remain unaffected by the spell.


\subsection*{Terrifying figure}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 3\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Magic Level+1 d6 minutes\\    \textbf{\trans{concentration_label}:} & Ja \\
\textbf{\trans{type_label}:} & Illusion\\
\textbf{\trans{variant_label}:} & Mind\\
\end{tabular}


The caster appears before the bystanders as a fearsome magician. Lightning flashes around him and wind swells his clothes. Anyone intending to approach the caster must pass a \textit{Courage} roll with \textbf{power} successes.


\subsection*{Blur}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 1\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Light\\
\end{tabular}


The spell refracts the light around him and blurs his form. For \textit{Power} rounds, attacks against him are difficult rolls (minimum roll + \textbf{magic level}).


\subsection*{Banish curses}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 4\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 10\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Abjuration\\
\textbf{\trans{variant_label}:} & Mind\\
\end{tabular}


The caster banishes a curse. The minimum roll of the check is raised by the power of the curse spell, and lowered by the \textbf{magic level}.


\subsection*{Healing}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 10\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Healing\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


The caster heals the target for \textbf{power}*\textbf{magic level} wounds.


\subsection*{Neron Statue}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 3\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Magic Level hours\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Illusion\\
\textbf{\trans{variant_label}:} & Light\\
\end{tabular}


The spellcaster makes a transparent statue appear, shaped after the model - a statue of the young Neron in the center of the Neronite settlement. Due to the fact that no Neronite has ever seen the living Neron, the statue appears static and lifeless. Depending on the will of the caster, the statue has a size from 10cm to life-size.


\subsection*{Detect black mage}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 3\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Magic Level d6 days\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Divination\\
\textbf{\trans{variant_label}:} & Mind\\
\end{tabular}


The magus can detect the disposition and alignment of any mage he sees for up to \textbf{magic level} d6 days. If a mage obstructs this examination by his Magic Lore, the White Mage still examines his spirit value. The spell is designed primarily against its black magic counterpart, White Mage; it neutralizes that spell completely.


\subsection*{End transformation}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


The caster banishes a transformation taking place in front of him. The transformer may roll his Magic Lore value against the caster's spell, increasing the minimum roll of the spell by the \textbf{power} of the End Transmutation spell. If the roll shows a success, the transformation remains.


\section{Black Magic}


\subsection*{Summon nightmare}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & 1 nights\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Mind\\
\end{tabular}


The caster summons an alp, a spirit creature that haunts its victims in their sleep. The alp has no shape, and can change places at will and without loss of time. The spirit is not under the control of the caster. If the alp is to perform a service, a successful charm roll is required. If this fails, the alp will disappear as soon as possible.

The minimum roll of the charm roll is 7-\textbf{magic level}. The caster can give \textbf{power} orders to the alp.


\subsection*{Domination}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 7\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 10\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power*5 minutes\\    \textbf{\trans{concentration_label}:} & Ja \\
\textbf{\trans{type_label}:} & Control\\
\textbf{\trans{variant_label}:} & Mind\\
\end{tabular}


The caster can make the victim carry out a command of the caster.

The command transmitted by the caster manifests itself as a strange idea in the mind of the controlled. During the duration of the spell, this idea keeps entering the mind of the victim, as long as the victim does not give in to it, and sometimes it can even disturb his concentration on other things. 

The caster can make the controlled do things that are not immediately life-threatening to him or go against his innermost principles. For example, a mage cannot be made to burn valuable books, but a paid henchman can be made to betray his master, or a mercenary to change sides in battle. 

The spell lasts for \textbf{power} minutes. Once a minute, the victim casts on his willPower. If it achieves less than the \textbf{power of the spell}+\textbf{magic level}, it is convinced of the strange idea and performs it.


\subsection*{Blood thorns}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 7\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 20\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Magic Level+1 rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


The caster causes dark thorns to sprout from the ground within a predetermined \textbf{Strength}*2 metre radius. Anyone standing in the area at the end of their own combat round takes \textbf{Strength} hits.

The blood thorns remain for \textbf{\_magic level}+1 combat rounds before turning into a black, stinking pulp.


\subsection*{Blood flow}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 7\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power rounds\\    \textbf{\trans{concentration_label}:} & Ja \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


The victim rears up while a torrent of blood seeps out of his body through all pores at lightning speed. The victim takes \textbf{magic level} wounds per combat round, and the spell lasts for \textbf{power} combat rounds.

At the end of the combat round, the victim rolls on his strength. If it reaches as many successes as the spell has \textbf{power}, the spell ends immediately.


\subsection*{Dark paths}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 7\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Control\\
\textbf{\trans{variant_label}:} & Mind\\
\end{tabular}


The mage can translocate at will within a radius of (\textbf{power}+\textbf{magic level})*3 meters. During translocation, a dark shadow appears to glide across the ground.


\subsection*{One with the shadows}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Enchantment\\
\textbf{\trans{variant_label}:} & Light\\
\end{tabular}


As long as the enchanted person remains in the shadow, he is difficult to make out. He can then only be recognized as a deeper shadow within the shadow itself. 

When he stands still, he will only be spotted by those who specifically look for him and look directly at him. For this, \textbf{Power} successes must be achieved on a Perception roll.

If the enchanted person moves slowly, the number of successes to be achieved is halved, while fast movements can be seen without difficulty.

The spell lasts for \textbf{Power} minutes.


\subsection*{Night creature}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 2\\
\textbf{\trans{duration_label}:} & 1 nights\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Enchantment\\
\textbf{\trans{variant_label}:} & Light\\
\end{tabular}


Once the sun has set, the enchanted person barely makes a sound when walking (the Stealth skill is increased by \textbf{power}+\textbf{magic level}) and can see in the dark as if it were daytime. 

The spell lasts for one night.


\subsection*{Voice of hate}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 11\\
    \textbf{\trans{arcana_cost_label}:} & 3\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Magic Level days\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Control\\
\textbf{\trans{variant_label}:} & Mind\\
\end{tabular}


The caster whispers something in the ear of the first victim. 

The victim is infused with hatred and feels the desire to carry the spell further by targeting more victims up to \textbf{Power}. Thus, the hatred builds up more and more.

The effect lasts for \textbf{magic level} days.


\subsection*{Vision of fear}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 7\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Enchantment\\
\textbf{\trans{variant_label}:} & Mind\\
\end{tabular}


The victim feels cruel images of distorted worlds, which he perceives as a vision. More and more, however, it seems to him as reality. If a Willpower roll with a minimum roll of \textbf{magic level}+2 fails, the victim is in danger of going insane for a short time. 

The spell lasts for \textbf{Power} minutes.


\subsection*{Tongues of Seth'Nra}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 10\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Demonic\\
\end{tabular}


In a circle of \textbf{Power} meters in diameter, \textbf{Power} tentacle-like black tongues grow out of the ground, holding creatures of any kind. Touching the tentacles decreases the held's arcana value by \textbf{magic level} points per combat round. Physical damage does not occur. The tentacles have 3 possible wounds. If they are not destroyed, they remain indefinitely.


\subsection*{Schwarzer Tod}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 20\\
    \textbf{\trans{arcana_cost_label}:} & 10\\
    \textbf{\trans{range_label}:} & 20\\
    \textbf{\trans{actions_label}:} & 2\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Damage\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


Der Zaubernde rezitiert die folgenden Worte mit klarer, fester Stimme:

Aus der Tiefe der Schatten, aus dem Schoß des Todes, rufe ich die schwarze Pest.
Faul sei das Fleisch, welk sei der Geist,
bis die Stille des Grabes dich heimführt!

Schwarze, geisterhafte Schwaden steigen aus deiner Hand empor und rasen auf das Ziel zu. Das Opfer verspürt sofort eine brennende Kälte in seinen Adern. Innerhalb von Sekunden breiten sich dunkle Flecken auf seiner Haut aus, begleitet von starkem Schwindel und Schwäche.

Falls der Zauber nicht rechtzeitig gebannt oder geheilt wird, verfällt das Ziel innerhalb von Minuten einem tödlichen Fieber.

Der Zauber fügt direkten Schaden zu und ignoriert jeglichen Rüstungswert des Ziels.

Wirft der Zaubernde einen Megakrit zerfällt das Ziel sofort bei Kontakt des Zaubers zu Staub.

Höhere Wesen erleiden durch diesen Zauber nicht den sofortigen Tod. Diese erleiden im Verlauf des Kampfes pro Runde Magieniveau * Stärke Schaden.

Gegenmittel:
Eine Priestersegnung oder ein starker Heilzauber kann den Fluch aufheben, wenn er innerhalb einer Stunde gewirkt wird.
Das Blut eines Engels kann den Effekt vollständig neutralisieren.


\section{Elemental Magic}


\subsection*{Energy Bolt}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 5\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Damage\\
\textbf{\trans{variant_label}:} & Energy\\
\end{tabular}


The caster summons a bolt of pure energy that flies toward a target, causing hits equal to the \textbf{spell power}+\textbf{magic level} on impact.


\subsection*{Flaming death}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 7\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 10\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Damage\\
\textbf{\trans{variant_label}:} & Fire\\
\end{tabular}


At a distance of no more than 10 meters a blazing fire is created that causes \textbf{magic level} wounds per combat round on an area of \textbf{Power} meters squared. The fire is not magical and burns until it consumes its food, without combustible material \textbf{Power} combat rounds.


\subsection*{Ice shard}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power*2 minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Water\\
\end{tabular}


The caster creates a small ice shard in his hand, which flies towards the victim at a fast speed, hitting him in a place of free skin. The shard penetrates deep into the skin, but then melts immediately, leaving not even a wound.

After a minute, the hit part of the body cools down so much that the victim can hardly use it. There is also no feeling left in the corresponding body part. The victim does not take any damage, all actions with the body part reduce the skill/attribute values by \textbf{magic level}*2. 

The effect lasts \textbf{Power}*2 minutes.


\subsection*{Wild Growth}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 3\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Magic Level days\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Nature\\
\end{tabular}


The caster creates unnaturally fast growth of plants. Within a radius of max \textbf{Power} meters, natural and unnatural plants are created that can burrow through the ground, penetrate walls, and burst steel. The plant growth persists for \textbf{magic level} days, after which the plants decay into a stinking something.

The caster cannot control the growth of the plants.


\subsection*{Shard Storm}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 9\\
    \textbf{\trans{arcana_cost_label}:} & 3\\
    \textbf{\trans{range_label}:} & 10\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Damage\\
\textbf{\trans{variant_label}:} & Earth\\
\end{tabular}


Splinters form in the caster's palm and fly towards the target at high speed. At an angle of \textbf{magic level}\textit{15°, the splinters cause a total of \textbf{Strength}}3 hits and cause major structural damage to solid objects. 

If living creatures are hit, the game master distributes the damage among the victims.


\subsection*{Screen}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Magic Level rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Air\\
\end{tabular}


The caster blurs against the background. Only a slight flicker in the air reveals the presence of an object at the spot. If the caster moves, the visual shield moves as well. Detecting the unusual glimmer requires a Perception roll, which achieves successes according to the \textbf{Power} of the spell.


\subsection*{Melting}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 7\\
    \textbf{\trans{arcana_cost_label}:} & 3\\
    \textbf{\trans{range_label}:} & 2\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Magic Level minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Nature\\
\end{tabular}


On an area of \textbf{Power}W6 square meters at a distance of 2 steps, the ground liquefies. After \textbf{magic level} minutes, the ground solidifies again within three seconds.


\subsection*{Odem}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 2\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Demonic\\
\end{tabular}


For \textbf{Power} combat rounds, the caster's breath is a foul, demonic surge which has a range of 2 meters and inflicts \textbf{magic level} wounds per combat round to anyone within the cloud.


\subsection*{Veil of mist}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Water\\
\end{tabular}


From the ground around the caster, as he raises his arms, a dense fog rises, obstructing vision and muffling sounds. The cloud of mist has a diameter of \textbf{Power}*3 meters and a height of about 3 meters. The higher the \textbf{Power} of the spell, the denser the fog cloud. The cloud is stationary and forms around the caster as the center.

The fog acts as an extension of the caster's senses through the magical connection to him. As long as he remains in the fog himself, he can instinctively perceive all movements within the cloud and better hear all sounds within it (Perception + \textbf{magic level}).

Rumor has it that loud, manic laughter while summoning the fog increases its later, threatening effect. However, this can almost certainly be dismissed to the realm of myths and legends.

The fog cloud persists for \textbf{Power} minutes.


\subsection*{Arcane storm}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 7\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Energy\\
\end{tabular}


Shortly after the invocation, a magical mist manifests directly above the caster, emitting lightning and creating a magical tension. The storm grows at a rate of one meter per combat round to a size of \textbf{Power}*5 meters, and can be controlled by the caster.

In the magical storm, each magic adept suffers one wound per combat round. In addition, no spellcaster is able to perform a magical action in the storm. Those not skilled in magic do not suffer any limitations.

The storm can be controlled at a speed of two meters per action. This control requires the caster to remain focused on the spell, which is not otherwise necessary.


\subsection*{Life Stream}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 5\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Healing\\
\textbf{\trans{variant_label}:} & Water\\
\end{tabular}


The caster completely undresses and lies face down in flowing water, which is so large that the caster is completely submerged in it. There he lets himself drift.

During the whole time of floating, the caster draws life energy from the river, and heals \textbf{power}+\textbf{magic level} wounds in an hour. During this time he can not and does not have to breathe, and not perceive his environment.


\subsection*{Charcoal stone}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 3\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Magic Level hours\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Energy\\
\end{tabular}


The caster can turn a diamond or gemstone of any size into a glowing piece of coal. The piece is equal to the size of the diamond and remains glowing for \textbf{magic level} hours. In the process, it is so hot that it ignites combustible materials. The purer the gemstone is, the hotter the piece of coal glows. An amber is not enough to ignite anything with the coal.


\subsection*{A fresh breeze}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 3\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & 2 hours\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Air\\
\end{tabular}


A fresh breeze makes an encouraging and fresh breeze appear. In moments of hopelessness, the spell is the right thing to increase the enterprise of companions.

The wind sweeps across the land for about a minute within a radius of 100 meters, filling everyone it touches with new courage and freshness. Anyone within the radius heals \textbf{power} wounds and receives a bonus of \textbf{magic level} points to their bravery for the next two hours.


\subsection*{Rot}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 9\\
    \textbf{\trans{arcana_cost_label}:} & 3\\
    \textbf{\trans{range_label}:} & 3\\
    \textbf{\trans{actions_label}:} & 3\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Damage\\
\textbf{\trans{variant_label}:} & Demonic\\
\end{tabular}


The adept must spit on a plant or creature.

As long as the saliva touches the victim, the flesh or plant continues to rot. As long as the flesh is rotting, the spell will cause a cumulative wound every third round of combat. When the spell ends, the victim will no longer rot, but the corrupted flesh will be lost forever.

The spell ends when the saliva is washed off or after wounds of \textbf{power}+\textbf{magic level}.


\subsection*{Leech tendrils}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 15\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Demonic\\
\end{tabular}


The caster kneels on the ground, fixes the target with his gaze and slams the fingers of one hand into the ground.

Tendrils sprout from the fingers of the caster with breathtaking speed, growing under the surface of the earth towards the opponent. Under the ground, the tendrils move at a speed of \textbf{magic level} meters per combat round. As soon as the tendrils are under the opponent, they grow to the surface and entwine his legs, so that he can neither run nor fight without restrictions. His combat skills (hand to hand combat, shooting, throwing) are reduced by \textbf{Power}.


\subsection*{Ivy coat}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & 1 hours\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Nature\\
\end{tabular}


The caster causes ivy tendrils to grow from the ground and entwine themselves around the caster's entire body, detaching them from the ground after growth so that the caster can move freely.

The tendrils provide the caster with \textbf{magic level} protection for \textbf{power} combat rounds in combat.

They decay into a withered heap after one hour. Until then, the tendrils also give a bonus of \textbf{power} to Stealth outside of combat depending on the environment.


\subsection*{Amber path}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 9\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 20\\
\textbf{\trans{duration_label}:} & Magic Level hours\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Nature\\
\end{tabular}


The caster places five amber crystals in the shape of a pentagram at the place where the amber portal is to be created and concentrates on the destination. Then, for one minute, he imagines a tunnel that will take him to this place.

The portal remains \textbf{magic level} hours and can transport \textbf{power}*2 people or animals.

At the location of the amber pentagram, an ivy plant begins to grow in a circle and form a vortex. The vortex forms a maw in the center which leads through a portal to a location known to the caster at a distance of 20 miles. When the caster enters the portal, he immediately appears on the other side at the destination.


\subsection*{Eye of Seth'Nra}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 7\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Magic level*5 minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Demonic\\
\end{tabular}


The caster takes one of his eyes out of the eye socket with two fingers and holds it on the flat of his hand.

The eye gets black outgrowths in the form of tentacles and wings and starts to fly by itself. It moves with the speed of 10 meters per second and has \textbf{power} maximum wounds. If the eye is not back when the spell expires, it falls to the ground. In this case, the caster can retrieve and use it within half an hour.

If the eye is destroyed or lost, it withers and grows back only after 2D6 days. In this case, it causes 2 wounds to the caster once.

The spell lasts for \textbf{magic level}*5 minutes.


\subsection*{Elemental Weapon}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Magic Level rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Energy\\
\end{tabular}


The character channels the magic of their favoured element into their melee weapon to strengthen it.

For the next \textbf{magic level} combat rounds, the weapon ignores the opponent's protection. In addition, attacks with the weapon have \textbf{strength} increased damage potential for the next two combat rounds.


\subsection*{Arrow of wind}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 15\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Air\\
\end{tabular}


The caster enchants up to \textbf{magic level} arrows with the element of wind.
On a successfull cast the weapon ignores armor.
The arrow hits the victim with such force that they have to throw their resistance. If it scores less than the strength of the spell, the victim is thrown to the ground.


\subsection*{Avatar of the storm}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 15\\
    \textbf{\trans{arcana_cost_label}:} & 3\\
    \textbf{\trans{range_label}:} & 25\\
    \textbf{\trans{actions_label}:} & 2\\
\textbf{\trans{duration_label}:} & Magic level d6 + Arcana spent rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Air\\
\end{tabular}


The caster consumes all his arcana and becomes the focus of a raging storm. For \textbf{magic level} d6 + \textbf{arcana spent} rounds, all surrounding creatures take electrical damage equal to the \textbf{power of the spell}. 

All creatures within the area of effect must make a Athletics roll with 2 successes per round or be thrown to the ground by the raging wind.


\subsection*{Chain lightning}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 3\\
    \textbf{\trans{range_label}:} & 15\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Damage\\
\textbf{\trans{variant_label}:} & Air\\
\end{tabular}


The caster summons the essence of a thunderstorm in his hand and hurls it as lightning at a creature. The creature struck suffers \textit{Strength}\_ hits.

The lightning bounces off it and moves to the creature closest to the one hit. This receives \textit{strength}-1 hit.

This process is repeated \textbf{magic level}+2 times.

The spell does not differentiate between friend and foe and only hits each victim once.


\subsection*{Wings of wind}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 1\\
    \textbf{\trans{actions_label}:} & 2\\
\textbf{\trans{duration_label}:} & Power+Magic level minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Air\\
\end{tabular}


The enchanted creature grows wind wings that carry it or another creature through the air.

The enchanted creature can fly for \textbf{power}+\textbf{magic level} minutes.


\subsection*{Small sandstorm}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 10\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Air\\
\end{tabular}


The caster concentrates and stirs up dust, earth or sand within their line of sight. A small sandstorm \textbf{Magieniveau} paces high and \textbf{Magieniveau} paces wide forms for \textbf{power} rounds.  

Anyone in the centre of the sandstorm must make a Perception check, with at least as many successes as the spell's power. Otherwise, they are blind for the duration of the spell, with all penalties to blindness.


\subsection*{Elementar}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 10\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 10\\
    \textbf{\trans{actions_label}:} & 2\\
\textbf{\trans{duration_label}:} & Power rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Air\\
\end{tabular}


The caster summons a creature of pure elemental energy for \textbf{power} rounds to aid them in battle. The elemental has \textbf{magic level} wounds and can attack with \textbf{magic level} damage potential.


\subsection*{Water breathing}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & (Power+Magic level)*2 minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Water\\
\end{tabular}


The caster says the words Þat mælti mín móðir, at mér skyldi kaupa fley ok fagrar árar.

The caster casts a spell on themselves or someone they can touch.

The enchanted person is able to breathe underwater for (\textbf{spell power}+\textbf{magic level})*2 minutes. When the spell ends, the enchanted person must say something in their natural language to be able to breathe air again.


\subsection*{Call elemental spirit}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 8\\
    \textbf{\trans{arcana_cost_label}:} & 4\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 10\\
\textbf{\trans{duration_label}:} & (Power+Magic level)*2 minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Mind\\
\end{tabular}


The caster places a little of the element whose elemental spirit is to be invoked in a bowl or on a surface of the opposite element. Then he kneels down in front of the bowl and invokes the powers of the element. 

After about 30 minutes, the face of an elemental spirit appears in the element used. This can vary greatly depending on the element, so that anything from a face to a non-material appearance is possible. The elemental spirit has no feelings and no alignment, but it can only be controlled by the caster if the latter binds it (Bind Elemental Spirit).

The elemental spirit remains for (\textbf{power}+\textbf{magic level})*2 minutes.


\subsection*{Bind elemental spirit}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & (Power+Magic level)*2 minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Control\\
\textbf{\trans{variant_label}:} & Mind\\
\end{tabular}


The caster points to the elemental spirit. 

The caster can bind an elemental spirit (which must have already materialised) to him. If this is done, the elemental spirit follows any command of the caster. If the elemental spirit is already bound, the caster can only take over the elemental spirit with a magic duel by taking over the foreign spell. The caster binds the elemental spirit for (\textbf{power}+\textit{}magic level)*2 minutes.


\subsection*{Elemental form}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & (Power+Magic level)*2 minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Nature\\
\end{tabular}


The caster touches the corresponding element, concentrates and murmurs (element) become my body. 

The caster's body transforms into the corresponding element, with all its advantages and disadvantages. It should be noted that clothing and equipment are not transformed and may be damaged. The spell can be dropped at any time. While the spell is being maintained, the caster cannot cast an elemental spell based on an element other than that of his body.

The spell lasts (\textbf{power}+\textbf{magic level})*2 minutes.


\subsection*{Summon element}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 3\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Nature\\
\end{tabular}


The caster closes his left hand into a fist. 

In the fist of the caster a small occurrence of the element he wants to summon is created. This spell is mainly used in combination with the calling of an elemental spirit.


\subsection*{Elemental object}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 4\\
\textbf{\trans{duration_label}:} & (Power+Magic level)*10 minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Nature\\
\end{tabular}


The caster focuses on the desired object in his mental eye, reaches into an object from a certain element (it is possible for him to simply slide his hand into the object during the spell) and pulls out the desired object.

The caster pulls an object of his choice from another object. Swords made of ice, drinking vessels made of wood, shields made of rock or water, etc. are possible. There are no limits to the caster's creativity, but he can only pull out one object at a time, which makes the creation of chains, for example, very time-consuming.

The item has its typical properties, plus the elemental component, so a sword made of fire inflicts fire damage on the victim, a sword made of wood receives no damage bonus. Only the caster does not receive this possible elemental damage. A drinking goblet of ice is very pleasant if one likes to enjoy very strongly chilled drinks, but it could freeze to the fingers and or lips of everyone else except the creator. 

The spell can be dropped by the caster at any time. If the caster does not return the item to its place of origin when dropping the spell (e.g. does not put the wooden shield back into the tree) he receives a wound on the hand, possibly a few burn or frost blisters and the item dissolves.

The object remains (\textbf{power}+\textbf{magic level})*10 minutes.


\subsection*{Ginae's Call}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 2\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Healing\\
\textbf{\trans{variant_label}:} & Water\\
\end{tabular}


The caster instructs the person to be treated to remove their clothes and lie down in a flowing body of water. There the caster stands next to the person to be treated and places his hand on his head. 

During the whole time of the drifting, the person to be treated draws life energy corresponding to \textbf{power}+\textbf{magic level} wounds per minute from the river. During this time he cannot and does not have to breathe. He is not aware of his surroundings. The caster must stand beside him during the entire time.


\subsection*{Cold}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power+Magic level minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Ice\\
\end{tabular}


The caster points his hand at the victim of the spell. Then he spreads his fingers and calls upon Jogran. 

The caster creates a small shard of ice in his hand, which flies towards the victim with rapid speed, hitting him in a spot of free skin. The shard penetrates deep into the skin, but then melts immediately, leaving not even a wound.

In the next 5 minutes, the part of the body that was hit cools down so much that the victim can hardly use it. There is also no feeling left in the corresponding part of the body. The victim does not take damage, all actions with the body part reduce the skill/attribute values by half.

The cold remains \textbf{power}+\textbf{magic level} minutes.


\subsection*{Fireball}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 15\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Damage\\
\textbf{\trans{variant_label}:} & Fire\\
\end{tabular}


The caster hurls a skull-sized flaming fireball at the target. On impact, the spell deals \textbf{Power} hits and sets anything flammable to \textbf{Burning} \textbf{magic level} status.


\subsection*{Grass ring}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Healing\\
\textbf{\trans{variant_label}:} & Earth\\
\end{tabular}


The spell caster creates a ring of grass that grows in the specified location within sight and is \textbf{power} metres in diameter. The grass emits a magical vapour, anyone who passes through the ring regenerates \textbf{magic level} wounds once and is \textit{Shocked 1}.

The spell lasts for \textbf{power} combat rounds.


\subsection*{Elemental shield}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 7\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Fire\\
\end{tabular}


The caster creates a magical shield around their body using their preferred element. The shield provides the caster with \textbf{magic level}*2 protection for \textbf{power} combat rounds and an additional effect depending on the element:

Fire: Attackers must roll a D6 for each attack. On a roll of 1-3, they are afflicted with the Burning 1 condition. Non-magical projectiles (arrows, slings, spears, etc.) have a 50\% chance of burning rather than piercing.


\subsection*{Shock}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 10\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Energy\\
\end{tabular}


Fires a bolt of pure energy at an enemy. The bolt deals \textbf{ Power}-3 hits and has a penetration 2. The victim gets Shocked \textbf{magic level} even if the spell does not cause any wounds.


\subsection*{Elementarer Köcher der Wandlung}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Nature\\
\end{tabular}


Dieser magisch verzauberte Köcher erkennt den aktiven Zauber des Trägers und wandelt gewöhnliche Pfeile in elementare Projektile, die dem gewirkten Zauber entsprechen. Die Wandlung erfolgt augenblicklich beim Ziehen des Pfeils.


\subsection*{Dornensturm}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 3\\
    \textbf{\trans{range_label}:} & 12\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Damage\\
\textbf{\trans{variant_label}:} & Nature\\
\end{tabular}


Der Waldläufer ruft den Zorn der Natur an. Aus dem Boden schießen scharfe Dornen und peitschen durch die Luft.

Alle feindlichen Einheiten in einem Kegel von 12 Zoll Reichweite erleiden W6+2 Schaden.

Betroffene Einheiten müssen einen Rüstungswurf mit -1 Modifikator ablegen.

Getroffene Einheiten haben in ihrer nächsten Runde -2 Bewegung (die Dornen halten sie fest).

Zusatz: Zorn des Waldes (verstärkte Variante)
Wenn der Waldläufer sich in einem bewaldeten oder naturverbundenen Gelände befindet, kann er 1 zusätzliches Mana ausgeben. In diesem Fall:

Schaden erhöht sich auf W8+3

Gegnerische Einheiten erleiden zusätzlich 1 Punkt anhaltenden Schaden zu Beginn ihrer nächsten Runde.

Gegenzauber:
Ein Feind kann diesen Zauber durch eine Magieresistenzprobe (8+) negieren.

Flufftext:

„Aus jedem Blatt wird eine Klinge, aus jedem Schatten eine Falle. Die Natur vergisst nichts – und sie kämpft mit mir.“


\section{Shamanism}


\subsection*{Simple healing}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 5\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Healing\\
\textbf{\trans{variant_label}:} & Nature\\
\end{tabular}


The caster heals a person or animal for \textbf{power}+\textbf{magic level} wounds.


\subsection*{Weather forcast}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 2\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 3\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Divination\\
\textbf{\trans{variant_label}:} & Nature\\
\end{tabular}


The caster is able to predict the weather for the next \textbf{magic level} days. If the \textbf{Power} of the spell is above 3, he can always predict the weather changes with exact time, otherwise he only knows how the weather will develop.


\subsection*{Call birds}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 3\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Nature\\
\end{tabular}


The caster summons all birds within a radius of \textbf{Power}*100 meters, who believe that there is a large amount of their favorite food at the desired location. The caster cannot control the birds, but a trained observer is able to recognize the individual bird species.

Magic level 4+: The caster can suggest that the birds do a task for him. If the caster rolls charm roll with \textbf{magic level} successes, the birds may heed their call.


\subsection*{Trust}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 5\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power*5 minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Control\\
\textbf{\trans{variant_label}:} & Nature\\
\end{tabular}


The animal fully trusts the caster. For \textbf{Power}*5 minutes, the animal is considered a familiar. The animal may be a natural creature the size of a wolf. The animal must not be hostile to the caster for this spell.

Magic level 4+: The animal may be the size of an elephant.


\subsection*{Locate animal}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 3\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Divination\\
\textbf{\trans{variant_label}:} & Nature\\
\end{tabular}


The caster goes to the natural habitat of an animal (e.g. a stream or a tree) and stays there for 5 minutes. During this time he directs his thoughts to the animal he is looking for. 

The caster tracks down the exact location of the animal. He knows at that moment where the animal is.


\subsection*{Salamander feet}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Magic Level minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Nature\\
\end{tabular}


The caster is able to walk on hands and feet on smooth walls and even ceilings or overhangs.

In addition, he can safely jump down from heights up to \textbf{Power}*3 meters and land on his feet unharmed. However, he needs free hands to catch himself with. He can keep his shoes and gloves on for this.

The effect lasts for \textbf{magic level} minutes.


\subsection*{Call of the wild}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 3\\
    \textbf{\trans{arcana_cost_label}:} & 3\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 3\\
\textbf{\trans{duration_label}:} & Magic Level minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Nature\\
\end{tabular}


The caster summons a group of a desired animal species from up to \textbf{Power} kilometers around. The animals behave like the caster's familiars for the duration of the spell. 

When the spell expires, the caster casts on Charm. If the roll fails, the animals turn on the caster or his companions.

The caster can call up to \textbf{Power} animals the size of a wolf.


\subsection*{Clear water}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 2\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Nature\\
\end{tabular}


The water that the caster touches, starting from the caster's hand, becomes so pure that it can be drunk. The final cost depends on the purity of the water before the spell is cast. The game master decides on this. The caster can purify up to \textbf{Power} buckets of water.

Magic level 4+: The water has a healing power. Drinking it heals \textbf{magic level} wounds.


\subsection*{Smoke}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Magic Level minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Fire\\
\end{tabular}


The caster throws a burning piece of cloth on the ground.

A dense smoke emanates from the burning piece of cloth as soon as it hits the ground. The smoke is driven by the wind and cannot be controlled. Enough eye-burning smoke is created to form a cloud of \textbf{Power}*10 meters around the caster.


\subsection*{Mark animal}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 2\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power days\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Divination\\
\textbf{\trans{variant_label}:} & Nature\\
\end{tabular}


The caster marks the animal so that he knows the direction in which the animal is for the entire period of the spell. The spell lasts \textbf{Power} days. The caster is able to determine the distance of the animal.


\subsection*{Living Hideaway}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 3\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power months\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Nature\\
\end{tabular}


The caster slides an object he wants to hide into a plant. 

The object enters the plant without damaging it. To release the item from the plant, the caster must cast the spell again. The item can remain in the plant for \textbf{Power} moons, after which it will be ejected from it.


\subsection*{Healing hands}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Healing\\
\textbf{\trans{variant_label}:} & Nature\\
\end{tabular}


The caster heals \textbf{power}+\textbf{magic level} wounds on the wounded. It also heals broken bones and closes wounds.


\subsection*{Hawk Eyes}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & 1 hours\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Enchantment\\
\textbf{\trans{variant_label}:} & Nature\\
\end{tabular}


The caster can clearly and accurately see everything up to a distance of \textbf{Power} kilometers for one hour, unless fog or smoke obstruct his vision. Attacks with ranged weapons gain \textbf{magic level} additional hit dice.


\subsection*{Nature play}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 3\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power+Magic level minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Enchantment\\
\textbf{\trans{variant_label}:} & Nature\\
\end{tabular}


To the enchanter and the other spectators, nature shows itself in all its grace, beauty and perfection. A perfect landscape reveals itself to them: The trees shine in their most beautiful colors and sway rhythmically to the pleasant whisper of the wind. Water casts magnificent plays of waves, over which fish leap symmetrically. The nature play is different in its expression every time and of course also dependent on the attitude of the spellcaster. 

The spell lasts \textbf{power}+\textbf{magic level} minutes.


\subsection*{Animal Companion}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 50\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & 8 hours\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Enchantment\\
\textbf{\trans{variant_label}:} & Nature\\
\end{tabular}


The caster connects his mind to an animials mind in range to compell it to be his ally.
The animal needs successes on its willpower equal to the \textbf{Power} of the spell or be his companion for the next \textbf{magic level} hours.

If the animal is hostile to the caster the spell casting roll is a difficult roll (+1).


\subsection*{Foxfire}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Magic Level d6 rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Earth\\
\end{tabular}


The caster creates \textbf{power} living bioluminescent beings within 10 paces. These beings are made of living plant matter. They magically illuminate their surroundings and can move very slowly (speed 1).

The creatures follow the caster and provide a pleasant light around the caster for the duration of their existence. They have no combat abilities, they are plants that crawl on the ground. 

They last for \textbf{magic level} D6 hours and then disintegrate.


\section{Sanguine Magic}


\subsection*{Transfusion}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 7\\
    \textbf{\trans{arcana_cost_label}:} & 3\\
    \textbf{\trans{range_label}:} & 2\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Damage\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


The caster taps into the life energy of a being, using a blood crystal to establish a connection with his victim. The victim must have a wound through which the caster can make the connection. He spins a thread of blood from his blood crystal to the wound of the victim.

The target suffers \textbf{Power} wounds and the caster is healed by the same number + \textbf{magic level}.


\subsection*{Rite of life}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 3\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Healing\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


The caster takes \textbf{Power} wounds. The target is healed twice as much and gains \textbf{magic level} health.


\subsection*{Rite of purification}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 2\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Healing\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


The caster enters a meditative state and focuses on harmful substances in his blood, such as diseases and poisons. He collects these in a certain place of his body and then lets them out through a cut.

For each disease and poison he wishes to cure, the caster takes a wound. This number is reduced by the \textbf{Power} of the spell.


\subsection*{Blood Arrow}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Damage\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


The caster summons an arrow-like projectile from his blood, which he hurls at the opponent at high speed.

The caster takes \textbf{magic level} wounds. The victim suffers \textbf{Power} wounds.


\subsection*{Blood Ban}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 7\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Control\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


The caster affects the blood circulation of his victim and can cause numbness and paralysis of certain parts of the body. Skills that require the affected body part are reduced by \textbf{magic level}.

After \textbf{Power} combat rounds, the caster must spend one arcana or wound to maintain the effect.


\subsection*{Rite of the blood crystal}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 8\\
    \textbf{\trans{arcana_cost_label}:} & 4\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 10\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


The caster enters a meditative state and concentrates on the flow of magic and blood. After a day, the caster opens his veins and lets almost all of his blood flow into a clay bowl.

After adding ruby dust, he reduces it to the absolute essence and forms a crystal shard from it. He then inserts this into an incision on his body. The caster then uses this crystal to cast his Sanguine magic without having to inflict a separate wound each time.


\section{Necrology}


\subsection*{Awaken zombie}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 11\\
    \textbf{\trans{arcana_cost_label}:} & 3\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Arcana\\
\end{tabular}


The caster awakens up to \textbf{magic level} corpses within a radius of 10 meters. The zombies follow his command and stay alive for up to \textbf{Power} minutes.


\subsection*{Path of bones}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 3\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power hours\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


The caster decays to fine dust and can travel at 10 kilometers / hour in this form. Maximum he can keep in this form \textbf{Power} hours.

The caster has \textbf{magic level} wounds in this form, but can only be wounded by things that can harm a pile of bones.


\subsection*{Dead signpost}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 10\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Divination\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


If a corpse (animal corpses also count, as long as they are at least the size of a mouse) is buried in the ground within a \textbf{Power}*10 meter radius, the caster is allowed to ask \textbf{magic level} directional questions: Which way is Meridian? The last rider to pass this ground, where did he ride?


\subsection*{Dead gaze}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 7\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Divination\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


The caster places his thumb and forefinger in the eyes of the dead person and closes his eyes.

The caster looks backward from the time of death into the dead person's past. In doing so, he sees everything that the dead person saw out of his eyes. The images appear more blurred the further the gaze goes into the dead person's past. The caster sees at most the last \textbf{Power} days before death. The higher the \textbf{magic level}, the clearer the impressions.


\subsection*{Creature of the Dead}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 7\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 3\\
\textbf{\trans{duration_label}:} & Magic Level*2 rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


The caster creates an undead hybrid being from different skeletons. The creature is capable of performing uncontrolled actions. It can wield weapons with a skill value of \textbf{Power*}2. The creature gains all the ability of the former creatures.

The creature remains \textbf{magic level}*2 combat rounds.


\subsection*{Death sword}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


The caster creates a death sword out of thin air. The sword has piercing 1 and a damage potential of \textbf{magic level} dice in melee combat.

Each wound caused, the sword absorbs. For each wound absorbed, the sword gets one die of damage potential. If the absorbed wounds reach \textbf{Power}+1, the sword disintegrates and the spell ends.


\subsection*{Death Scream}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 6\\
    \textbf{\trans{arcana_cost_label}:} & 3\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Illusion\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


The caster lets out a cruel death cry, which makes all those present within a radius of 10 meters, who did not cover their ears, become incapacitated for \textbf{magic level} combat rounds. 

Each victim makes a roll on his willPower. If it does not succeed according to the \textbf{Power of the spell}, the victim flees in panic.


\subsection*{Dance of Death}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 9\\
    \textbf{\trans{arcana_cost_label}:} & 3\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power hours\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


Within \textbf{power}*3 meters of the caster, all dead rise from the ground, and are under the control of the caster. The dead are able to perform uncontrolled actions and remain alive for \textbf{magic level} hours.


\subsection*{Summon skeletons}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 9\\
    \textbf{\trans{arcana_cost_label}:} & 3\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power*3 rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


\textbf{Power} Skeletons rise from the ground, armed with bone swords (penetration 0). They can fight with the caster's skill. They have \textbf{magic level} possible wounds and stay for \textbf{Power}*3 combat rounds.


\subsection*{Torment of the bones}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Control\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


The victim suffers incredible pain, believing his bones would burst.

If the victim fails a Willpower roll, the effect causes the victim to collapse on the ground, unable to act, for \textbf{Power} combat rounds. The minimum roll for this throw is increased by \textbf{magic level}.


\subsection*{Breath of transience}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 3\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


All living plants within \textbf{Power}*3 meters perish under the caster's breath and weather into a dead, black mass. This also affects magically created plants.


\subsection*{Bone whip}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power*3 rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


A bone whip about 3 meters long forms from the caster's arm, which can be wielded by the caster as a weapon. The range of the whip is 3 meters, it has a penetration of 0 and a damage potential of \textbf{magic level} dice.

The whip lasts up to \textbf{Power}*3 combat rounds.


\subsection*{The wrath of bones}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 20\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Damage\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


The caster throws bone splinters at enemies, summoning the wrath of the bones. The splinters deal \textbf{Power}+1 hits to all enemies in the cone, evenly distributed among \textbf{magic level} opponents.


\subsection*{Secrets of the Dead}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 4\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 10\\
\textbf{\trans{duration_label}:} & Power hours\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Divination\\
\textbf{\trans{variant_label}:} & Mind\\
\end{tabular}


The caster kneels over a corpse or skeleton and begins to slowly cut it apart. 

The caster learns a part of the dead person's knowledge with each piece he cuts. At the end of the ritual he has an impression of all the memories of the dead person. The process is an ordeal in the realm of the dead for the soul of the dead. The necrologist receives +\textbf{magic level} in the attribute corresponding to the highest of the dead for \textbf{power} hours.


\subsection*{Bone shield}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Mind\\
\end{tabular}


The necrologist throws a bone splinter to the ground and shouts Protect me!. 

Pieces of bone shoot out of the ground and surround the necrologist. Practically, they are equivalent to a protection of \textbf{magic level}+2 on the whole body. The bone shield is equivalent to a encumbrance of 2. 

The bone shield lasts \textbf{power} combat rounds.


\subsection*{Bone growth}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 4\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 10\\
\textbf{\trans{duration_label}:} & Magic Level hours\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Mind\\
\end{tabular}


The caster must kneel in the centre of the area to be enchanted and drill a bone splinter into the ground. 

The caster creates an unnatural growth of bone that grows to full size within 25 minutes. Within a radius of max. \textbf{power} steps, a large growth of bones is created. The necrologist can climb walls with the help of the bone growth, or make it break open gaps in doors. The bone growth remains for \textbf{magic level} hours, after which it disintegrates into dust. The caster only gives the growth an approximate direction, he cannot control it.


\section{Mysticism}


\subsection*{Translocation}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 2\\
    \textbf{\trans{arcana_cost_label}:} & 3\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 10\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Control\\
\textbf{\trans{variant_label}:} & Mind\\
\end{tabular}


The caster begins to slowly blur and become more indistinct after the preparation time of 30 seconds. This process lasts another 30 seconds, but during this time the caster is no longer vulnerable. If someone tries to touch the caster during this time, his hand will penetrate a cold, dense mass.

The caster can be transported a maximum of \textbf{Power} kilometers. His body appears at the destination without actually traveling the distance. At the destination, again, it takes 30 seconds for the body to appear completely.


\subsection*{Protection aura}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Magic Level rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Arcana\\
\end{tabular}


The caster creates a magical protective aura around him. The aura radiates from him and can be seen through magical actions. It is impenetrable to all forms of magic, which includes magical attacks or transformations. The protective aura can absorb \textbf{Power}*2 wounds before it collapses. The spell can be maintained for a maximum of \textbf{magic level} rounds.


\subsection*{False feeling}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 7\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Control\\
\textbf{\trans{variant_label}:} & Mind\\
\end{tabular}


The victim feels a feeling chosen by the caster. This is a concrete feeling, such as pride in something. The feeling lasts for \textbf{Power} minutes.


\subsection*{Swiftness}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 3\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Magic Level d6 rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Enchantment\\
\textbf{\trans{variant_label}:} & Air\\
\end{tabular}


The caster accelerates. His speed and range for \textit{Running} and \textit{Walking} are increased by \textit{Power\textbf{ for }magic level}\_ d6 rounds.


\section{Hermeticism}


\subsection*{Unseen, unnoticed}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 7\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power hours\\    \textbf{\trans{concentration_label}:} & Ja \\
\textbf{\trans{type_label}:} & Control\\
\textbf{\trans{variant_label}:} & Mind\\
\end{tabular}


The magician appears to his surroundings as nothing in the truest sense of the word. No attention is paid to him, people bump into him on the street, but do not care. Even if he addresses someone, he is ignored. If he manages to attract someone's attention, they immediately forget about him as soon as he withdraws from them.

This spell is not a transformation of the caster, but a mass hypnosis. As a result, the caster cannot be detected even by clairvoyance spells like Recognize Life. His aura is just as visible as ever, but no attention is paid to it.

Someone who specifically searches for the caster is entitled to a Perception check in order to discover him nevertheless. If this is done with \textbf{Power} successes, the hypnosis effect falls off the seeker and he can perceive the caster normally again.

The caster must succeed in a test of willpower against the minimum roll \textbf{magic level}*2 after the spell to avoid falling into a deep depression.


\subsection*{Veil of oblivion}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Magic Level*10 minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Control\\
\textbf{\trans{variant_label}:} & Mind\\
\end{tabular}


This spell allows the caster to manipulate his victim's memories of an event that occurred in the last \textbf{Power} hours. For \textbf{magic level}*10 minutes, the victim forgets to perform a task specified by the caster and related to the event in question (for example, alerting the guards). If he is reminded of the task by anything or anyone, the spell immediately falls off him.

The victim may make a WillPower roll. If he succeeds according to the \textbf{Power} of the spell, it is not manipulated.


\subsection*{Open}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 3\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Energy\\
\end{tabular}


The caster is able to open locked, non-magical objects such as doors, chests or other locks.

In addition to normally locked locks, the caster is able to open magically locked locks with a seal of the Power of the spell.

Magic level 5+: The spell opens all locks.


\subsection*{Magic analysis}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 40\\
    \textbf{\trans{actions_label}:} & 2\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Divination\\
\textbf{\trans{variant_label}:} & Arcana\\
\end{tabular}


The caster is able to perform an analysis of a spell that has been cast or is in the process of being cast. The caster recognizes the school of magic, essence of the spell (whether healing, damage, type of element, duration, etc.) and a rough estimate of the strength of the spell.


\subsection*{Spirit of wine}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 7\\
    \textbf{\trans{arcana_cost_label}:} & 3\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power*10 minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Control\\
\textbf{\trans{variant_label}:} & Mind\\
\end{tabular}


The caster gestures to drink a glass of wine. As he does so, he murmurs the name of the spell. 

Up to \textbf{magic level} victims of the spell instantly experience a drunken stupor that causes them to stagger and makes any normal action difficult. the minimum roll for all rolls is increased by 2. The spell's effect lasts a maximum of \textbf{Power}*10 minutes. 

Each victim of the spell may make a WillPower roll. If the roll reaches successes equal to the \textbf{Power} of the spell, it resists the spell.


\subsection*{Extreme performance}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 7\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Control\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


The caster can temporarily increase a Persona Attribute, Combat Skill (Shooting, Hand to Hand Combat, or Throwing), or Evasion to extreme levels for a difficult task. The chosen value increases by \textbf{magic level}*2 points for a period of \textbf{Power} minutes.


\subsection*{Freeze}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power actions\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Water\\
\end{tabular}


The victim freezes in place for \textbf{Strength} actions. It is fully conscious and all senses function normally. However, physical actions or attacks are not possible.

At the start of each action, the victim rolls for willpower, increasing the minimum roll by the \textbf{magic level}. If the roll is successful, the stun is lifted and the action is available to the victim. The difficulty of the minimum roll decreases by 1 after each roll.


\subsection*{Dilatio}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 7\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Air\\
\end{tabular}


The caster creates a momentary spontaneous portal under himself, into which he is immediately sucked. He creates another portal at a location that is at most \textbf{Power}*10 steps away from his current position.

Without any delay he appears at the desired destination.


\subsection*{Bloodlust}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 7\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Control\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


The enchanted man falls into an uncontrollable bloodlust. His mental abilities have atrophied to the point that he can barely tell friend from foe. His combat stats (shooting, hand to hand combat, and throwing) each increase by \textbf{Power} points.

Education, Logic, and Deftness decrease by \textbf{magic level} points. The enchanted feels no pain or exhaustion, only an uncontrollable desire to fight. After the spell falls from him, he collapses unconscious.


\subsection*{Arrest}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Enchantment\\
\textbf{\trans{variant_label}:} & Arcana\\
\end{tabular}


The victim of the enchantment is trapped in the place where it is for \textbf{power}+\textbf{magic level} combat rounds. It is able to act normally and can also attack, but cannot move from the spot.


\subsection*{Invisibility}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 1\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Magic Level minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Light\\
\end{tabular}


The caster shrouds himself or another being in an arcane cloak of reflecting light, rendering their form unrecognisable.

For the duration of the spell, the target gains \textbf{Strength} to the Stealth skill.


\subsection*{Absorb magic}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 15\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Abjuration\\
\textbf{\trans{variant_label}:} & Arcana\\
\end{tabular}


The caster can absorb arcana from a magical object or creature. Arcana \textbf{power}+\textbf{magic level} is transferred from the target to the caster.

A magical creature rolls on its willpower. For each success on this roll, the amount of arcana transferred is reduced by 1.


\subsection*{Aevum}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 80\\
    \textbf{\trans{arcana_cost_label}:} & 1000\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1000\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Mind\\
\end{tabular}


The ritual requires extensive preparation. Thus, the most precise preparation of the hermeticist as well as that of the target person is required.

The hermeticist activates the spell at the very beginning of the ritual. Over the whole time he has to maintain this spell, which devours a considerable amount of magic. Every single day he has to spend two hours of meditation, working on the painting. The painting must be created solely by the Hermeticist.

The target needs no preparation other than the realisation to become fleshless. For this purpose, he should torture himself with all kinds of burning, poisoning and the like to facilitate the completion of the ritual.

At the time of performance, the hermeticist only has to maintain the sphere with his concentration and control the arms. Scenery as well as atmosphere are irrelevant, as in most hermetic acts.

During the time of the creation of the image, the hermeticist binds the spirit and soul of the target person to it. At the time of execution, a sphere of pure magic is created not far from the painting, which mostly floats in the air in a semi-transparent matt white. This sphere forms arms which glide like hoses over the heads of the victims to be provided. With a continuous humming sound, the sphere collects the innards of the victims and then condenses them into the image.

The hermeticist thus creates a firm bond between the spirit and soul of the target person and the painting. The spirit in the painting is able to enter any person in the immediate vicinity of the painting at any time within one second. The target person then lives on in this person until his or her death or an exorcism, and then enters the painting again. It completely dominates the person, feels their feelings and lives completely in them. This process of dominating and regressing only comes to an end once the image is destroyed or the target person has returned to the image four times. After that, he remains in the image.

The created image is itself almost indestructible. It is considered an artefact of the Hermeticist level and requires the same effort to destroy as any other artefact of that level. Only immense magical influence or divine work can destroy the object.

The target can enter the image \textbf{power}+\textbf{magic level} times before being trapped inside.


\subsection*{Expolitio}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 3\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Water\\
\end{tabular}


The caster can cleanse an area of \textit{spellpower} square steps in size of any contamination. The cleaning is instantaneous and removes dirt and odours.


\section{Necromancy}


\subsection*{Death Vision}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 9\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Special rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Divination\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}

\begin{quote}
To die proudly when it is no longer possible to live proudly. Death of one's own free choice, death at the proper time, with a clear head and with joyfulness, consummated in the midst of children and witnesses: so that an actual leave-taking is possible while he who is leaving is still there.
    \begin{flushright}
    -- Friedrich Nietzsche
    \end{flushright}
\end{quote}

The victim is tormented by a very realistic vision of his death, the manner of death can be determined by the caster. The vision includes dying, the rotting of the flesh and the decay of the bones to dust. The victim does not take any physical harm from the spell, though there is a possibility that he may be traumatized by the death vision. For the duration of the spell, the victim is barely capable of any meaningful action. 

The victim can attempt to abort the spell with a willPower check. This requires as many successes as the spell has \textbf{Power}.

The spell lasts until the willPower check is successful.


\subsection*{Call animal spirit}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 7\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Nature\\
\end{tabular}


The caster draws a pentagram in the ground and concentrates on the animal spirit. 

At the moment the ritual is finished, the animal spirit appears in the place of the pentagram. The animal spirit performs \textbf{Power} simple services for its master. The services must be simple and involve only one action, e.g. a ride that begins with mounting and ends with dismounting, or help in a fight against an opponent. The values of the animal spirit correspond to those of the normal animal, raised by \textbf{magic level} points.


\subsection*{Voice of the dead}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 7\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Divination\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


The caster places an object of the dead in front of him, closes his eyes and concentrates on the object and the realm of the dead. 

The caster goes into a light trance, his voice changes and resembles that of the dead, the more personal the object is and the more the caster knows about the dead. The caster can ask \textbf{power}+\textbf{magic level} questions to the dead, which will be answered with yes/no to. The dead the must answer also before his death could have given.


\subsection*{Spirit protection}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Magic Level rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Abjuration\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


The caster invokes the protection of the spirits. The protection of \textbf{Power} people increases by 3 normal protection for \textbf{magic level} combat rounds, the Resistance value increases by 3.


\subsection*{Spirits advice}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Divination\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


The caster can ask \textbf{Power} questions to the spirit world, which will be answered if the spirits are willing. The questions must allow a simple yes/no answer.

\textbf{Magic level} ghosts appaer to answer possible questions.


\subsection*{Living armor}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 9\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Mind\\
\end{tabular}


The caster creates \textbf{Power} living armors. The armors can perform simple defense and attack missions. They have 4 possible wounds and wield swords with a penetration of 0 and 3+\textbf{magic level} dice.


\subsection*{Animate body}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 7\\
    \textbf{\trans{arcana_cost_label}:} & 3\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 15\\
\textbf{\trans{duration_label}:} & Magic Level hours\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Mind\\
\end{tabular}


The moment the ritual is finished, the caster binds a simple spirit into a dead body, which controls the body and performs simple commands. The movements are slow, and since only normal movements are available to it, the body should be chosen prudently beforehand. A doll or corpse can walk, a ball can roll but cannot climb stairs, for example. 

The caster can take direct control of the body as if he were inside it. However, this costs 1 arcana per \textbf{Power}*5 minutes, and any damage the body suffers, the caster's body suffers as well.

The spell ends after \textbf{magic level} hours.


\subsection*{Deathly Cold}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 9\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Damage\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


The moment the caster touches his target, a terrible cold spreads from the place of the touch, causing \textbf{magic level)} wounds per combat round. The caster can cancel the spell at any time, but if it is not canceled, it ends when the target is completely cooled and dead. 

The victim rolls a Resistance roll at the beginning of each combat round before taking damage. If the roll succeeds with at least \textbf{Power}, the spell ends and no more damage is done.


\subsection*{Exorcise spirit}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 3\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Abjuration\\
\textbf{\trans{variant_label}:} & Mind\\
\end{tabular}


The caster chooses up to \textbf{Power} spirits or beings ruled by spirits. The spirits are banished and leave their earthly existence.


\subsection*{Animate object}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 5\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 15\\
\textbf{\trans{duration_label}:} & Power+Magic level hours\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Mind\\
\end{tabular}


The moment the ritual is completed, the caster binds a simple spirit into the chosen object, which performs a simple action on the object.

Unlike the Animate Weapon ritual, the basic idea of this ritual is rather peaceful, so the most common uses of this ritual are to make crystal balls swirl glowing mist, or to make candlesticks light the candles as soon as the room is entered.

In the ritual, the caster must determine who and how the trigger is. For some things, like the mentioned crystal balls, it makes sense if this is only a certain touch of the user, for the mentioned candlestick rather everyone who comes within a certain range around the candlestick. 

The object remains animated up to \textbf{power}+\textbf{magic level} hours.


\subsection*{Simple service spirit}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 7\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 15\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Nature\\
\end{tabular}


The caster rubs his hand with bone dust, draws a pentagram in the air and concentrates on the spirit.

At the moment the ritual is finished, the service spirit appears in the place of the pentagram. The service spirit performs a simple service for its master, the service can consist of max \textbf{Power} things. The service spirit is not able to directly harm a living being or object. Examples of services include delivering very short messages (max \textbf{Power} words to one person, or 1 word to a total of \textbf{Power} people), notifying the caster when one of \textbf{Power} certain events occurs, or even gathering \textbf{Power} apples.

Magic level 4+: The ghost can also harm people.


\subsection*{Possession}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 11\\
    \textbf{\trans{arcana_cost_label}:} & 3\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 15\\
\textbf{\trans{duration_label}:} & (Power+Magic level)*10 minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Control\\
\textbf{\trans{variant_label}:} & Mind\\
\end{tabular}


The caster draws a pentagram on the target's forehead and concentrates on the spirit and the target.

In this ritual, the caster allows a spirit to enter the target's body. The spirit can be a service spirit, a free spirit or the spirit of the caster. In the latter case, the caster's body slumps, does not react, breathes slowly and stares into the void when his eyes are opened. The target is (\textbf{power}+\textbf{magic level})*10 minutes under the control of the spirit driven into it, which can control the entire body (run, punch, fight, speak, etc.). 

Should the target's body die during the possession, the spirit abruptly disappears from the body and returns to its sphere. If the target's body dies while the caster is in it, the caster's spirit returns to its original body and the caster is unconscious for 3W6 minutes.


\subsection*{Animate Weapon}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 15\\
    \textbf{\trans{arcana_cost_label}:} & 5\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 15\\
\textbf{\trans{duration_label}:} & Magic Level*5 actions\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Nature\\
\end{tabular}


The caster forms an incantation circle around the weapon to be animated. 

At the moment the ritual is finished, the caster binds a spirit to the anointed weapon. This spirit inflicts additional \textbf{Power} wounds on the victim, in addition to the weapon's usual wounds. The weapon is considered a magical weapon, but can only be used by the caster. Anyone else who attempts to use the weapon will themselves be attacked by the spirit. The appearance of the ghost can be freely determined by the caster.

The weapon can be used to attack \textbf{magic level}*5 times before the ghosts leaves the weapon.


\subsection*{Ghostly body}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 4\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 2\\
\textbf{\trans{duration_label}:} & Power+Magic level minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Mind\\
\end{tabular}


The caster closes his eyes, thinks the verse My body, a spirit and then opens his eyes again. 

The caster is able to perform all the actions of a spirit, e.g. see, touch things, cast spells unless ingredients are needed or within reach, fly, move through inanimate objects, etc. The spell can be dropped at any time, causing the caster to take on their normal physical form, but without clothing. 

The spell can be dropped at any time, causing the caster to take on their normal physical form, but without clothing as this is not transformed with them. Objects strongly familiar to the caster should probably also be carried in ghost form. As spirits are immune to non-magical weapons and attacks, so is the caster. 

The caster can also be banished in spirit form. When exorcised, the caster ends up unconscious in his body for 2W6 minutes at the point where he started the spell. 

The spell lasts for \textbf{power}+\textbf{magic level} minutes.


\section{Demonology}


\subsection*{Black call}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 15\\
    \textbf{\trans{arcana_cost_label}:} & 5\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 5\\
\textbf{\trans{duration_label}:} & Power*10 minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Demonic\\
\end{tabular}


The caster summons the appearance of a lesser demon into the world. The servant appears within the next 3d6 minutes. No binding takes place, the creature has its own will. For \textbf{Power}*10 minutes the demon remains in the world.

The minimum roll for this spell is 7-\textbf{magic level}. Modifiers for character are applied after that.


\subsection*{Unnatural growth}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 9\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Magic Level hours\\    \textbf{\trans{concentration_label}:} & Ja \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Demonic\\
\end{tabular}


The caster crouches down and cuts his flesh with a ritual dagger so that blood drips onto the floor. He closes his eyes and imagines the growth. 

The form he imagines grows out of the caster's body. The surface and the appearance are based on the appearance of the archdemon or his servants who are attached to him. The caster can thus create a body part of almost any shape, which can be moved almost at will. The body part can have a length of \textbf{power} meters.


\subsection*{Deadly stone}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 7\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Damage\\
\textbf{\trans{variant_label}:} & Demonic\\
\end{tabular}


The caster leads an attack with a stone weapon. Usually a ritual dagger is used. 

If the attack is successful, the weapon melts into two tentacle-like outgrowths of liquid stone in the victim's body. The damage potential of the weapon is \textbf{power}+\textbf{magic level} dice, but it also takes 2 actions to pull the weapon out again (the outgrowths are already gone when you pull them out).


\subsection*{Maw}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 11\\
    \textbf{\trans{arcana_cost_label}:} & 3\\
    \textbf{\trans{range_label}:} & 10\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & 5 minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Demonic\\
\end{tabular}


At any point within range, a maw \textbf{magic level} meters in diameter and \textbf{power} meters deep opens up.


\subsection*{New flesh}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 11\\
    \textbf{\trans{arcana_cost_label}:} & 3\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 2\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Healing\\
\textbf{\trans{variant_label}:} & Demonic\\
\end{tabular}


The caster touches the wound of the target. He strokes it and speaks the name of the patron. 

The wound of the target closes completely. Any damage associated with the wound is erased. The wound closes with new flesh, and the wounded person immediately feels as if reborn. The new flesh that is created, however, is demonic in nature. It is an indefinable substance that naturally combines with human flesh. No one can say how the new flesh will behave in the future, whether it will be accepted by the body, or whether completely unexpected effects will occur. 

The spell heals (\textbf{power}+\textbf{magic level})*2 wounds.


\subsection*{Globulus}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 7\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Magic Level*5 minutes\\    \textbf{\trans{concentration_label}:} & Ja \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Demonic\\
\end{tabular}


The caster creates a hiding place by creating a bubble in the demon world into which he and \textbf{Power}*2 other characters are translocated. The bubble is created somewhere in the demon world, is transparent, and allows odor but nothing else to pass through. After the spell is completed, the characters in the bubble are translocated back.

The globe persists for \textbf{magic level}*5 minutes.


\subsection*{Demonic vision}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power+Magic level rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Divination\\
\textbf{\trans{variant_label}:} & Demonic\\
\end{tabular}


The vision of the caster changes, and he perceives the world with the vision of a demon. He recognizes all occurrences of demonic origin clearly and luminously even through walls, but is also limited to some extent by the distortion of the sight. In addition, the caster can accurately detect magical activity in his field of vision.

The spell lasts \textbf{power}+\textbf{magic level} rounds.


\subsection*{Breath of Wisgu}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 5\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power*2 rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Damage\\
\textbf{\trans{variant_label}:} & Demonic\\
\end{tabular}


Foul-smelling slime, blood, and filth are flung from the caster's mouth. Anyone who comes into contact with the substances is completely consumed by an unnatural disgust for a time of \textbf{Power}*2 rounds and is given the condition Shocked \textbf{magic level}.

After the effect time, the slime remains.


\subsection*{Banning circle}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 3\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 6\\
\textbf{\trans{duration_label}:} & Power+Magic level nights\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Abjuration\\
\textbf{\trans{variant_label}:} & Demonic\\
\end{tabular}


The demonologist draws a pentagram in a border in the floor or ceiling with the dagger or another object. The pentagram may have a maximum diameter of \textbf{power} meters. The more powerful the demon, the more complex the drawing. 

The outer border of the pentagram can be broken by a demonic being from the outside to the inside, but not in the opposite direction. Usually a spell circle is drawn around an incantation circle to hold the demon in place until it binds. However, places can also be protected by the spell circle independently of summons. Within the spell circle, the demon has no magical or demonic powers, but does have the abilities of its physical form. 

The following paraphernalia have an effect on the minimum roll of the spell circle : 

* \textbf{Suitable environment, rest}: -1
* \textbf{Banishing circle is made of blood}: -2
* \textbf{5 candles}: -1
* \textbf{Each additional demonologist}: -1
* \textbf{The stars are right}: -10
* \textbf{Animal Sacrifice (each)}: -2
* \textbf{Human sacrifice (each)}: -5
* \textbf{Temple nearby}: 20
* \textbf{day}: 5
* \textbf{Priest nearby}: 10
* \textbf{Consecration water nearby}: 5 
* \textbf{Superior Demon}: 10
* \textbf{Arch Demon}: 100

If the spell is reversed, the spell circle also applies in reverse. It will not let a demon in, but it will let it out. In this way, a demonologist can draw an additional circle around himself.


\subsection*{Brood}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 1\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Demonic\\
\end{tabular}


The demonologist stabs the demon he has previously summoned with his ritual weapon. 

The demonologist splits the being into \textbf{power} independent demons. The demons act independently and must also be bound independently (if the original demon was not already) and banished. Only lesser beings can be divided, not servants or even archdemons. A pactier is able to divide the direct servants of the archdemons.

Magic level 4+: Direct servants can be divided also.


\subsection*{Demonic Form}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 4\\
\textbf{\trans{duration_label}:} & Power minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Demonic\\
\end{tabular}


The demonologist crouches down, cuts his flesh with the Ritual Weapon and drips the blood onto the element attached to the Archdemon (For mist, water is enough, magic implies a Magical Artefact). 

The demonologist transforms into the form of one of the servants of his bonded archdemon. In doing so, he partially assumes the demon's abilities, though the body is just as vulnerable as in his human form. In addition, the demonologist gains only the demon's physical abilities at its normal human size, and no magical abilities at all. 

The transformation lasts \textbf{power} minutes. He receives a bonus of \textbf{magic level} points on an appropriate attribute.


\subsection*{Web}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 2\\
\textbf{\trans{duration_label}:} & Magic Level nights\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Demonic\\
\end{tabular}


The caster throws a piece of demonic nature (artefact, demonic object or new flesh) at the place over which the sphere is to be created. Then he waits until he is heard. 

Tentacles of demonic substance grow into a grid-like sphere of max \textbf{power} steps. The tentacles have a strength of 500 wounds and are therefore almost impossible to cut. The net can both lock in and lock out living creatures.


\subsection*{Call demon}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 10\\
    \textbf{\trans{arcana_cost_label}:} & 4\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 10\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Demonic\\
\end{tabular}


The rules for invoking a demon are as varied as they are controversial. It has been proven that the invocation benefits from the provision of various paraphernalia. There are also some peculiarities in the action that have a positive effect on its success. In general, it can be said that the invocation should take place in a suitable atmosphere and is a direct calling of the demon on the part of the demonologist. So it is also possible to make an invocation without any preparation only with the verse.

The following paraphernalia have an effect on the minimum roll of the Invocation :

* \textbf{Magic level}: -\textbf{magic level}
* \textbf{Suitable environment, silence}: -1
* \textbf{Heptagram drawn}: -1
* \textbf{Heptagram is made of blood}: -2
* \textbf{Sigil drawn}: -1
* \textbf{Player draws sigil from hand}: -10
* \textbf{7 candles}: -1
* \textbf{Each additional demonologist}: -1
* \textbf{The stars are right}: -10
* \textbf{Animal Sacrifice (each)}: -4
* \textbf{Human sacrifice (each)}: -10
* \textbf{Ban circle drawn}: obligatory
* \textbf{Temple nearby}: 20
* \textbf{day}: 5
* \textbf{Priest nearby}: 10
* \textbf{Holy water nearby}: 5
* \textbf{A sacrifice begins to pray}: 2 (each). 
* \textbf{Lesser demon is summoned}: -1
* \textbf{Higher demon is summoned}: 5
* \textbf{Servant of an Archdemon is summoned}: 30
* \textbf{Arch demon is summoned}: 100

Calling a demonic being does not include binding the demon.


\subsection*{Bind demonic being}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 7\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Control\\
\textbf{\trans{variant_label}:} & Demonic\\
\end{tabular}


The demonologist has to look into the eyes (if any) of the being he wants to bind and has to face its will.

If the spell succeeds, the demonologist gains control over a demon. If the demon is unbound, the mere casting of the spell is enough to bind it. However, if the demon has already been controlled by another demonologist, it is necessary to first (before casting the spell) perform a magical comparison (comparison roll spell casting) against the controlling caster. If this fails, the demon remains under the dominion of its original master. If the spell fails after a won magic comparison, the demon is no longer subject to any master. 

The minimum roll of the spell is modified according to the being to be bound:

* \textbf{Lower Demon}: -2
* \textbf{Higher Demon}: 2
* \textbf{Servant of an Archdemon}: 20
* \textbf{Arch Demon}: 100

The minimum roll is reduced by the \textbf{magic level}.


\subsection*{Pact}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 30\\
    \textbf{\trans{arcana_cost_label}:} & 12\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 100\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Demonic\\
\end{tabular}


Only a few who have made a pact with an archdemon have reported how the pact took place, but some facts are known, the demonologist must make contact through one of the servants. Demonologists have an easier time of it, as they are able to summon them. Other alignments must go to one of the demon's places of worship.

Once a caster has made contact, the demon takes control, usually for this purpose the demon opens a portal into its globe of the demon sphere, only those who can cross this threshold without perishing have any chance of a pact.

What exactly happens in the demon sphere is uncertain, but there are reports of cruel trials that the gifted have to endure, even the strongest usually return broken. 

If the pact is successfully concluded, the demonologists return as other beings. Mostly only the appearance reminds of the one who entered the portal.

In any case, the pactors are now subordinates of the demon, disobedience is punished, immediately and from within, it does not matter where the pactor is. The pact binds demon and demonologist across all spheres and ailments.

At the beginning, some particularly powerful demonologists are still able to resist and even assert their own will against the demon, but sooner or later all pactors are subordinate to their master.

With the conclusion of a pact, not only is one's life committed to the demon, but also any existence after death. The demonologist only dies when the demon allows it, otherwise he is merely drawn into the demon sphere to be released again by the demon at will.

It is said that there are demons who withdraw the pact from pactors, which would be the only possibility for a pactor to return to a halfway normal life, but most of them prefer to kill the demonologist or make him a lowly subordinate if he resists.


\subsection*{Mephitic Cloud}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 8\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 15\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Magic Level d6 rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Demonic\\
\end{tabular}


Summons a cloud of poisonous gas that lasts for \textbf{magic level} d6 combat rounds. The cloud has a diameter of \textbf{Power} steps and can be summoned up to 15 paces away from the caster.

If a character ends his combat round inside the cloud, he receives Poisoned 2 and 2 wounds. If a character crosses the cloud without ending their combat round inside, they receive 'Poisoned 1'.


\subsection*{Shadow Split}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 10\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Damage\\
\textbf{\trans{variant_label}:} & Demonic\\
\end{tabular}

\begin{quote}
"Als wir in den Wald stürmten stand da nur diese junge Frau. Unser Hauptmann lachte. Das sollte alles sein, was uns diese Menschen hier entgegen werfen? Eine Hexe? Unser Hauptmann stürmte ihr entgegen, doch die Hexe erhob nur ihre Hände. Im gleichen Moment wurde der erhobene Schwertarm unseres Hauptmanns von dunklen nebligen Tentakeln zurück gerissen mit einem gräßlichen Geräusch. Er schrie. Als die Hexe erneut ihre dämonische Geste vollführte, kamen weitere Tentakel und rissen ihm den ganzen Arm am Gelenk aus! Wir konnten grade noch fliehen!"
    \begin{flushright}
    -- Totschläger-Arne, Räuber
    \end{flushright}
\end{quote}

The ‘Shadow Split’ is a powerful and cruel spell that summons the dark forces of the Demon Sphere to tear apart an opponent's joints with unimaginable force. The caster summons dark, tentacle-like shadows that wrap themselves around the target's limbs and pull the joints apart with an eerie crack. In the worst case, this can lead to the complete loss of the affected limb.

If the target is wearing special armour such as bracers or greaves on the affected joints, the number of protection points will be deducted from the successes.

Target: A single living creature within the caster's line of sight.

Effect: The target suffers severe damage to the joints, resulting in considerable movement restrictions. With a particularly powerful cast, a limb can be completely severed. The damage is strength plus magic level.

Duration: Immediate effect, with continued movement restrictions until the target is healed.

Side effects: Using this spell may attract the attention of dark forces that may haunt the caster in the future.


\section{Astral Magic}


\subsection*{Crystal barrier}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 5\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Earth\\
\end{tabular}


At a point within reach, a barrier of grown crystals is formed, which is quite hard and therefore difficult to overcome. The crystals look like rock crystals, which grow out of the ground like normal crystals. The crystal barrier can have a maximum depth of \textbf{power} cm and a width of \textbf{power} meters. It takes about \textbf{magic level}*5 rounds to punch through the barrier.


\subsection*{Light of stars}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power+Magic level hours\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Enchantment\\
\textbf{\trans{variant_label}:} & Light\\
\end{tabular}


After about 20 minutes the eyes of the caster begin to dull and he sees both day and night. Bright light does not blind the caster. However, in complete darkness, the caster cannot see. The spell lasts \textbf{power}+\textbf{magic level} hours.


\subsection*{Path of the stars}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 3\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power+Magic level nights\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Divination\\
\textbf{\trans{variant_label}:} & Light\\
\end{tabular}


A bright star shows the caster the way to his intended destination.


\subsection*{Star message}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 3\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Magic Level nights\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Light\\
\end{tabular}


The astrologer looks at the starry sky and murmurs repeatedly the message to be conveyed. 

After about 35 minutes, individual stars of the celestial bodies begin to shine brighter than others. Skilled astrologers and astral magicians can read out of these constellations a message about one \textbf{power of the spell} sentence long, no matter where they are in the world.


\subsection*{Greater magic analysis}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 60\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Divination\\
\textbf{\trans{variant_label}:} & Arcana\\
\end{tabular}


The caster is able to perform an analysis of a spell that has been cast or is in the process of being cast. The caster recognizes the school of magic, essence of the spell (whether healing, damage, type of element, duration, etc.) and a rough estimate of the strength of the spell.


\subsection*{Silence of the cosmos}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 8\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Light\\
\end{tabular}


The caster calls upon the silence of the cosmos. This silence silences both the magical actions and the sounds. The area of silence has a diameter of \textbf{magic level} steps and moves with the caster.

The minimum roll for spells and magic knowledge is increased by 4 within the circle, including the caster. All sound is swallowed by silence. The caster cannot hear anything for the duration of the spell.

The spell lasts \textbf{power} minutes.


\subsection*{Irradiate}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power rounds\\    \textbf{\trans{concentration_label}:} & Ja \\
\textbf{\trans{type_label}:} & Damage\\
\textbf{\trans{variant_label}:} & Light\\
\end{tabular}


The caster stares at the target and summons the light of the sun. Bright rays come out of his eyes and hit the target directly in the face. 

The rays blind the target, who can barely see. All Perception rolls and attacks have a minimum roll increased by \textbf{magic level}. 

The spell remains active for \textbf{power} combat rounds.


\section{Lizard Folk Magick}


\subsection*{Blood Sacrifice Ritual}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 10\\
    \textbf{\trans{arcana_cost_label}:} & 3\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 3\\
\textbf{\trans{duration_label}:} & Magic Level hours\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Healing\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


In a gruesome ritual, the caster sacrifices a small creature to temporarily increase any attribute by the amount of the caster's strength. The boost lasts for \textbf{magic level} hours.


\subsection*{Mind ban}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 12\\
    \textbf{\trans{arcana_cost_label}:} & 3\\
    \textbf{\trans{range_label}:} & 10\\
    \textbf{\trans{actions_label}:} & 3\\
\textbf{\trans{duration_label}:} & Magic Level*5 hours\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Control\\
\textbf{\trans{variant_label}:} & Mind\\
\end{tabular}


The target rolls with their logic value, the roll is made more difficult by the \textbf{spell power}.

If the roll fails, the target is forced to obey the caster's commands until the spell expires or is cancelled.


\subsection*{Whiff of acid}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 8\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 5\\
    \textbf{\trans{actions_label}:} & 2\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Damage\\
\textbf{\trans{variant_label}:} & Demonic\\
\end{tabular}


The caster spits out a cloud of acid that causes damage to all targets in the area of effect equal to the spell's \textbf{power}+\textbf{magic level}.


\subsection*{Scale armour}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 6\\
    \textbf{\trans{arcana_cost_label}:} & 3\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 2\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


The caster's body becomes covered in additional scales. He gains \textbf{spell power} normal protection and \textbf{magic level} bleed protection.


\subsection*{Venomous Bite}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 7\\
    \textbf{\trans{arcana_cost_label}:} & 3\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 2\\
\textbf{\trans{duration_label}:} & 3 rounds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Damage\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


The caster receives a poison bite for \textbf{magic level} rounds of combat, dealing additional poison damage equal to the spell's \textbf{power} when hits are scored.


\subsection*{Dark Vision}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 10\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & 8 hours\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


The caster can see up to \textbf{power} × \textbf{magic level} steps in total darkness.


\subsection*{Shadow Step}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 6\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 2\\
\textbf{\trans{duration_label}:} & Magic Level minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Illusion\\
\textbf{\trans{variant_label}:} & Light\\
\end{tabular}


The caster fuses with the shadows, increasing their stealth by the \textbf{power} of the spell.


\subsection*{Swamp Fever}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 12\\
    \textbf{\trans{arcana_cost_label}:} & 4\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 3\\
\textbf{\trans{duration_label}:} & 1 weeks\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Enchantment\\
\textbf{\trans{variant_label}:} & Nature\\
\end{tabular}


The target takes damage equal to the spell's \textbf{power} each day the curse is active. In addition, all physical attributes are reduced by the amount of \textbf{magic level}.


\subsection*{Lizard Call}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 8\\
    \textbf{\trans{arcana_cost_label}:} & 3\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 3\\
\textbf{\trans{duration_label}:} & Magic Level hours\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Conjuration\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


Summon a number of small lizards that will obey simple commands. The number summoned is equal to the \textbf{power} of the spell.


\subsection*{Decomposition}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 10\\
    \textbf{\trans{arcana_cost_label}:} & 4\\
    \textbf{\trans{range_label}:} & 15\\
    \textbf{\trans{actions_label}:} & 2\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Damage\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


Causes the target's flesh to rot, dealing direct damage and attribute loss based on the spell's \textbf{power}+\textbf{magic level}. The target of the spell chooses the attributes and distributes the penalty points among them.

The attribute penalties are not removed until the damage is fully healed.


\subsection*{Snake Eyes}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 9\\
    \textbf{\trans{arcana_cost_label}:} & 3\\
    \textbf{\trans{range_label}:} & 10\\
    \textbf{\trans{actions_label}:} & 3\\
\textbf{\trans{duration_label}:} & Spell Power rounds\\    \textbf{\trans{concentration_label}:} & Ja \\
\textbf{\trans{type_label}:} & Control\\
\textbf{\trans{variant_label}:} & Light\\
\end{tabular}


The caster fixes the target with a hypnotic gaze, paralysing it for rounds equal to the spell's \textbf{power}+\textbf{magic level}.


\subsection*{Acid Thorn}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 6\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 15\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Damage\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


A sharp acid thorn is hurled at the target, causing poison damage equal to the spell's \textbf{power}. The thorn has piercing \textbf{magic level}.


\subsection*{Crawling Fear}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 10\\
    \textbf{\trans{arcana_cost_label}:} & 4\\
    \textbf{\trans{range_label}:} & 15\\
    \textbf{\trans{actions_label}:} & 4\\
\textbf{\trans{duration_label}:} & Magic Level minutes\\    \textbf{\trans{concentration_label}:} & Ja \\
\textbf{\trans{type_label}:} & Control\\
\textbf{\trans{variant_label}:} & Mind\\
\end{tabular}


All creatures within range of the spell make a Willpower roll, made harder by the \textbf{power} of the spell.

Those who fail the roll will flee from the lizard in panic.


\section{Chimerology}


\subsection*{Adapt ability}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 8\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Power hours\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Control\\
\textbf{\trans{variant_label}:} & Nature\\
\end{tabular}


The caster touches an animal and begins to murmur the verse repeatedly. 

If the spell is successful, the gifted person receives the animal's ability for \textbf{power} hours. For example, he grows wings capable of flight or receives the nose of a dog. The associated transformation can take several minutes and can sometimes be extremely painful.

The caster gains a bonus of \textbf{magic level} to an attribute corresponding to the animal.


\subsection*{Leviathan creation}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 12\\
    \textbf{\trans{arcana_cost_label}:} & 4\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 10\\
\textbf{\trans{duration_label}:} & 10-Power months\\    \textbf{\trans{concentration_label}:} & Ja \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Nature\\
\end{tabular}


The eggs of a crocodile are wrapped in black cloth beforehand.

The caster encloses one or more crocodile eggs with his hands and speaks the verses of the leviathan creation on them. The eggs are then kept in a dark and warm environment until they hatch. 

\textbf{Magic level} small leviathans hatch from the eggs in 10-\textbf{power} months.


\subsection*{Unholy bond}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 12\\
    \textbf{\trans{arcana_cost_label}:} & 3\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 30\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Nature\\
\end{tabular}


The caster presses all the animals he wants to unite tightly together for the whole duration of the action and casts the spell. 

The animals unite to form a chimera for \textbf{power}*10 minutes as specified by the caster. When the spell expires or is cancelled, they separate again to their original form. The chimera is aggressive and not under the caster's control. 

The chimera may consist of a maximum of \textbf{magic level} animals.


\section{Curses}


\subsection*{Aging}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 2\\
\textbf{\trans{duration_label}:} & Power+Magic level years\\    \textbf{\trans{concentration_label}:} & Ja \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


The caster must cast the curse while touching the victim.

Shortly after the cursing, the victim starts to feel the first effects. The cursed person feels weakened, which, in addition to the unpleasant feeling, is manifested in the reduction of the values for strength, willpower, reaction, speed and perception by 1.

As long as the curse is active, these values decrease every day by another point. If one of the attributes reaches the value 0, the victim becomes bedridden and can no longer get up by himself.

The curse can be broken by countermagic, divine work or a blessing. Likewise, the curse ends if the caster drops the spell or becomes unconscious.


\subsection*{Fear}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 2\\
\textbf{\trans{duration_label}:} & Magic Level d6 minutes\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Control\\
\textbf{\trans{variant_label}:} & Mind\\
\end{tabular}


The caster must cast the curse while touching the victim.

The victim panics and thinks only of escape for the next \textbf{magic level} d6 minutes. 
The victim escapes the curse with a successful Courage roll. The minimum roll for this is increased by the spell's power.

The curse can be broken by countermagic, divine work or a blessing. Likewise, the curse ends if the caster drops the spell or becomes unconscious.


\subsection*{Drying out}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 3\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 2\\
\textbf{\trans{duration_label}:} & Power years\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


The caster must cast the curse while touching the victim.

The victim loses \textbf{magic level} + 5\% of his body fluid every day. By ingesting fluid, he can slow down the effect to 3\%, but not completely prevent it. After the cursed person has lost 20\% of his body fluid, one can already see the first signs of the deficiency. The skin becomes drier, the first sores appear. At 40\%, the cursed is already weakened to the point that all attribute values are halved. From a fluid loss of 70\% (now the skin seems to resemble a dry piece of leather) it is hardly possible for the cursed to stand up. Everything around him becomes blurred, and he has no way to take care of himself. Only when all liquid has escaped from the body, the cursed dies. Until that time, the fox keeps him alive. 

The curse can be broken by countermagic, divine work or a blessing. Likewise, the curse ends if the caster drops the spell or becomes unconscious.


\subsection*{Curse of the mind}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 3\\
    \textbf{\trans{range_label}:} & 40\\
    \textbf{\trans{actions_label}:} & 10\\
\textbf{\trans{duration_label}:} & Power months\\    \textbf{\trans{concentration_label}:} & Ja \\
\textbf{\trans{type_label}:} & Damage\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


The caster must cast the curse while writing the victim's name on a piece of paper or parchment.

The caster enters a trance-like state in which he bleeds the preferably stunned victim. The curse is transferred to the one whose name is written on the paper and on whom the caster has focused his hatred. After that, the caster falls into a swoon that turns into a restless sleep.

The victim bleeds from all pores as long as the curse lasts. Blood leaks from his eyes and nose, and the victim takes \textbf{magic level} d6 wounds per day.

The curse can be broken by countermagic, divine work or a blessing. Likewise, the curse ends if the caster drops the spell or becomes unconscious.


\subsection*{Paralysis of self}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 2\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 2\\
\textbf{\trans{duration_label}:} & Power+Magic level hours\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Control\\
\textbf{\trans{variant_label}:} & Mind\\
\end{tabular}


The caster must speak the curse while touching the victim.

The victim's tongue and limbs feel heavy and do not want to do their job properly. 
All physical attributes except Resistance are reduced by 1 with all consequences. The curse lasts \textbf{power}+\textbf{magic level} hours.

The curse can be broken by countermagic, divine work or a blessing. Likewise, the curse ends if the caster drops the spell or becomes unconscious.


\subsection*{Madaeus flu}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 3\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Transmutation\\
\textbf{\trans{variant_label}:} & Blood\\
\end{tabular}


The caster must speak the curse while touching the victim.

The victim falls ill with Madeus flu the next day. Throat and pharyngeal complaints, in addition to a slight fever and coughing irritations characterize the clinical picture. The victim remains sick until he is either magically cured or at least two other people are naturally infected. The flu is never fatal, but it is perceived as an annoying, unpleasant nuisance. The contagion rate is \textbf{magic level}*10 \% per day of stay in the company of a cursed person. 

The curse can be broken by countermagic, divine work or a blessing. Likewise, the curse ends if the caster drops the spell or becomes unconscious.


\subsection*{Bad luck}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 2\\
\textbf{\trans{duration_label}:} & Power+Magic level hours\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Control\\
\textbf{\trans{variant_label}:} & Mind\\
\end{tabular}


The caster must speak the curse while touching the victim.

The victim of the curse receives a bad luck value equal to the strength of the spell for the duration of the curse.

The victim, after making a roll for their actions, must roll on the bad luck value. If the bad luck roll shows a success, the action fails.

The curse can be broken by countermagic, divine work or a blessing. Likewise, the curse ends if the caster drops the spell or becomes unconscious.


\subsection*{Self blame}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Control\\
\textbf{\trans{variant_label}:} & Mind\\
\end{tabular}


The caster must speak the curse while touching the victim.

The victim does not feel the curse until he makes the first strike/shot against any target. 

The damage caused to a target by a hit from the cursed one comes back to him 1 to 1, he suffers the same hits as the attacked one. The curse lasts \textbf{magic level} attacks from the cursed.

The curse can be broken by countermagic, divine work or a blessing. Likewise, the curse ends if the caster drops the spell or becomes unconscious.


\subsection*{Shura's madness}

\begin{tabular}{@{}ll@{}}
    \textbf{\trans{spell_points_label}:} & 5\\
    \textbf{\trans{arcana_cost_label}:} & 1\\
    \textbf{\trans{range_label}:} & 0\\
    \textbf{\trans{actions_label}:} & 1\\
\textbf{\trans{duration_label}:} & Magic Level d6 seconds\\    \textbf{\trans{concentration_label}:} & Nein \\
\textbf{\trans{type_label}:} & Control\\
\textbf{\trans{variant_label}:} & Mind\\
\end{tabular}


The caster must speak the curse while touching the victim.

The victim is immediately seized by panic. The only thought that can be held for the next \textbf{magic level} d6 seconds is GET AWAY HERE. However, the fear can be shaken off by a test of willpower. The minimum roll of this trial is increased by the strength of the spell.

The curse can be broken by countermagic, divine work or a blessing. Likewise, the curse ends if the caster drops the spell or becomes unconscious.


\end{multicols}